### 2024-10-09 ila/document.tex
daje che si parte

\documentclass[]{scrreprt}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}

\tikzstyle{startstop} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black]
\tikzstyle{process} = [rectangle, minimum width=3cm, minimum height=1cm, text centered, draw=black]
\tikzstyle{decision} = [diamond, minimum width=1.5cm, minimum height=0.5cm, text centered, draw=black]
\tikzstyle{arrow} = [thick,->,>=stealth]

% Title Page
\title{}
\author{}
\date{}

\begin{document}
\pagestyle{empty}
ILA

	\begin{tikzpicture}[node distance=3cm]

	% Nodes
	\node (start) [startstop] {Start, for $k \geq 1$};
	\node (target) [process, below of=start] {$\theta_{target} = \arg\max |\mathbf{TIF}^* - \mathbf{TIF}^{k-1}|$};
	\node (additem) [process, below of=target] {$Q^{k} = Q^{k-1} \cup \arg\min |\theta_{target} - b_i|$};
	\node (update) [process, below of=additem] {$\mathbf{TIF}^{k} = \frac{\sum_{i \in Q^k} \mathbf{IIF}_i}{||Q^k||}$};
	\node (check) [decision, right of=update, xshift=4cm] {$|\mathbf{TIF}^* - \mathbf{TIF}^k| \geq |\mathbf{TIF}^* - \mathbf{TIF}^{k-1}|$?};
	\node (stop) [startstop, below of=check, yshift=-3.5cm] {Stop \& Return $Q_{ILA} = Q^{k-1}$};

	% Arrows
	\draw [arrow] (start) -- (target);
	\draw [arrow] (target) -- (additem);
	\draw [arrow] (additem) -- (update);
	\draw [arrow] (update) -- (check);
	\draw [arrow] (check) -- node[anchor=east] {Yes} (stop);
	\draw [arrow] (check.east) -- ++(1,0) -- ++(0,6) -- node[anchor=north] {No, $k = k +1$} (target.east);

\end{tikzpicture}

\newpage

FRANK

$B$ set of items of the item bank

$Q^k \subset B \setminus Q^{k-1}$: Set of items included up to iteration k

$\mathbf{TIF}^*$: TIF Target

Termination criterion:

$|TIF^* - TIF^k| \geq |TIF^* - TIF^{k-1}|$ se è vero si ferma e prende la selezione in $Q^k$. Dettaglio non indifferente il cofnronto è fatto sulla media. cioè calcolo la distanza puntuale e poi faccio la media

Se è falso $k = k + 1$ (Livio io sta roba dei due punti non l'ho capita mettitela via)

Start, $k = 0$, $Q^0 = \emptyset$

$Q^k = Q^{k-1} \cup \arg \min |TIF^* - IIF_{i \in B \setminus Q^{k-1}}|$

Per come funziona è impossibile che ci sia solo un item selezionato. Comunque ora testa il criterio di uscita e va avanti

Per $k \geq 1$:

Adesso io ho un vettore colonna $IIF_{i \in Q^{k-1}}$ che è la iif per tutto il tratto latente $\theta$. Questo vettore colonna diventa una matrice di n righe quanti sono i livelli di theta e $i$ colonne quanti sono gli item considerati a $k-1$.

Io adesso avrei bigono di creare una TIF temporanea dove vado ad aggiungere alle IIF degli item in $Q^k-1$ la IIF di ognuno degli item rimasti in B che non sono in $Q^{k-1}$ uno alla volta. Attenzione perché dovrebbe essere la TIF media, quindi la somma delle IIF divise per il numero $i$ di colonne di questa matrice. Dato il $k$ (l'iterazione), il denominatore è fisso, cambia l'item che viene aggiunto alla matrice. Va bhe sta robala capisco solo io. Teoricamente sarebbe:

$$TIF_{i \in B\setminus Q^{k-1}}^k = \frac{IIF_{i \in Q^{k-1}} + IIF_{i \in B \setminus Q^{k-1}}}{||Q^{k-1}|| + 1}$$ (+1 perché aggiungo questo item temporaneo)

Però così non va bene perché qui $TIF_{i \in B\setminus Q^{k-1}}^k$ non so se è chiaro che viene aggiunto un item alla volta.

Bon a sto punto l'item che devo aggiungere a Q è quello che permettte di minimizzare la distanza dalla tif target:

$Q^k = Q^{k-1} \cup \arg \min |TIF^* - TIF^k|$

\end{document}

### 2024-10-09 the-good-the-bad-the-ugly.qmd
daje che si parte

---
title: "IRT procedures for shortening tests"
author: "Ottavia M. Epifania & Friends"
format: 
  revealjs: 
    theme: mytheme.scss
background-opacity: "0.45"
title-slide-attributes: 
   data-background-image: "https://psicostat.github.io/shine-bright/gbu.jpg"
   data-background-size: 350px, cover
   data-background-position: 50% 5%, center
---

```{r, setup, include=FALSE}
library(knitr)

```

## Item Locating Algotihm -- ILA
### The bad

:::: {.columns}

::: {.column width="40%"}

<font size="4">
$B$: Item bank

$Q^k \subset B \setminus Q^{k-1}$: Set of item indexes selected for inclusion in the STF up to iteration $k$ ($Q^0 = \emptyset$)

$\mathbf{TIF}^*$: TIF target

$TIF^k = \frac{\sum_{i\in Q^k} IIF_i}{||Q^k||}$, where $||Q^k||$ denotes the cardinality of $Q^k$, $\mathbf{TIF}^0 = (0, 0, \ldots, 0)$

</font>

:::

::: {.column width="60%"}

```{r}
#| fig-align: center
knitr::include_graphics("img/ila.png")
```

:::

::::

## Frank[^1]
### The good

[^1]: **FRANK**ly I didnt' know how to name it

## Bruto 
### The bad

## Bullets

When you click the **Render** button a document will be generated that includes:

-   Content authored with markdown
-   Output from executable code

## Code

When you click the **Render** button a presentation will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

### 2024-10-09 frank/forward search.R

@@ -1,0 +1,374 @@
+rm(list = ls())
+library(tidyverse)
+# dovresti lanciare dalle funzioni fino in fondo :) grazie 
+# funzioni forme brevi
+# funzione per stimare la probabilità dati i parametrid egli item e del soggetto
+IRT <- function(theta, a = 1, b = 0, c = 0,e = 1) {
+  y <- c + (e - c) * exp(a * (theta - b)) / (1 + exp(a * (theta - b)))
+  return(y)
+}
+# calcola l'IIF per un item specifico
+i_info <- function(b, a=1,c=0, theta = seq(-5,5,length.out=1000)){
+  P <- NULL
+  Q <- NULL
+  Ii <- NULL
+  
+  for(i in 1:length(theta)){
+    P[i] <- 1/(1+ exp (-a*(theta[i] - b)))
+    Q[i]= 1-P[i]
+    Ii[i] =(a*Q[i]*(P[i]-c)^2)/(P[i]*((1-c)^2)) # (3PL)
+  }
+  return(Ii)
+}
+# calcola l'IIF di tutti gli item e restituisce in una lista di lunghezza ugaule a tutti 
+# gli item per cui si è calcolata l'IIF
+item_info <- function(ipar, theta = seq(-5,5,length.out=1000)){
+  item <- NULL
+  for(i in 1:nrow(ipar)){
+    item[[i]] <- i_info(ipar[i, "b"],ipar[i, "a"], theta = theta)
+  }
+  return(item)
+}
+#' Franco
+#'
+#' @param target dataframe con i valori theta (theta) e la tif target (target)
+#' @param parameters dataframe con as many rowas as number of items e due colonne, difficoltà (b) e discriminatività (a)
+#'
+#' @return 
+#' @export
+#'
+#' @examples
+franco = function(target, parameters) {
+  # calcolo le iifs di tutti gli item dato il theta e i parametri
+  all_iifs = item_info(parameters, theta = target$theta)
+  all_iifs = data.frame(do.call("cbind", all_iifs))
+  colnames(all_iifs) = rownames(parameters)
+  all_iifs = cbind(theta, all_iifs)
+  # prende solo le IIF
+  iif_start = data.frame(all_iifs[, grep("item", colnames(all_iifs))])
+  # inizializza le varie robe che servon nella funzione 
+  index_item = NULL
+  temp_sel = NULL
+  sel_temp = NULL
+  dist_k = NULL
+  temp_dist = NULL
[…]

### 2024-10-09 frank/franco.R

@@ -1,0 +1,557 @@
+# frank ------
+rm(list = ls())
+library(tidyverse)
+# dovresti lanciare dalle funzioni fino in fondo :) grazie 
+# funzioni forme brevi
+# funzione per stimare la probabilità dati i parametrid egli item e del soggetto
+IRT <- function(theta, a = 1, b = 0, c = 0,e = 1) {
+  y <- c + (e - c) * exp(a * (theta - b)) / (1 + exp(a * (theta - b)))
+  return(y)
+}
+# calcola l'IIF per un item specifico
+i_info <- function(b, a=1,c=0, theta = seq(-5,5,length.out=1000)){
+  P <- NULL
+  Q <- NULL
+  Ii <- NULL
+  
+  for(i in 1:length(theta)){
+    P[i] <- 1/(1+ exp (-a*(theta[i] - b)))
+    Q[i]= 1-P[i]
+    Ii[i] =(a*Q[i]*(P[i]-c)^2)/(P[i]*((1-c)^2)) # (3PL)
+  }
+  return(Ii)
+}
+# calcola l'IIF di tutti gli item e restituisce in una lista di lunghezza ugaule a tutti 
+# gli item per cui si è calcolata l'IIF
+item_info <- function(ipar, theta = seq(-5,5,length.out=1000)){
+  item <- NULL
+  for(i in 1:nrow(ipar)){
+    item[[i]] <- i_info(ipar[i, "b"],ipar[i, "a"], theta = theta)
+  }
+  return(item)
+}
+# lo chiamo ILA ma è lo stesso di Ilocate
+ila = function(TIF, parameters, print = TRUE) {
+  # tif target
+
+  mygraphs = list()
+  data_graphs = list()
+  mytif = TIF
+  token = TRUE
+  mysel = NULL
+  interim_infos = list()
+  interim_infos_temp = list()
+ # browser()
+  for (i in 1:nrow(parameters)) {
+    if (token == TRUE) {
+      if (i == 1) {
+        parameters$temp_theta = mytif[which(mytif$mean_tif == max(mytif$mean_tif)), "theta"] 
+      } else {
+        parameters$temp_theta = widesel[which(widesel$difference == max(widesel$difference)), "theta"]
+        
+      }
+      # questo codice funziona molto bene per Rasch, è la cosa migliore 
+      parameters$temp_iif = with(parameters,
+                                 abs(temp_theta - b))
+      if (is.null(mysel)) {
[…]

### 2024-10-09 ila/die-algorithm-10-items-mod-index.R

@@ -1,0 +1,998 @@
+# die algorithm
+rm(list = ls())
+library(tidyverse)
+# dovresti lanciare dalle funzioni fino in fondo :) grazie 
+# funzioni forme brevi
+# funzione per stimare la probabilità dati i parametrid egli item e del soggetto
+IRT <- function(theta, a = 1, b = 0, c = 0,e = 1) {
+  y <- c + (e - c) * exp(a * (theta - b)) / (1 + exp(a * (theta - b)))
+  return(y)
+}
+# calcola l'IIF per un item specifico
+i_info <- function(b, a=1,c=0, theta = seq(-5,5,length.out=1000)){
+  P <- NULL
+  Q <- NULL
+  Ii <- NULL
+  
+  for(i in 1:length(theta)){
+    P[i] <- 1/(1+ exp (-a*(theta[i] - b)))
+    Q[i]= 1-P[i]
+    Ii[i] =(a*Q[i]*(P[i]-c)^2)/(P[i]*((1-c)^2)) # (3PL)
+  }
+  return(Ii)
+}
+# calcola l'IIF di tutti gli item e restituisce in una lista di lunghezza ugaule a tutti 
+# gli item per cui si è calcolata l'IIF
+item_info <- function(ipar, theta = seq(-5,5,length.out=1000)){
+  item <- NULL
+  for(i in 1:nrow(ipar)){
+    item[[i]] <- i_info(ipar[i, "b"],ipar[i, "a"], theta = theta)
+  }
+  return(item)
+}
+
+# questa funzione serve per selezionare (dal dataframe oridnato per differenze di tif medie )
+# le forme brevi con diversa lunghezza più vicine possibili alla forma target
+select_combos = function(vector, element_to_find) {
+  my_selections = NULL
+  for (i in element_to_find) {
+    index <- 1
+    while (index <= length(vector) && vector[index] != i) {
+      index <- index + 1
+    }
+    my_selections = c(index, my_selections)
+  }
+  return(my_selections)
+}
+# questa è la forza bruta che prova tutte le possibili combinazioni di item 
+# da 1 a n item - 1
+select_items = function(parameters, 
+                        theta = seq(-5,5, length.out = 1000), 
+                        length_target = NULL, 
+                        add_difficulty = NULL, 
+                        add_discriminativity = NULL, 
+                        seed = 1312) {
+  set.seed(seed)
+  if (is.null(parameters)) {
[…]

### 2024-10-09 ila/modified-indexes-ILA.R

@@ -1,0 +1,1438 @@
+# simulazione per stabilire quale è la massima accuratezza raggiungibile 
+# con l'algoritmo intelligente Iselect 
+
+# die algorithm
+
+rm(list = ls())
+library(tidyverse)
+# dovresti lanciare dalle funzioni fino in fondo :) grazie 
+# funzioni forme brevi
+# funzione per stimare la probabilità dati i parametrid egli item e del soggetto
+IRT <- function(theta, a = 1, b = 0, c = 0,e = 1) {
+  y <- c + (e - c) * exp(a * (theta - b)) / (1 + exp(a * (theta - b)))
+  return(y)
+}
+# calcola l'IIF per un item specifico
+i_info <- function(b, a=1,c=0, theta = seq(-5,5,length.out=1000)){
+  P <- NULL
+  Q <- NULL
+  Ii <- NULL
+  
+  for(i in 1:length(theta)){
+    P[i] <- 1/(1+ exp (-a*(theta[i] - b)))
+    Q[i]= 1-P[i]
+    Ii[i] =(a*Q[i]*(P[i]-c)^2)/(P[i]*((1-c)^2)) # (3PL)
+  }
+  return(Ii)
+}
+# calcola l'IIF di tutti gli item e restituisce in una lista di lunghezza ugaule a tutti 
+# gli item per cui si è calcolata l'IIF
+item_info <- function(ipar, theta = seq(-5,5,length.out=1000)){
+  item <- NULL
+  for(i in 1:nrow(ipar)){
+    item[[i]] <- i_info(ipar[i, "b"],ipar[i, "a"], theta = theta)
+  }
+  return(item)
+}
+
+# questa funzione serve per selezionare (dal dataframe oridnato per differenze di tif medie )
+# le forme brevi con diversa lunghezza più vicine possibili alla forma target
+select_combos = function(vector, element_to_find) {
+  my_selections = NULL
+  for (i in element_to_find) {
+    index <- 1
+    while (index <= length(vector) && vector[index] != i) {
+      index <- index + 1
+    }
+    my_selections = c(index, my_selections)
+  }
+  return(my_selections)
+}
+# questa è la forza bruta che prova tutte le possibili combinazioni di item 
+# da 1 a n item - 1
+select_items = function(parameters, 
+                        theta = seq(-5,5, length.out = 1000), 
+                        length_target = NULL, 
+                        add_difficulty = NULL, 
+                        add_discriminativity = NULL, 
[…]

### 2024-10-09 the-good-the-bad-the-ugly.R

@@ -1,0 +1,757 @@
+# confronot the good the bad and the ugly 
+rm(list = ls())
+library(tidyverse)
+#' ilafrank
+#' 
+#' Confronta le robe ottenute con ila frank e frankie per fare i grafici
+#'
+#' @param ila l'oggetto dei risultati ottenuto con ila
+#' @param frank l'oggetto dei risultati ottenuto con frank 
+#' @param frankie l'oggetto dei risultati ottenuto con frankie
+#' @param n il numero di iterazione di cui si vogliono vedere i risultati (se non ci sono iterazioni ci si attacca al cazzo perché non funge)
+#' @param last se falso si vedono TUTTI gli step di item inclusion fatti da frank e frankie
+#'
+#' @return
+#' @export
+#'
+#' @examples
+ilafrank = function(ila, frank, frankie = NULL, n=1, last = TRUE) {
+  # browser()
+  if (is.null(frankie)) {
+    tempAttempt = ila[[n]]$select_attempts[[length(ila[[n]]$select_attempts)]]
+    ilaGraph = tempAttempt[, c("theta", "type","mean_tif.x")]
+    colnames(ilaGraph) = c("theta",    "type", "mean_tif")
+    ilaGraph$type = gsub("temp", "ila", ilaGraph$type)
+    
+    frankLong =  pivot_longer(frank[[n]]$tif, 
+                              cols = !theta, 
+                              names_to = "tif")
+    colnames(frankLong) = colnames(ilaGraph)
+    frankLong$type = gsub("temp", "frank", frankLong$type)
+    frank_lab = unique(frankLong$type)
+    frank_lab = frank_lab[c(length(frank_lab))]
+    frankieLong = NULL
+  } else {
+    frankieLong =  pivot_longer(frankie[[n]]$tif, 
+                                cols = !theta, 
+                                names_to = "tif")
+    colnames(frankieLong) = colnames(ilaGraph)
+    frankieLong$type = gsub("temp", "frankie", frankieLong$type)
+    frankie_lab = unique(frankieLong$type)
+    frankie_lab = frankie_lab[c(length(frankie_lab))]
+  }
+  
+  if (last == TRUE & !is.null(frankie)) {
+    frankieLong = frankieLong[frankieLong$type %in% c("mean_tif", frankie_lab),]
+    frankLong = frankLong[frankLong$type %in% c("mean_tif", frank_lab),]
+  } else if (last == TRUE & is.null(frankie)) {
[…]

### 2024-10-09 the-good-the-bad-the-ugly.qmd
a lot

@@
    data-background-position: 50% 5%, center
+server: shiny
 ---
@@
 library(knitr)
+library(shiny)
+IRT <- function(theta, a = 1, b = 0, c = 0,e = 1) {
+  y <- c + (e - c) * exp(a * (theta - b)) / (1 + exp(a * (theta - b)))
+  y[is.na(y)] = 1
+  return(y)
+}
+
+i_info <- function(b, a=1,c=0, theta = seq(-5,5,length.out=1000)){
+
+P <- NULL 
+Q <- NULL
+Ii <- NULL
+for(i in 1:1000){
+  P[i] <- 1/(1+ exp (-a*(theta[i] - b)))
+  Q[i]= 1-P[i]
+  Ii[i] =(a*Q[i]*(P[i]-c)^2)/(P[i]*((1-c)^2)) # (3PL)
+   }
+return(Ii)
+}
+# Function to get all item information
+item_info <- function(b,a=1, c= 0){
+item <- NULL
+  for(i in 1:length(b)){
+  item[[i]] <- i_info(b[i],a[i])
+  }
+return(item)
+}
+
+set.seed(999)
+```
+
+## The 2-Parameter Logistic Model
+
+$$P(x_{pi} = 1|\theta_p, b_i, a_i) = \frac{\exp[a_i(\theta_p - b_i)])}{1 + \exp[a_i(\theta_p - b_i)])}$$
+
+$$IIF_i = a_i^2P(\theta, b_i, a_i)[1-P(\theta, b_i, a_i)]$$
+
+$$TIF = \sum_{i = 1}^{||B||} IIF_i$$
+
+## Intuitively
+
+```{r}
+#| panel: sidebar
+tags$style(HTML(".js-irs-0 .irs-single, .js-irs-0 .irs-bar-edge, .js-irs-0 .irs-bar {background: royalblue}"))
+tags$style(HTML(".js-irs-1 .irs-single, .js-irs-1 .irs-bar-edge, .js-irs-1 .irs-bar {background: magenta}"))
+tags$style(HTML(".js-irs-2 .irs-single, .js-irs-2 .irs-bar-edge, .js-irs-2 .irs-bar {background: seagreen}"))
+tags$style(HTML(".js-irs-3 .irs-single, .js-irs-3 .irs-bar-edge, .js-irs-3 .irs-bar {background: royalblue}"))
+tags$style(HTML(".js-irs-4 .irs-single, .js-irs-3 .irs-bar-edge, .js-irs-4 .irs-bar {background: magenta}"))
+tags$style(HTML(".js-irs-5 .irs-single, .js-irs-5 .irs-bar-edge, .js-irs-5 .irs-bar {background: seagreen}"))
+
+ sliderInput("b1", "b1",
+                  min = -3, max = 3,
+                  value = 0, step = 0.1)
+sliderInput("b2", "b2",
+                  min = -3, max = 3,
+                  value = 0, step = 0.1)
+sliderInput("b3", "b3",
+                  min = -3, max = 3,
+                  value = 0, step = 0.1)
+
+sliderInput("a1", "a1",
+                  min = 0.20, max = 3,
+                  value = 1, step = 0.1)
+sliderInput("a2", "a2",
+                  min = 0, max = 3,
+                  value = 0.70, step = 0.1)
+sliderInput("a3", "a3",
+                  min = 0, max = 3,
+                  value = 1.90, step = 0.1)
+checkboxInput("showTif", "Show Test Information Function", value = FALSE)
 
@@
 
-## Item Locating Algotihm -- ILA
+```{r}
+#| panel: fill
+
+plotOutput("plot", height = "300px")
+
+plotOutput("tif", height = "300px")
+```
+
+```{r}
+#| context: server
+ output$plot <- renderPlot({
+   theta <- theta <- seq(-7, 7, .001)
+  par(mar = c(5,7,4,2) + 0.1)
+  b = c(input$b1, input$b2, input$b3)
+  a = c(input$a1, input$a2, input$a3)
+
+ plot(theta, IRT(theta, b = input$b1, a = input$a1), 
+                 type = "l", lwd = 2, lty = 2,
+     col = "royalblue", main = "Item Characteristics Curves - ICCs", 
+     ylab = expression(paste("P(", x[p][i],  "= 1|", theta[p], ", ", b[i], ", ", a[i], ")")), 
+     xlab = expression(theta), 
+     cex.lab = 2.4, 
+     cex.main = 3, 
+     cex.text=2, cex.axis=1.5)
+
+segments(min(theta)-3, 0.5, 
+         input$b1, 0.5, 
+         col = "gray56", lty = 3, lwd = 1.3)
+segments(input$b1, -0.5, 
+         input$b1, 0.5, 
+         col = "royalblue", lty = 3, lwd = 1.3)
+
+lines(theta, IRT(theta, b=input$b2,
+                 a=input$a2),
+       type = "l", lwd = 2, lty = 2,
+     col = "magenta")
+ lines(theta, IRT(theta, b=input$b3,
+                 a=input$a3),
+       type = "l", lwd = 2, lty = 2,
+     col = "seagreen")
+ segments(min(theta)-3, 0.5, 
+         input$b2, 0.5, 
+         col = "gray56", lty = 3, lwd = 1.3)
+segments(input$b2, -0.5, 
+         input$b2, 0.5, 
+         col = "magenta", lty = 3, lwd = 1.3)
+ segments(min(theta)-3, 0.5, 
+         input$b3, 0.5, 
+         col = "gray56", lty = 3, lwd = 1.3)
+segments(input$b3, -0.5, 
+         input$b3, 0.5, 
+         col = "seagreen", lty = 3, lwd = 1.3)
+  })
+
+output$tif <- renderPlot({
+
+   theta <- theta <- seq(-7, 7, .001)
+  par(mar = c(5,7,4,2) + 0.1)
+  b = c(input$b1, input$b2, input$b3)
+  a = c(input$a1, input$a2, input$a3)
+c <- item_info(b,a)
+Theta <- matrix(seq(-4,4, length.out=1000))
+check <- data.frame(Theta,
+                    item_info = c[[1]],
+                    item_info2 = c[[2]],
+                    item_info3 = c[[3]])
+d <- do.call('cbind',c)
+sum_info1 <- rowSums(d)
+d1 <- do.call('cbind',c)
+sum_info2 <- rowSums(d1)
+plot(check$Theta, check$item_info, cex.lab= 2, main = "Item Information Functions - IIFs",
+      cex.lab = 2.4, 
+     cex.main = 3, 
+     cex.text=2, cex.axis=1.5,
+        xlab = expression(theta), ylab = expression(paste("IIF"[i])),
+ type = "l", lwd =2,
+      col = "royalblue", ylim = c(0,1))
+ lines(check$Theta, check$item_info2, lwd =2,
+       col = "magenta", lty = 4)
+ lines(check$Theta, check$item_info3, lwd =2,
+       col = "seagreen", lty = 2)
+
+checkTif <- data.frame(Theta, sum_info1, sum_info2)
+
+if (input$showTif == TRUE) {
+  plot(checkTif$Theta, checkTif$sum_info2,
+       type = "l", lwd =2,
+     col = "black", ylim = c(0, 2),
+       xlab = expression(theta), 
+     ylab = expression(paste("I(", theta, ")")), 
+     cex.axis=1.5, main = "IIFs and Test Information Functions",  
+     cex.lab = 2.4, 
+     cex.main = 3, 
+     cex.text=2)
+  lines(check$Theta, check$item_info, lwd =2,
+       col = "royalblue", lty = 4)
+   lines(check$Theta, check$item_info2, lwd =2,
+       col = "magenta", lty = 4)
+ lines(check$Theta, check$item_info3, lwd =2,
+       col = "seagreen", lty = 2)
+}
+
+})
+```
+
+## Some premises
+
+::: {.callout-note}
+## Key concept
+
+<font size = "4">
+**TIF target** ($\mathbf{TIF}^*$) describing the desired characteristics of a test
+</font>
+:::
+
+::: {.callout-tip}
+## The aim of the algorithms
+
+<font size = "4">
+*Minimize the distance* between $\mathbf{TIF}^*$ and that of the short test forms (STFs) 
+</font>
+:::
+
+::: {.callout-warning}
+## Their differences
+
+<font size = "4">
+The method for selecting and including the items in $Q \subset B$ from the item bank
+</font>
+:::
+
+::: {.callout-important}
+## Mean TIF
+
+<font size = "4">
+TIF is considered as mean TIF $\rightarrow$ as the number of items increases, the TIF increases
+</font>
+:::
+
+## Bruto (tu quoque?!)
 ### The bad
+
+<font size = "5">
+
+$Q_m \subset B = 2^{||B||}-2$ STFs of different lengths considering different item combination can be developed from $B$. That's what Bruto does
+
+1. $\mathbf{TIF}^{Q_m} =  \frac{\sum_{i \in Q_m} IIF_i}{||Q_m||}$
+2. $\overline{\Delta}_{\mathbf{TIF}^{Q_m}} =  \mathit{mean}(|\mathbf{TIF}^* - \mathbf{TIF}^{Q_m}|)$
+
+$Q_{bruto} = \arg \min_{Q_m \subset B} \overline{\Delta}_{\mathbf{TIF}^{Q_m}}$
+</font>
+
+```{r}
+#| fig-align: center
+#| out-width: "50%"
+knitr::include_graphics("www/eeato.jpg")
+```
+
+## Item Locating Algorithm -- ILA
+### The ugly
 
@@
 #| fig-align: center
-knitr::include_graphics("img/ila.png")
+#| out-width: "200%"
+knitr::include_graphics("www/ila.png")
 ```
@@
 
-[^1]: **FRANK**ly I didnt' know how to name it
+At $k = 0$, $Q^0 = \emptyset$. For $k \geq 1$, iterate
 
-## Bruto 
-### The bad
+1. $Q^{k+1} = Q^k \cup \arg \min |TIF^* - IIF_{i \in B \setminus Q^k}|$
 
-## Bullets
+2. $TIF_{i \in B\setminus Q^{k+1}}^{k+1} = \frac{IIF_{i \in Q^{k+1}} + IIF_{i \in B \setminus Q^{k+1}}}{||Q^{k+1}|| + 1}$
 
-When you click the **Render** button a document will be generated that includes:
+Until the termination criterion $|TIF^* - TIF^{k+1}| \geq |TIF^* - TIF^{k}|$ is true $\rightarrow$ $Q_{frank} = Q^{k+1}$
 
--   Content authored with markdown
--   Output from executable code
+[^1]: <font size="3"><font size="6">**FRANK**</font>ly I didnt' know how to name it</font>
 
-## Code
+## Simulation time
 
-When you click the **Render** button a presentation will be generated that includes both content and the output of embedded code. You can embed code like this:
+1. Generate an item bank $B$ of $6$ items: 
+			- Difficulty parameters: $\mathcal{U}(-3, 3)$
+			- Discrimination parameters:  $\mathcal{U}(.90, 2.0)$
 
-```{r}
-1 + 1
-```
+2. Random item selections of lengths $l$ from $B$ ($M_l = 3.34 \pm 1.13$) + modification parameters $\mathcal{U}(-0.20, 0.20)$ $\rightarrow$ $\mathbf{TIF}^*$
+
+3. Considering $\mathbf{TIF}^*$ at Step 2 and item parameters at Step 1:
+
+      - Bruto  $\rightarrow$ Systematically tests
+
+      - ILA  $\rightarrow$ Forwardly searches considering a single $\theta$
+      - Frank $\rightarrow$ Forwardly searches considering the whole latent trait

### 2024-10-09 the-good-the-bad-the-ugly.qmd
i give up

@@
     theme: mytheme.scss
+    logo: "www/psicostat.jpg"
 background-opacity: "0.45"
@@
 library(shiny)
+library(ggplot2)
+library(tidyverse)
 IRT <- function(theta, a = 1, b = 0, c = 0,e = 1) {
@@
 
+Item Response Function:
+
 $$P(x_{pi} = 1|\theta_p, b_i, a_i) = \frac{\exp[a_i(\theta_p - b_i)])}{1 + \exp[a_i(\theta_p - b_i)])}$$
+<br>
+
+Item Information Function:
 
 $$IIF_i = a_i^2P(\theta, b_i, a_i)[1-P(\theta, b_i, a_i)]$$
+
+<br>
+
+Test Information Function:
 
@@
       - Frank $\rightarrow$ Forwardly searches considering the whole latent trait
+
+## Results
+
+```{r}
+load("gbu-comparison.RData")
+item_comparison$iter = 1:100
+ic_long = pivot_longer(item_comparison, cols = !iter)
+
+ic = ic_long %>%  
+  group_by(name) %>%  
+  summarise(min = min(value), max = max(value), mean = mean(value), median = mean(value), 
+            sd = sd(value))
+ggplot(ic, 
+       aes(x = name, y = mean, color = name)) + geom_point(shape = 5, size = 3) + ylim(0,6) + 
+  geom_errorbar(aes(ymin = mean-sd, ymax = mean+sd), width = .2)+ 
+  geom_point(aes(x = name, y = min), shape = 1) + geom_point(aes(x = name, y = max), shape = 15) + 
+  geom_point(aes(x = name, y = median), shape = 4, size = 3) + 
+  scale_color_manual(values = c("royalblue","red",  "seagreen")) + 
+  ylab("Item") + theme_light() + 
+  theme(axis.text = element_text(size = 25), 
+        axis.title.x = element_blank(), 
+        legend.position = "none")
+
+```
+
+## When $||Q_{ILA}|| = ||Q_{Frank}||$
+
+```{r}
+library(patchwork)
+equal_IF = as.numeric(rownames(item_comparison[item_comparison$nfrank == item_comparison$nila, ]))
+wrap_plots(g[equal_IF])
+```

### 2024-10-09 the-good-the-bad-the-ugly.R

@@ -564,6 +564,8 @@ for (i in 1:length(myfrank)) {
   item_comparison[i, "nila"] = nrow(myila[[i]]$end)
   item_select[i, "iila"] = paste(rownames(myila[[i]]$end)[order(rownames(myila[[i]]$end), decreasing = T)], collapse = " ")
 }
+# I saved the enrivorment till here 
+
 x = item_select[1,-3]
 
 
@@ -614,6 +616,35 @@ for (i in 1:length(myfrank)) {
 library(patchwork)
 wrap_plots(g[equal])
 g[[1]]
+
+item_comparison$iter = 1:100
+ic_long = pivot_longer(item_comparison, cols = !iter)
+
+ggplot(ic_long, 
+       aes(x = name, y = value)) + geom_boxplot()
+
+
+ic = ic_long %>%  
+  group_by(name) %>%  
+  summarise(min = min(value), max = max(value), mean = mean(value), median = mean(value), 
+            sd = sd(value))
+
+ggplot(ic, 
+       aes(x = name, y = mean, color = name)) + geom_point(shape = 5, size = 3) + ylim(0,6) + 
+  geom_errorbar(aes(ymin = mean-sd, ymax = mean+sd), width = .2)+ 
+  geom_point(aes(x = name, y = min), shape = 1) + geom_point(aes(x = name, y = max), shape = 15) + 
+  geom_point(aes(x = name, y = median), shape = 4, size = 3) + 
+  scale_color_manual(values = c("royalblue","red",  "seagreen")) + 
+  ylab("Item") + theme_light() + 
+  theme(axis.text = element_text(size = 25), 
+        axis.title.x = element_blank(), 
+        legend.position = "none")
+
+
+apply(item_comparison,2, min)apply(item_comparisiteron,2, min)
+apply(item_comparison,2, max)
+apply(item_comparison,2, median)
+apply(item_comparison,2, mean)
 
 
 # calcolo la distanza media per ogni iteraione di frank e ila da bruto 

### 2024-10-10 the-good-the-bad-the-ugly.qmd
non funziona niente

--- 2024-10-09 the-good-the-bad-the-ugly.qmd
@@
     theme: mytheme.scss
+    logo: "www/psicostat.jpg"
+    footer: "Psicostat meeting"
 background-opacity: "0.45"
@@
    data-background-image: "https://psicostat.github.io/shine-bright/gbu.jpg"
-   data-background-size: 350px, cover
-   data-background-position: 50% 5%, center
+   data-background-size: 450px, cover
+   data-background-position: 50% 15%, center
 server: shiny
 ---
+
+```{css include = FALSE}
+.reveal .slide-logo {
+  height: 100px !important;
+  width: 100px !important;
+  max-width: unset !important;
+  max-height: unset !important;
+}
+```
 
@@
 
-$$P(x_{pi} = 1|\theta_p, b_i, a_i) = \frac{\exp[a_i(\theta_p - b_i)])}{1 + \exp[a_i(\theta_p - b_i)])}$$
+Item Response Function:
+
+$$P(x_{pi} = 1|\theta_p, b_i, a_i) = \frac{\exp[a_i(\theta_p - b_i)])}{1 + \exp[a_i(\theta_p - b_i)]}$$
+<br>
+
+Item Information Function:
 
 $$IIF_i = a_i^2P(\theta, b_i, a_i)[1-P(\theta, b_i, a_i)]$$
+
+<br>
+
+Test Information Function:
 
@@
 
-<font size = "5">
+$\forall Q \in\mathcal{Q} = 2^B \setminus \{\emptyset, B\}$,
 
-$Q_m \subset B = 2^{||B||}-2$ STFs of different lengths considering different item combination can be developed from $B$. That's what Bruto does
+1. $\mathbf{TIF}^{Q} =  \frac{\sum_{i \in Q} IIF_i}{||Q||}$
+2. $\overline{\Delta}_{\mathbf{TIF}^{Q}} =  \mathit{mean}(|\mathbf{TIF}^* - \mathbf{TIF}^{Q}|)$
 
-1. $\mathbf{TIF}^{Q_m} =  \frac{\sum_{i \in Q_m} IIF_i}{||Q_m||}$
-2. $\overline{\Delta}_{\mathbf{TIF}^{Q_m}} =  \mathit{mean}(|\mathbf{TIF}^* - \mathbf{TIF}^{Q_m}|)$
-
-$Q_{bruto} = \arg \min_{Q_m \subset B} \overline{\Delta}_{\mathbf{TIF}^{Q_m}}$
-</font>
+$Q_{bruto} = \arg \min_{Q \in \mathcal{Q}} \overline{\Delta}_{\mathbf{TIF}^{Q}}$
 
@@
 
-$Q^k \subset B \setminus Q^{k-1}$: Set of item indexes selected for inclusion in the STF up to iteration $k$ ($Q^0 = \emptyset$)
+$Q^k \subset B$: Set of item selected for inclusion in the STF up to iteration $k$ ($Q^0 = \emptyset$)
 
@@
 
-At $k = 0$, $Q^0 = \emptyset$. For $k \geq 1$, iterate
+At $k =0$, $TIF^0 = (0, 0, \ldots, 0)$, $Q^0 = \emptyset$, iterate
 
-1. $Q^{k+1} = Q^k \cup \arg \min |TIF^* - IIF_{i \in B \setminus Q^k}|$
+1. $A^k = B \setminus Q^k$
 
-2. $TIF_{i \in B\setminus Q^{k+1}}^{k+1} = \frac{IIF_{i \in Q^{k+1}} + IIF_{i \in B \setminus Q^{k+1}}}{||Q^{k+1}|| + 1}$
+2. $\forall i \in A^k$, $PIF_{i}^k = \frac{TIF^k + IIF_{i}}{||Q^k||+1}$
 
-Until the termination criterion $|TIF^* - TIF^{k+1}| \geq |TIF^* - TIF^{k}|$ is true $\rightarrow$ $Q_{frank} = Q^{k+1}$
+3. $D = \arg \min_{i \in A^k} |TIF^* - PIF_i^k|$
 
-[^1]: <font size="3"><font size="6">**FRANK**</font>ly I didnt' know how to name it</font>
+Termination criterion: $|TIF^* - PIF_D^{k}| \geq |TIF^* - TIF^{k-1}|$:
+
+  - If false, $k = k + 1,$ $Q^{k+1} = Q^k \cup \{D\}$, restart from 1
+
+  - If true, stops, $Q_{Frank} = Q^k$
+
+[^1]: <font size="3"><font size="6">**FRANK**</font>ly I didn't know how to name it</font>
 
@@
 
+100 data frames
+
 1. Generate an item bank $B$ of $6$ items:
+
       - Difficulty parameters: $\mathcal{U}(-3, 3)$
+
       - Discrimination parameters:  $\mathcal{U}(.90, 2.0)$
@@
       - Frank $\rightarrow$ Forwardly searches considering the whole latent trait
+
+## Results
+
+::: {.panel-tabset}
+
+## So...
+
+```{r}
+
+load("gbu-comparison.RData")
+mycomparison = item_comparison[, c("nbruto", "nfrank", "nila")]
+mycomparison$iter = 1:100
+ic_long = pivot_longer(mycomparison, cols = !iter)
+
+ic = ic_long %>%  
+  group_by(name) %>%  
+  summarise(min = min(value), max = max(value), mean = mean(value), median = mean(value), 
+            sd = sd(value))
+ggplot(ic, 
+       aes(x = name, y = mean, color = name)) + geom_point(shape = 5, size = 6) + ylim(0,6) + 
+  geom_errorbar(aes(ymin = mean-sd, ymax = mean+sd), width = .2)+ 
+  geom_point(aes(x = name, y = min), shape = 19, size = 6) + geom_point(aes(x = name, y = max), 
+                                                                       shape = 15, size = 6) + 
+  geom_point(aes(x = name, y = median), shape = 4, size = 6) + 
+  scale_color_manual(values = c("royalblue","red",  "seagreen")) + 
+  ylab("Number of items") + theme_light() + 
+  theme(axis.text = element_text(size = 26),
+        axis.title.y = element_text(size = 28),
+        axis.title.x = element_blank(), 
+        legend.position = "none")
+
+```
+
+## In summary
+
+```{r}
+ggplot(sum_algo, 
+       aes(x = l_stf, y = mean, color = algo, 
+           shape = algo)) + geom_line(linewidth = 1.2) + geom_point(size = 4) + theme_light() +
+  ylab(expression(paste(TIF^"* - ", TIF[STF]))) +  xlab("Length STF") +
+  scale_color_manual(values = c("royalblue","red",  "seagreen")) +
+  scale_x_continuous(n.breaks = 6)  + theme(axis.title = element_text(size = 28), 
+        axis.text = element_text(size = 26), 
+        legend.position = c(.7,.9), 
+        legend.title = element_blank(), 
+        legend.text = element_text(size = 24), 
+        legend.key.size = unit(2, "cm")) +
+  guides(color=guide_legend(ncol=3))
+
+```
+
+## Spill the tea
+
+```{r}
+ggplot(allalgo, 
+       aes(x = factor(l_stf), y = value, color = algo)) + geom_boxplot() + theme_light() +
+  ylab(expression(paste(TIF^"* - ", TIF[STF]))) +  xlab("Length STF") +
+  scale_color_manual(values = c("royalblue","red",  "seagreen")) +
+  theme(axis.title = element_text(size = 28), 
+        axis.text = element_text(size = 26), 
+        legend.position = c(.7,.9), 
+        legend.title = element_blank(), 
+        legend.text = element_text(size = 24), 
+        legend.key.size = unit(2, "cm")) +
+  guides(color=guide_legend(ncol=3))
+```
+
+:::
+
+## When $||Q_{ILA}|| = ||Q_{Frank}|| = ||Q_{Bruto}||$
+### But $Q_{Ila} \neq Q_{frank} \neq Q_{bruto}$
+
+```{r}
+library(patchwork)
+all_equals = as.numeric(rownames(select_equal1[select_equal1$is_equal_all == FALSE, ])
+)
+wrap_plots(g[all_equals])
+```
+
+## In the end
+
+<br>
+
+Mathematically, we are at loss
+
+Psychologically? I don't know
+
+Do they work? Hopefully
+
+::: {.callout-tip}
+## Acknowfndabfjknc
+
+Pasquale Anselmi, Egidio Robusto, Livio Finos, Gianmarco Altoè
+
+:::
+
+</br>
+
+. . .
+
+::: {.callout-note}
+
+## This happened too
+
+Roses are red, violets are blue,
+
+my computer broke down on these simulations,
+
+and I broke down too
+:::

### 2024-10-10 the-good-the-bad-the-ugly.R

@@ -261,6 +261,8 @@ frank = function(target, parameters) {
         token = TRUE
       } else if (dist_k[i] >= dist_k[i-1]) {
         token  = FALSE
+        tif_k = tif_k[,-ncol(tif_k)]
+        index_item = index_item[-length(index_item)]
       } else {
         token = TRUE
       }
@@ -604,9 +606,9 @@ for (i in 1:length(myfrank)) {
   g[[i]] = ggplot(temp, 
                   aes( x= theta, y = mean_tif, color = type)) + 
     geom_line(linewidth=1.2) + 
-    ggtitle(paste("frank= ", item_comparison[i, "nfrank"], 
-                  " ila=", item_comparison[i, "nila"], 
-                  paste("bruto = ", resBruto[[i]]$best_selections_summary$cat[1]))) + 
+    ggtitle(paste("frank=", item_comparison[i, "nfrank"], 
+                  "ila=", item_comparison[i, "nila"], 
+                  paste("bruto=", resBruto[[i]]$best_selections_summary$cat[1]))) + 
     scale_color_manual(values = c("royalblue","red",  "seagreen", "black"))  +
     theme(legend.position = "none") 
   #   print(g[[i]])
@@ -630,10 +632,11 @@ ic = ic_long %>%
             sd = sd(value))
 
 ggplot(ic, 
-       aes(x = name, y = mean, color = name)) + geom_point(shape = 5, size = 3) + ylim(0,6) + 
+       aes(x = name, y = mean, color = name)) + geom_point(shape = 5, size = 6) + ylim(0,6) + 
   geom_errorbar(aes(ymin = mean-sd, ymax = mean+sd), width = .2)+ 
-  geom_point(aes(x = name, y = min), shape = 1) + geom_point(aes(x = name, y = max), shape = 15) + 
-  geom_point(aes(x = name, y = median), shape = 4, size = 3) + 
+  geom_point(aes(x = name, y = min), shape = 19, size = 6) + geom_point(aes(x = name, y = max), 
+                                                                       shape = 15, size = 6) + 
+  geom_point(aes(x = name, y = median), shape = 4, size = 6) + 
   scale_color_manual(values = c("royalblue","red",  "seagreen")) + 
   ylab("Item") + theme_light() + 
[…]

### 2024-10-10 the-good-the-bad-the-ugly.qmd
upd
mmm

@@
    data-background-image: "https://psicostat.github.io/shine-bright/gbu.jpg"
-   data-background-size: 450px, cover
-   data-background-position: 50% 15%, center
+   data-background-size: 400px, cover
+   data-background-position: 50% 10%, center
 server: shiny
@@
 
+. . .
+
 Item Information Function:
@@
 <br>
+
+. . .
 
@@
                   min = -3, max = 3,
-                  value = 0, step = 0.1)
+                  value = -1, step = 0.1)
 sliderInput("b3", "b3",
                   min = -3, max = 3,
-                  value = 0, step = 0.1)
+                  value = 1, step = 0.1)
 
@@
                   min = 0, max = 3,
-                  value = 0.70, step = 0.1)
+                  value = 1, step = 0.1)
 sliderInput("a3", "a3",
                   min = 0, max = 3,
-                  value = 1.90, step = 0.1)
+                  value = 1, step = 0.1)
 checkboxInput("showTif", "Show Test Information Function", value = FALSE)
@@
 
-At $k =0$, $TIF^0 = (0, 0, \ldots, 0)$, $Q^0 = \emptyset$, iterate
+At $k =0$, $\mathbf{TIF}^0 = (0, 0, \ldots, 0)$, $Q^0 = \emptyset$, iterate
 
@@
 
-2. $\forall i \in A^k$, $PIF_{i}^k = \frac{TIF^k + IIF_{i}}{||Q^k||+1}$
+2. $\forall i \in A^k$, $\mathbf{PIF}_{i}^k = \frac{\mathbf{TIF}^k + \mathbf{IIF}_{i}}{||Q^k||+1}$
 
-3. $D = \arg \min_{i \in A^k} |TIF^* - PIF_i^k|$
+3. $D = \arg \min_{i \in A^k} |\mathbf{TIF}^* - \mathbf{PIF}_i^k|$
 
-Termination criterion: $|TIF^* - PIF_D^{k}| \geq |TIF^* - TIF^{k-1}|$:
+Termination criterion: $|\mathbf{TIF}^* - \mathbf{PIF}_D^{k}| \geq |\mathbf{TIF}^* - \mathbf{TIF}^{k-1}|$:
 

### 2024-10-11 the-good-the-bad-the-ugly.R
update

@@ -605,7 +605,7 @@ for (i in 1:length(myfrank)) {
   temp = rbind(tempBruto, temp)
   g[[i]] = ggplot(temp, 
                   aes( x= theta, y = mean_tif, color = type)) + 
-    geom_line(linewidth=1.2) + 
+    geom_line(linewidth=1) + 
     ggtitle(paste("frank=", item_comparison[i, "nfrank"], 
                   "ila=", item_comparison[i, "nila"], 
                   paste("bruto=", resBruto[[i]]$best_selections_summary$cat[1]))) + 

### 2024-10-18 paper/algorithms.tex
update

\documentclass[12pt, a4paper, titilepage]{article}
\usepackage{graphicx}
\usepackage{subcaption}
\graphicspath{{C:/Users/huawei/Desktop/imag es/}} \usepackage{easyReview}
\usepackage{setspace}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{apacite}
\usepackage{titlesec}
\usepackage{dcolumn}
\usepackage{lscape}
\usepackage{pdflscape}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{times}
\usepackage{booktabs}
\usepackage{fancyhdr}
\usepackage[margin=1in]{geometry}
\usepackage{color}
\usepackage{dcolumn}
\usepackage{siunitx}
\usepackage{array}
\usepackage{longtable}
\usepackage{lineno}
\usepackage{array}
\usepackage{siunitx}
\usepackage{listings}
\usepackage{regexpatch}
\usepackage{multicol}
\usepackage{bm}
\usepackage{lineno}
\usepackage{color, colortbl} %righe colorate
\usepackage{lineno}
\usepackage{easyReview}
\usepackage{amssymb}

\usetikzlibrary{shapes.geometric, arrows}

\tikzstyle{startstop} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black]
\tikzstyle{process} = [rectangle, minimum width=3cm, minimum height=1cm, text centered, draw=black]
\tikzstyle{decision} = [diamond, minimum width=1.5cm, minimum height=0.5cm, text centered, draw=black]
\tikzstyle{arrow} = [thick,->,>=stealth]

%opening
\title{The good, the bad, and the ugly}
\author{}

\begin{document}

\maketitle

\begin{abstract}

\end{abstract}

\newpage

\doublespacing

\section{Bruto}

$ \theta = \{ x \in \mathbb{R} \,|\, \theta_{min} \leq x \leq \theta_{max} \}$: Latent trait levels, where $\theta_{min}$ is the minimum value of $\theta$ and $\theta_{max}$ is its maximum value \add{(non sono sicura della x)}

$||\theta||$: cardinality of the latent trait

$\forall Q \in\mathcal{Q} = 2^B \setminus \{\emptyset, B\}$,

\begin{enumerate}
	\item $\mathbf{TIF}^{Q} =  \frac{\sum_{i \in Q} IIF_i}{||Q||}$
	\item $\overline{\Delta}_{\mathbf{TIF}^{Q}} =  \mathit{mean}(|\mathbf{TIF}^* - \mathbf{TIF}^{Q}|)$  \add{ho dei dubbi su questa notazione. la media è calcolata attraverso i valori di theta}. In alternativa a questa notazione: $\overline{\Delta}_{\mathbf{TIF}^{Q}} = \frac{|\mathbf{TIF}^* - \mathbf{TIF}^{Q}|}{||\theta||}$

\end{enumerate}

$Q_{bruto} = \arg \min_{Q \in \mathcal{Q}} \overline{\Delta}_{\mathbf{TIF}^{Q}}$

\section{Item Locating Algorithm}

\add{Siccome la filosofia di ILA e ISA è molto simile sarebbe carino trovare loro un nome comune e poi declinarle nelle loro specificità. ci pensiamo}

\textbf{Set up: }

$B$: Item bank

$Q^k \subset B$: Set of item indexes selected for inclusion in the STF up to iteration $k$

$\mathbf{TIF}^*$: TIF target

$D$: Item selected at each iteration

$\mathbf{PIF}_D^k = \frac{\sum_{i\in Q^k \cup \{D^k\}} IIF_i}{||Q^k \cup \{D\}||}$, provisional mean tif at iteration $k$, including the item selected in $D^k$

$||Q^k||$: cardinality of $Q^k$ at iteration $k$

At $k = 0$: $\mathbf{PIF}_D^0 = (0, 0, \ldots, 0)$, $Q^0 = \emptyset$, $D^0 = \emptyset$,

\begin{enumerate}
	\item $\theta_{target} := \arg \max |\mathbf{TIF}^* - \mathbf{PIF}_D^{k}|$
	\item $D^k = \arg \min_{i \in B\setminus Q^k} |\theta_{target} - b_i|$
	\item $\mathbf{PIF}_D^k = \frac{\sum_{i \in Q^k \cup \{D\}} IIF_i}{||Q^k \cup \{D\}||}$
	\item Termination Criterion: $|\mathbf{TIF}^* - \mathbf{PIF}_D^k| < |\mathbf{TIF}^* - \mathbf{TIF}^{k}|$: 
	\begin{itemize}
		\item TRUE: $k := k +1$, $Q^{k} = Q^{k-1} \cup \{D\}$, iterates 1-5 (\add{Ho scritto $k-1$ perché siccome ho scritto all'inizio che $k$ si aggiorna e diventa $k+1$ mi sembrava sensato})
		\item FALSE: The item in $D$ does not contribute to reduce the distance from the TIF target, hence: $Q_{ISA} = Q^k$
	\end{itemize}
\end{enumerate}

\section{Item Selecting Algorithm}

Same as ILA but based on the Item Information Functions.

\color{blue}

Set up same as ILA: 
$B$: Item bank

$Q^k \subset B$: Set of item indexes selected for inclusion in the STF up to iteration $k$

$\mathbf{TIF}^*$: TIF target

$D$: Item selected at each iteration

$\theta_{target}$: theta target selected at each iteration

$\mathbf{PIF}_D^k = \frac{\sum_{i\in Q^k \cup \{D\}} IIF_i}{||Q^k \cup \{D\}||}$, provisional mean tif at iteration $k$, including the item selected in $D$

$||Q^k \cup \{D\}||$: cardinality of $Q^k \cup \{D\}$ at iteration $k$

\normalcolor

At $k = 0$: $\mathbf{PIF}_D^0 = (0, 0, \ldots, 0)$, $Q^0 = \emptyset$, $D^0 = \emptyset$,

\begin{enumerate}
	\item $\theta_{target} := \arg \max |\mathbf{TIF}^* - \mathbf{PIF}_D^{k}|$
	\item $IIF_{i \in B \setminus Q^k} = a_i^2P(\theta_{target}, a_i, b_i)[1-P(\theta_{target}, a_i, b_i)]$
	\item $D := \arg \min_{i \in B\setminus Q^k} |\theta_{target} - IIF_i|$
	\item $\mathbf{PIF}_{D^k} = \frac{\sum_{i \in Q^k \cup \{D\}} IIF_i}{||Q^k \cup \{D\}||}$
	\item Termination Criterion: $|\mathbf{TIF}^* - \mathbf{PIF}_D^k| < |\mathbf{TIF}^* - \mathbf{TIF}^{k}|$: 
	\begin{itemize}
		\item TRUE: $k := k +1$, $Q^{k} = Q^{k-1} \cup \{D\}$, iterates 1-5 (\add{Ho scritto $k-1$ perché siccome ho scritto all'inizio che $k$ si aggiorna e diventa $k+1$ mi sembrava sensato})
		\item FALSE: The item in $D$ does not contribute to reduce the distance from the TIF target, hence: $Q_{ISA} = Q^k$
	\end{itemize}
\end{enumerate}

\section{Frank}

The setup is like the one of ILA and ISA:

$B$: Item bank

$Q^k$: set of items selected at iteration $k$

$D$: provisional item selected at each iteration

\add{$\mathbf{PIF}$: provisional mean tif}

At $k =0$, $\mathbf{PIF}^0 = (0, 0, \ldots, 0)$, $Q^0 = \emptyset$, iterate

\begin{enumerate}
	\item  $A^k = B \setminus Q^k$ (sets of available items at iteration $k$)
	\item $\forall i \in A^k$, $\mathbf{PIF}_{i}^k = \frac{\mathbf{TIF}^k + \mathbf{IIF}_{i}}{||Q^k||+1}$
	\item $D = \arg \min_{i \in A^k} |\mathbf{TIF}^* - \mathbf{PIF}_i^k|$
	\item Termination criterion: $|\mathbf{TIF}^* - \mathbf{PIF}_D^{k}| < |\mathbf{TIF}^* - \mathbf{TIF}^{k-1}|$: 
	\begin{itemize}
		\item  If true, $k := k + 1,$ $Q^{k} = Q^{k-1} \cup \{D\}$, restart from 1 \add{C'è il meno 1 per la stessa ragione scritta per ILA e ISA}

		\item  If false, stops, $Q_{Frank} = Q^k$

	\end{itemize}
\end{enumerate}

\end{document}

### 2024-10-18 the-good-the-bad-the-ugly.R

@@ -342,7 +342,7 @@ bruto = function(parameters,
   all_iifs = data.frame(do.call("cbind", all_iifs))
   colnames(all_iifs) = rownames(parameters)
   all_iifs = cbind(theta, all_iifs)
-  # ora deve calcolare tutte le possibili forme brevi da 2 a nrow(parameters)-1 sui parametri iniziali 
+  # ora deve calcolare tutte le possibili forme brevi da 1 a nrow(parameters)-1 sui parametri iniziali 
   my_comb = 1:(nrow(parameters)-1)
   # ora estraggo le varie terzine cinquine eccetera 
   item = NULL
@@ -515,8 +515,8 @@ isa = function(TIF, parameters, print = FALSE) {
                  the_graphs = mygraphs)
   return(results)
 }
-b <- runif(6, -3, 3)
-a <- runif(6, 0.9, 2)
+b <- runif(10, -3, 3)
+a <- runif(10, 0.9, 2)
 parameters = data.frame(a,b)
 rownames(parameters) = paste("item", rownames(parameters), sep = "_")
 theta = seq(-4,4, length.out = 1000)
@@ -527,8 +527,8 @@ resBruto = list()
 
 for (i in 1:iterations) {
   set.seed(i)
-  parameters[[i]] = data.frame(b = runif(6, -3, 3), 
-                               a = runif(6, 0.9, 2))
+  parameters[[i]] = data.frame(b = runif(9, -3, 3), 
+                               a = runif(9, 0.9, 2))
   rownames(parameters[[i]]) = paste("item", rownames(parameters[[i]]), sep = "_")
   resBruto[[i]] = bruto(parameters[[i]], theta, 
                         add_difficulty = runif(nrow(parameters[[i]]), -.2, .2),
@@ -567,7 +567,7 @@ for (i in 1:length(myfrank)) {
   item_select[i, "iila"] = paste(rownames(myila[[i]]$end)[order(rownames(myila[[i]]$end), decreasing = T)], collapse = " ")
 }
 # I saved the enrivorment till here 
-
+load("gbu-comparison-10items.RData")
 x = item_select[1,-3]
 
 
@@ -632,7 +632,7 @@ ic = ic_long %>%
             sd = sd(value))
 
 ggplot(ic, 
-       aes(x = name, y = mean, color = name)) + geom_point(shape = 5, size = 6) + ylim(0,6) + 
+       aes(x = name, y = mean, color = name)) + geom_point(shape = 5, size = 6) + ylim(0,8) + 
[…]

### 2024-10-18 functions.R
tif target function

@@ -1,0 +1,62 @@
+tif_target = function(parameters, 
+                      theta = seq(-3,3, legnth.out = 1000), 
+                      length_target = NULL,
+                      add_difficulty = NULL, 
+                      add_discriminativity = NULL, 
+                      seed = 999) {
+  set.seed(seed)
+  if (is.null(parameters)) {
+    stop("I need the item paramters, you fool!")
+  }
+  if (is.null(length_target)) {
+    length_target = sample(1:(nrow(parameters)-1), 1)
+  } else {
+    length_target = length_target
+  }
+  # tutte le possibili combinazioni di lunghezza N 
+  possible_comb = sample(nrow(parameters), length_target)
+  possible_comb = possible_comb[order(possible_comb)] 
+  # seleziona gli item della forma breve target
+  sel_items = parameters[possible_comb, ]
+  if (is.null(add_difficulty)) {
+    warning("Something will be randomly added to the difficulties of the items")
+    add_difficulty = sample(runif(1000, min = -0.2, 0.2), nrow(sel_items))
+  } else if (length(add_difficulty) > 1) {
+    add_difficulty = sample(add_difficulty, nrow(sel_items))
+  } 
+  if (is.null(add_discriminativity)) {
+    warning("Something will be randomly added to the discriminativities of the items")
+    add_discriminativity = sample(runif(1000, min =  -0.1, 0.1), nrow(sel_items))
+  } else if (length(add_discriminativity) > 1) {
+    add_discriminativity = sample(add_discriminativity, nrow(sel_items))
+  }
+  # modifica i paramatri degli item per poter creare la tif target 
+  sel_items$b = sel_items$b + add_difficulty
+  sel_items$a = sel_items$a + add_discriminativity
+  if (any(sel_items$a< 0) == TRUE ) {
+    sel_items[which(sel_items$a < 0), "a"] = sel_items[which(sel_items$a < 0), "a"]*-1
+    warning("There were negative discrimination parameters, I changed them!")
+  } else {
+    sel_items = sel_items 
+  }
+  # calcola la TIF TARGET MEDIA basata su qtheta = # calcola la TIF TARGET MEDIA basata su quegli item 
+  iifs_target <- item_info(sel_items,
+                           theta = theta)
+  target_info = data.frame(cbind(theta, do.call("cbind", iifs_target)))
+  colnames(target_info)[-1] = rownames(sel_items)
[…]

### 2024-10-18 functions.R
Update functions.R

@@ -56,7 +56,19 @@ tif_target = function(parameters,
   return(target_info)
 }
 
-bruto = function(parameters, tif_target){
-  
-}
+states<-expand.grid(rep(list(0:1),nrow(parameters)))
+states = states[-c(1,nrow(states)), ]
+states$sum = rowSums(states)
+states = states[order(states$sum), ]
+states$sum = NULL
 
+states[states == 0] <- NA 
+
+all_iifs = item_info(parameters, theta = theta)
+all_iifs = data.frame(do.call("cbind", all_iifs))
+colnames(all_iifs) = rownames(parameters)
+all_iifs = cbind(theta, all_iifs)
+
+# qui ci vuole il loop che prima itera nelle forme brevi per lunghezza (i) e poi si prende 
+# le j combinazioni dentro i 
+item_index = all_iifs[, which(!is.na(states[8,]))]

### 2024-10-29 paper/algorithms.tex
update

@@
 
-$ \theta = \{ x \in \mathbb{R} \,|\, \theta_{min} \leq x \leq \theta_{max} \}$: Latent trait levels, where $\theta_{min}$ is the minimum value of $\theta$ and $\theta_{max}$ is its maximum value \add{(non sono sicura della x)}
+%$ \theta = \{ x \in \mathbb{R} \,|\, \theta_{min} \leq x \leq \theta_{max} \}$: Latent trait levels, where $\theta_{min}$ is the minimum value of $\theta$ and $\theta_{max}$ is its maximum value \add{(non sono sicura della x)}
 
-$||\theta||$: cardinality of the latent trait
+%$||\theta||$: cardinality of the latent trait
+
+$||X||$: cardinality of $X$
 
@@
 \begin{enumerate}
-	\item $\mathbf{TIF}^{Q} =  \frac{\sum_{i \in Q} IIF_i}{||Q||}$
-	\item $\overline{\Delta}_{\mathbf{TIF}^{Q}} =  \mathit{mean}(|\mathbf{TIF}^* - \mathbf{TIF}^{Q}|)$  \add{ho dei dubbi su questa notazione.
+	\item $\mathbf{TIF}^{Q} =  \frac{\sum_{i \in Q} IIF_i}{||Q||}$, where $||Q||$ is the cardinality of set $Q$
+	\item $\overline{\Delta}_{\mathbf{TIF}^{Q}} =  \mathit{mean}(|\mathbf{TIF}^* - \mathbf{TIF}^{Q}|)$ %, that is the mean across all $\theta$ levels of the absolute difference between $TIF^*$ and $TIF^Q$ %\add{ho dei dubbi su questa notazione.
 la media è calcolata attraverso i valori di theta}.
@@
 $Q_{bruto} = \arg \min_{Q \in \mathcal{Q}} \overline{\Delta}_{\mathbf{TIF}^{Q}}$
+
+\add{spiegazione dell'algoritmo a parole}
 
@@
 
-$D$: Item selected at each iteration
+$i^*$: Item selected at each iteration
 
-$\mathbf{PIF}_D^k = \frac{\sum_{i\in Q^k \cup \{D^k\}} IIF_i}{||Q^k \cup \{D\}||}$, provisional mean tif at iteration $k$, including the item selected in $D^k$
+%$\mathbf{pTIF}^k = \frac{\sum_{i\in Q^{k-1} \cup \{i^*\}} IIF_i}{||Q^{k-1}||+1}$, mean tif at iteration $k$, including the item selected in $D$
 
@@
 
-At $k = 0$: $\mathbf{PIF}_D^0 = (0, 0, \ldots, 0)$, $Q^0 = \emptyset$, $D^0 = \emptyset$,
+At $k = 0$: $\mathbf{TIF}^0(\theta) = 0 \, \forall \theta$, $Q^0 = \emptyset$. For $k \geq 0$,
 
 \begin{enumerate}
-	\item $\theta_{target} := \arg \max |\mathbf{TIF}^* - \mathbf{PIF}_D^{k}|$
-	\item $D^k = \arg \min_{i \in B\setminus Q^k} |\theta_{target} - b_i|$
-	\item $\mathbf{PIF}_D^k = \frac{\sum_{i \in Q^k \cup \{D\}} IIF_i}{||Q^k \cup \{D\}||}$
-	\item Termination Criterion: $|\mathbf{TIF}^* - \mathbf{PIF}_D^k| < |\mathbf{TIF}^* - \mathbf{TIF}^{k}|$: 
+	\item $\theta_{target} := \arg \max |\mathbf{TIF}^* - \mathbf{TIF}^{k}|$
+	\item $i^* = \arg \min_{i \in B\setminus Q^{k}} |\theta_{target} - b_i|$
+	\item $\mathbf{pTIF}_{i^*} = \frac{TIF^k + IIF_{i^*}}{||Q^{k}|| + 1}$ %$\mathbf{pTIF}_{i^*}= \frac{\sum_{i \in Q^{k} \cup \{i^*\}} IIF_i}{||Q^{k} \cup \{i^*\}||}$ $=$ 
+	\item Termination Criterion: $|\mathbf{TIF}^* - \mathbf{pTIF}_{i^*}| \geq |\mathbf{TIF}^* - \mathbf{TIF}^{k}|$: 
 	\begin{itemize}
-		\item TRUE: $k := k +1$, $Q^{k} = Q^{k-1} \cup \{D\}$, iterates 1-5 (\add{Ho scritto $k-1$ perché siccome ho scritto all'inizio che $k$ si aggiorna e diventa $k+1$ mi sembrava sensato})
-		\item FALSE: The item in $D$ does not contribute to reduce the distance from the TIF target, hence: $Q_{ISA} = Q^k$
+		\item FALSE:  $Q^{k+1} = Q^{k} \cup \{i^*\}$, $TIF^{k+1} = pTIF_{i^*}$, iterates 1-4 
+		\item TRUE: Stop, %The item in $i^*$ does not contribute to reduce the distance from the TIF target, hence: 
+		$Q_{ILA} = Q^k$
 	\end{itemize}
@@
 
-$D$: Item selected at each iteration
+$i^*$: Item selected at each iteration
 
-$\theta_{target}$: theta target selected at each iteration
+%$\mathbf{pTIF}^k = \frac{\sum_{i\in Q^{k-1} \cup \{i^*\}} IIF_i}{||Q^{k-1}||+1}$, mean tif at iteration $k$, including the item selected in $D$
 
-$\mathbf{PIF}_D^k = \frac{\sum_{i\in Q^k \cup \{D\}} IIF_i}{||Q^k \cup \{D\}||}$, provisional mean tif at iteration $k$, including the item selected in $D$
-
-$||Q^k \cup \{D\}||$: cardinality of $Q^k \cup \{D\}$ at iteration $k$
+$||Q^k||$: cardinality of $Q^k$ at iteration $k$
 
@@
 
-At $k = 0$: $\mathbf{PIF}_D^0 = (0, 0, \ldots, 0)$, $Q^0 = \emptyset$, $D^0 = \emptyset$,
+At $k = 0$: $\mathbf{TIF}^0(\theta) = 0 \, \forall \theta$, $Q^0 = \emptyset$. For $k \geq 0$,
 
@@
 	\item $\theta_{target} := \arg \max |\mathbf{TIF}^* - \mathbf{PIF}_D^{k}|$
-	\item $IIF_{i \in B \setminus Q^k} = a_i^2P(\theta_{target}, a_i, b_i)[1-P(\theta_{target}, a_i, b_i)]$
-	\item $D := \arg \min_{i \in B\setminus Q^k} |\theta_{target} - IIF_i|$
-	\item $\mathbf{PIF}_{D^k} = \frac{\sum_{i \in Q^k \cup \{D\}} IIF_i}{||Q^k \cup \{D\}||}$
-	\item Termination Criterion: $|\mathbf{TIF}^* - \mathbf{PIF}_D^k| < |\mathbf{TIF}^* - \mathbf{TIF}^{k}|$: 
+%	\item $IIF_{i \in B \setminus Q^k}(\theta_{target}) = a_i^2P(\theta_{target}, a_i, b_i)[1-P(\theta_{target}, a_i, b_i)]$
+	\item $i^* := \arg \max_{i \in B\setminus Q^k} IIF_i(\theta_{target})$
+	\item $\mathbf{pTIF}_{i^*} = \frac{TIF^k + IIF_{i^*}}{||Q^{k}|| + 1}$
+	\item Termination Criterion: $|\mathbf{TIF}^* - \mathbf{PIF}_D^k| \geq |\mathbf{TIF}^* - \mathbf{TIF}^{k}|$: 
 	\begin{itemize}
@@
 
-$D$: provisional item selected at each iteration
+$i^*$: provisional item selected at each iteration
 
@@
 At $k =0$, $\mathbf{PIF}^0 = (0, 0, \ldots, 0)$, $Q^0 = \emptyset$, iterate
-
+\alert{gira il cirterio di terminazione e uniforma con gli altri}
 \begin{enumerate}
@@
 	\item $\forall i \in A^k$, $\mathbf{PIF}_{i}^k = \frac{\mathbf{TIF}^k + \mathbf{IIF}_{i}}{||Q^k||+1}$
-	\item $D = \arg \min_{i \in A^k} |\mathbf{TIF}^* - \mathbf{PIF}_i^k|$
-	\item Termination criterion: $|\mathbf{TIF}^* - \mathbf{PIF}_D^{k}| < |\mathbf{TIF}^* - \mathbf{TIF}^{k-1}|$: 
+	\item $D = \arg \min_{i \in A^k} |\mathbf{TIF}^* - \mathbf{PIF}_i|$
+	\item Termination criterion: $|\mathbf{TIF}^* - \mathbf{PIF}_D^{k}| < |\mathbf{TIF}^* - \mathbf{TIF}^{k}|$: 
 	\begin{itemize}

### 2024-10-29 all-algorithms.R

@@ -1,0 +1,208 @@
+# carico bruto 
+load("bruto-10item.RData")
+source("functions-new.R")
+library(tidyverse)
+parameters = list()
+replications = 100
+resFrank = list()
+frank_elapsed = NULL
+theta = seq(-4,4, length.out = 1500)
+resIla = list()
+ila_elapsed = NULL
+resIsa = list()
+isa_elapsed = NULL
+for (i in 1:replications) {
+  set.seed(i)
+  parameters[[i]] = data.frame(b = runif(10, -3, 3), 
+                               a = runif(10, 0.9, 2))
+  rownames(parameters[[i]]) = paste("item", rownames(parameters[[i]]), sep = "_")
+  target = tif_target(parameters[[i]], theta, 
+                      add_difficulty = runif(nrow(parameters[[i]]), -.2, .2), 
+                      add_discriminativity = runif(nrow(parameters[[i]]), -.2, .2), 
+                      seed = i)
+  # Frank
+  frank_start = Sys.time()
+  resFrank[[i]] = frank(parameters[[i]], target)
+  frank_end = Sys.time()
+  temp_elapsed = frank_end - frank_start
+  frank_elapsed = c(frank_elapsed, temp_elapsed)
+  # ILA 
+  ila_start = Sys.time()
+  resIla[[i]] = ila(parameters[[i]], target)
+  ila_end = Sys.time()
+  temp_elapsed = ila_end - ila_start
+  ila_elapsed = c(ila_elapsed, temp_elapsed)
+  # ISA 
+  isa_start = Sys.time()
+  resIsa[[i]] = isa(parameters[[i]], target)
+  isa_end = Sys.time()
+  temp_elapsed = isa_end - isa_start
+  isa_elapsed = c(isa_elapsed, temp_elapsed)
+}
+
+
+item_stf = data.frame(item_ila = character(replications), 
+                      n_ila = numeric(replications), 
+                      item_isa = character(replications), 
+                      n_isa = numeric(replications), 
+                      item_frank = character(replications), 
+                      n_frank = numeric(replications))
+for (i in 1:replications) {
+  item_stf[i, "item_ila"] = resIla[[i]]$q_ila
+  item_stf[i, "n_ila"] = unique(resIla[[i]]$stf$n_stf)
+  item_stf[i, "item_isa"] = resIsa[[i]]$q_isa
[…]

### 2024-10-29 bruto-sim.R

@@ -4,7 +4,7 @@ source("functions-new.R")
 parameters = list()
 replications = 100
 resBruto = list()
-bruto_elapsed = numeric(replications)
+bruto_elapsed = NULL
 theta = seq(-4,4, length.out = 1500)
 for (i in 1:replications) {
   set.seed(i)
@@ -18,22 +18,37 @@ for (i in 1:replications) {
   bruto_start = Sys.time()
   resBruto[[i]] = bruto(parameters[[i]], target)
   bruto_end = Sys.time()
-  bruto_elapsed[i] = c(bruto_elapsed, bruto_end - bruto_start)
+  temp_elapsed = bruto_end - bruto_start
+  bruto_elapsed = c(bruto_elapsed, temp_elapsed)
 }
-bruto_start = Sys.time()
-resBruto[[i]] = bruto(parameters[[i]], target)
-bruto_end = Sys.time()
-bruto_elapsed[i] = c(bruto_elapsed, bruto_end - bruto_start)
+# ho fatto casino e non ho i tempi per bruto se non dell'utlima replicazione
+bruto_end - bruto_start
+all_q_bruto = NULL
+temp = NULL
+for (i in 1:length(resBruto)) {
+  temp = resBruto[[i]]$q_bruto
+  temp$replication = i
+  temp$n_item_target = unique(resBruto[[i]]$all_infos$length_target)
+  temp$item_target = unique(resBruto[[i]]$all_infos$item_target)
+  all_q_bruto = rbind(all_q_bruto, temp)
+}
 
-parameters = data.frame(b = runif(10, -3, 3), 
-                             a = runif(10, 0.9, 2))
-target = tif_target(parameters, theta, 
-                    add_difficulty = runif(nrow(parameters), -.2, .2), 
-                    add_discriminativity = runif(nrow(parameters), -.2, .2), 
-                    seed = i)
-# provo FRANCO ---- 
-# all'inizio, guarda solo la distanza della IIF di ogni item dalla target 
-res_frank = frank(parameters, target)
+sum(all_q_bruto$n_item == all_q_bruto$n_item_target)
+sum(all_q_bruto$item == all_q_bruto$item_target)
 
-
+mydBruto = list()
+temp= NULL
+distance_bruto=NULL
+for (i in 1:nrow(all_q_bruto)) {
[…]

### 2024-10-29 functions-new.R

@@ -150,7 +150,7 @@ bruto = function(parameters, target = NULL) {
     my_target$distance = abs(my_target$mean_tif - my_target$mean_tif_stf)
     
     differences[i, "n_item"] = unique(my_target$n_item) 
-    differences[i, "item"]  =  item = unique(my_target$item) 
+    differences[i, "item"]  =  unique(my_target$item) 
     differences[i, "mean_distance"] = mean(my_target$distance)
     all_targets = rbind(all_targets, my_target) 
   }
@@ -222,6 +222,7 @@ ila = function(parameters, target) {
       distances_pif =c(distances_pif, mean(abs(my_target$mean_tif - pif))) 
       names(distances_pif)[length(distances_pif)] = paste("temp", i, sep = "_")
       # qua testa il criterio di uscita
+   #   browser()
       if (mean(abs(my_target$mean_tif - pif)) < mean(abs(my_target$mean_tif - my_target$tif_stf))) {
         token = TRUE
       } else {
@@ -233,11 +234,19 @@ ila = function(parameters, target) {
   }
   all_stfs = all_stfs[-1, ]
   all_items = sel_item
-  sel_item = all_items[-length(all_items)]
-  sel_item = sel_item[order(sel_item)]
+  if (length(sel_item) == 1) {
+    sel_item = sel_item
+    warning("Apparetly there were no items able to minimize the distance")
+  } else {
+    sel_item = all_items[-length(all_items)] 
+  }
+  temp_item = sel_item
+  temp_item = as.numeric(gsub("item_", "", temp_item))
+  temp_item = temp_item[order(temp_item)]
+  sel_item = paste("item", temp_item, sep = "_")
   my_target$n_stf = length(sel_item)
   my_target$item_stf = paste(sel_item, collapse = " ")
-  results = list(q_ila = sel_item, 
+  results = list(q_ila = paste(sel_item, collapse = " "), 
                  all_items = all_items,
                  stf = my_target, 
                  distances_tif = distances_tif, 
@@ -257,6 +266,7 @@ isa = function(parameters, target) {
   token = TRUE
   distances_tif = NULL
   distances_pif = NULL
+ # browser()
   all_stfs = data.frame(matrix(nrow = 1, ncol = 3))
   colnames(all_stfs) = c("nitems", "items", "pif")
   for (i in 0:nrow(parameters)) {
@@ -273,7 +283,7 @@ isa = function(parameters, target) {
[…]

### 2024-11-12 paper/algorithms.tex
update

@@
 
-\add{spiegazione dell'algoritmo a parole}
+Bruto is a brute force algorithm that aims at the selection of best combination of items to recreate a given TIF target by comparing the TIF target with the TIF obtained with all the possible combinations of items of different lengths that are obtainable from an item bank $B$.
+The total number of item combinations of different lengths $\mathcal{Q}$ is equal to the power set of the item bank minus the empty set and the full set of items.
+For each item combination $Q \in \mathcal{Q}$, the mean TIF $TIF^Q$ is computed, and is compared against the TIF target.
+Specifically, the average distance between the TIF target and $TIF^Q$ is computed and the item combination selected by Bruto is the one among all item combinations that allows fro minimizing the distance between $TIF^*$ and $TIF^Q$.
 
@@
 
-$Q^k \subset B$: Set of item indexes selected for inclusion in the STF up to iteration $k$
+$Q^k \subset B$: Set of items selected for inclusion in the STF up to iteration $k$
 
@@
 
-$||Q^k||$: cardinality of $Q^k$ at iteration $k$
+%$||Q^k||$: cardinality of $Q^k$ at iteration $k$
 
-At $k = 0$: $\mathbf{TIF}^0(\theta) = 0 \, \forall \theta$, $Q^0 = \emptyset$. For $k \geq 0$,
+At $k = 0$: $TIF^0(\theta) = 0 \, \forall \theta$, $Q^0 = \emptyset$. For $k \geq 0$,
 
@@
 \end{enumerate}
+
+ILA selects the best combination of items to approximate a pre-defined TIF target by iteratively and forwardly searching for the item that allows for minimizing the distance from a specific $\theta$ target.
+The $\theta$ target is updated at each iteration of the procedure as the point on the latent trait for which the greatest distance between the TIF target and the provisional TIF ($pTIF$) obtained with the last selected item is observed.
+ILA iterates through $k$ until the termination criterion is met, that is, when the distance between the TIF target and the $pTIF$ with the last selected item is greater or equal to the distance between the TIF target and the TIF obtained from the items in $Q^k$.
+If the termination criterion is false, the last selected item can be added in $Q$ since it is useful to reduce the distance between the TIF target and the TIF of the STF.
+Otherwise, the procedure ends and the final item selection does not include the last selected item, since it does not contribute in reducing the distance from the TIF target.
 
@@
 
-$||Q^k||$: cardinality of $Q^k$ at iteration $k$
+%$||Q^k||$: cardinality of $Q^k$ at iteration $k$
 
@@
 
-At $k = 0$: $\mathbf{TIF}^0(\theta) = 0 \, \forall \theta$, $Q^0 = \emptyset$. For $k \geq 0$,
+At $k = 0$: $TIF^0(\theta) = 0 \, \forall \theta$, $Q^0 = \emptyset$. For $k \geq 0$,
 
 \begin{enumerate}
-	\item $\theta_{target} := \arg \max |\mathbf{TIF}^* - \mathbf{PIF}_D^{k}|$
+	\item $\theta_{target} := \arg \max |\mathbf{TIF}^* - \mathbf{TIF}^{k}|$
 %	\item $IIF_{i \in B \setminus Q^k}(\theta_{target}) = a_i^2P(\theta_{target}, a_i, b_i)[1-P(\theta_{target}, a_i, b_i)]$
@@
 	\begin{itemize}
-		\item TRUE: $k := k +1$, $Q^{k} = Q^{k-1} \cup \{D\}$, iterates 1-5 (\add{Ho scritto $k-1$ perché siccome ho scritto all'inizio che $k$ si aggiorna e diventa $k+1$ mi sembrava sensato})
-		\item FALSE: The item in $D$ does not contribute to reduce the distance from the TIF target, hence: $Q_{ISA} = Q^k$
+		\item FALSE:  $Q^{k+1} = Q^{k} \cup \{i^*\}$, $TIF^{k+1} = pTIF_{i^*}$, iterates 1-4 
+\item TRUE: Stop, %The item in $i^*$ does not contribute to reduce the distance from the TIF target, hence: 
+$Q_{ISA} = Q^k$
 	\end{itemize}
@@
 
-At $k =0$, $\mathbf{PIF}^0 = (0, 0, \ldots, 0)$, $Q^0 = \emptyset$, iterate
-\alert{gira il cirterio di terminazione e uniforma con gli altri}
+At $k = 0$: $TIF^0(\theta) = 0 \, \forall \theta$, $Q^0 = \emptyset$. For $k \geq 0$,
+
 \begin{enumerate}
@@
 	\item $D = \arg \min_{i \in A^k} |\mathbf{TIF}^* - \mathbf{PIF}_i|$
-	\item Termination criterion: $|\mathbf{TIF}^* - \mathbf{PIF}_D^{k}| < |\mathbf{TIF}^* - \mathbf{TIF}^{k}|$: 
+	\item Termination criterion: $|\mathbf{TIF}^* - \mathbf{PIF}_D^{k}| \geq |\mathbf{TIF}^* - \mathbf{TIF}^{k}|$: 
 	\begin{itemize}
-		\item  If true, $k := k + 1,$ $Q^{k} = Q^{k-1} \cup \{D\}$, restart from 1 \add{C'è il meno 1 per la stessa ragione scritta per ILA e ISA}
-
-		\item  If false, stops, $Q_{Frank} = Q^k$
+		\item FALSE:  $Q^{k+1} = Q^{k} \cup \{i^*\}$, $TIF^{k+1} = pTIF_{i^*}$, iterates 1-4 
+\item TRUE: Stop, %The item in $i^*$ does not contribute to reduce the distance from the TIF target, hence: 
+$Q_{Frank} = Q^k$
 

### 2024-11-12 all-algorithms.R

@@ -229,18 +229,33 @@ bruto_acc$algo = "bruto"
 all_acc = rbind(ila_acc, isa_acc, frank_acc, bruto_acc)
 #all_acc$algo = rep(c("ila", "isa", "frank", "bruto"), each = 100)
 all_acc$replication = the_distances$replica
-ggplot(all_acc, 
+ggplot(all_acc[!all_acc$algo %in% "bruto",], 
        aes(x = reorder(replication, accuracy), y = accuracy, 
            shape = algo, 
-           color = algo)) + geom_point()
+           color = algo)) + geom_point(alpha = .8)
+
+ggplot(all_acc[!all_acc$algo %in% "bruto",], 
+       aes(x = algo, y = accuracy, 
+           shape = algo, 
+           color = algo)) +geom_boxplot()
 ggplot(all_acc, 
        aes(x = reorder(replication, specificity11), y = specificity11, 
            shape = algo, 
            color = algo)) + geom_point()
+ggplot(all_acc[!all_acc$algo %in% "bruto",], 
+       aes(x = algo, y = specificity11, 
+           shape = algo, 
+           color = algo)) +geom_boxplot()
+
 ggplot(all_acc, 
        aes(x = reorder(replication, sensitivity00), y = sensitivity00, 
            shape = algo, 
            color = algo)) + geom_point()
+ggplot(all_acc[!all_acc$algo %in% "bruto",], 
+       aes(x = algo, y = sensitivity00, 
+           shape = algo, 
+           color = algo)) +geom_boxplot()
+
 all_acc %>%  
   group_by(algo) %>%  
   summarise(mean_acc = mean(accuracy), sd_acc = sd(accuracy), 

### 2024-11-12 functions-new.R

@@ -7,16 +7,22 @@ IRT <- function(theta, a = 1, b = 0, c = 0,e = 1) {
   return(y)
 }
 # calcola l'IIF per un item specifico
-i_info <- function(b, a=1,c=0, theta = seq(-5,5,length.out=1000)){
-  Ii = a^2*IRT(theta, b = b, a = a )*(1- IRT(theta, b = b, a = a ))
+i_info <- function(b, a=1,c=0, e= 1,  theta = seq(-5,5,length.out=1000)){
+  Ii = (a^2)*IRT(theta, b = b, a = a, e = e )*(1- IRT(theta, b = b, a = a, e = e ))
   return(Ii)
 }
 # calcola l'IIF di tutti gli item e restituisce in una lista di lunghezza ugaule a tutti 
 # gli item per cui si è calcolata l'IIF
 item_info <- function(ipar, theta = seq(-5,5,length.out=1000)){
   item <- NULL
-  for(i in 1:nrow(ipar)){
-    item[[i]] <- i_info(ipar[i, "b"],ipar[i, "a"], theta = theta)
+  if (any(colnames(ipar) == "e")) {
+    for(i in 1:nrow(ipar)){
+      item[[i]] <- i_info(b = ipar[i, "b"],a = ipar[i, "a"], e = ipar[i, "e"], theta = theta)
+    } 
+  } else {
+    for(i in 1:nrow(ipar)){
+      item[[i]] <- i_info(b = ipar[i, "b"],a = ipar[i, "a"], theta = theta)
+    }
   }
   item = data.frame(do.call("cbind", item))
   colnames(item) = rownames(ipar)
@@ -493,7 +499,9 @@ delta = function(all_q, nitems = NULL, replica = 1,
   }
 return(distance)
 }
-performance = function(distance_data, target_items = "target_items", stf_items = "stf_items") {
+performance = function(distance_data, 
+                       target_items = "target_items", 
+                       stf_items = "stf_items") {
   myT = table(distance_data[, target_items], distance_data[,stf_items])
   if(sum(dim(myT)) < 4) {
     accuracy = 0

### 2024-11-12 tired.R

@@ -1,0 +1,63 @@
+# i'm just so tired, please have mercy (Cit. anyone during the administration of the MMPI)
+library(tidyverse)
+source("functions-new.R")
+
+# item bank, 11 items with their diffiuclty and discirmianton parameters
+set.seed(1312)
+q = data.frame(b = runif(12, -3, 3), 
+               a = runif(12, .9, 2))
+rownames(q) = paste("item", 1:nrow(q), sep ="_")
+q
+theta = seq(-4, 4, length.out = 1000)
+
+plot(theta, IRT(theta, b= q[1, "b"], a = q[1, "a"]), type = "l")
+for (i in 2:nrow(q)) {
+  lines(theta, IRT(theta, b= q[i, "b"], a = q[i, "a"]), type = "l")
+}
+
+all_iif = item_info(q, theta)
+tif = data.frame(theta, tif = rowSums(all_iif), 
+                 mean_tif = rowMeans(all_iif))
+plot(theta, tif$tif, type = "l")
+# questa è la tif dell'item banck senza l'influenza della stanchezza 
+
+# ci sono diverse possibiliutà per definire la stanchezza, ovvero per capire se inizia a rompere le apll dal primo item, dal secondo 
+# item eccetera. 
+# forse la cosa più appropiata sarebbe una funzione esponenziale in funzione 
+# del numero di item  ma questo è un problema per la me del futuro 
+IRT(theta, b = q[1, "b"], a = q[1, "a"])
+IRT(theta[1], b = q[1, "b"], a = q[1, "a"], e = .99)
+plot(theta,  IRT(theta, b = q[1, "b"], a = q[1, "a"]), type = "l")
+e = seq(.99, .90, by = -.02)
+ for (i in 1:length(e)) {
+   lines(theta, IRT(theta, b = q[1, "b"], a = q[1, "a"], e = e[i]), type = "l", col = i)
+ }
+abline(a = .5, b = 0, lty = 2, lwd = 3, col = "red")
+abline(v = q[1, "b"], lty = 2, lwd = 3, col = "red")
+
+seq(1, .90, by = -0.03)
+q$e = rep(seq(1, .90, by = -0.03), each = 3)
+# stessi item di prima ma con la stanchezza 
+
+plot(theta, IRT(theta, b= q[1, "b"], a = q[1, "a"], e = q[1, "e"]), 
[…]

### 2025-02-04 all-algorithms.R
tired-estimate

@@ -23,6 +23,7 @@ for (i in 1:replications) {
   #                     add_discriminativity = runif(nrow(parameters[[i]]), -.2, .2), 
   #                     seed = i)
   # Frank
+  parameters[[i]][, c("c", "e")] = c(rep(0,11), rep(1,11))
   frank_start = Sys.time()
   resFrank[[i]] = frank(parameters[[i]], target[[i]])
   frank_end = Sys.time()
@@ -45,6 +46,19 @@ for (i in 1:replications) {
 mean(frank_elapsed)
 mean(ila_elapsed)
 mean(isa_elapsed)
+mean(bruto_elapsed)
+
+elapsed = data.frame(bruto_elapsed, ila_elapsed, isa_elapsed, frank_elapsed)
+elapsed$iteration = 1:nrow(elapsed)
+
+elapsed = pivot_longer(elapsed, cols = !iteration)
+
+elapsed %>% 
+  group_by(name) %>% 
+  summarise(min = round(min(value), 3), 
+            mean = round(mean(value), 3), 
+            sd = round(sd(value), 3), 
+            max = round(max(value), 3))
 
 item_stf = data.frame(item_ila = character(replications), 
                       n_ila = numeric(replications), 
@@ -82,15 +96,17 @@ all_item_stf = item_stf
 # add rank to bruto: it means the distance of teh STF developed with Bruto from the target
 # io sarei dell'idea di arrontarder a 4 decimali
 for (i in 1:length(resBruto)) {
-  resBruto[[i]]$differences$rank = rank(resBruto[[i]]$differences$mean_distance, 
+  resBruto[[i]]$differences$rank = rank(round(resBruto[[i]]$differences$mean_distance,6), 
                                         ties = "min")
 }
+
 
 # faccio una sottoselezione solo di quelle forme brevi che sono effettivamnente riuscite 
 item_stf = all_item_stf[all_item_stf$stf_not_found_isa == F,]
 apply(item_stf[, c("n_frank", "n_ila", "n_isa")], 2, max)
 apply(item_stf[, c("n_frank", "n_ila", "n_isa")], 2, min)
 apply(item_stf[, c("n_frank", "n_ila", "n_isa")], 2, mean)
+apply(item_stf[, c("n_frank", "n_ila", "n_isa")], 2, sd)
 
 rank_ila = NULL
 rank_isa = NULL
[…]

### 2025-02-04 functions-new.R

@@ -243,7 +243,7 @@ ila = function(parameters, target) {
         temp_pif = data.frame(nitems = ncol(selected_iifs), 
                               items = paste(colnames(selected_iifs), collapse = " "), 
                               pif = pif)
-        all_stfs = rbind(all_stfs, mypif)
+        all_stfs = rbind(all_stfs, temp_pif)
       }
       parameters[index_item, ] = NA
       # contiene le distanze tra la target e la tif stf (quelle che vanno confrontate con la pif)
@@ -351,7 +351,7 @@ isa = function(parameters, target) {
         temp_pif = data.frame(nitems = ncol(selected_iifs), 
                               items = paste(colnames(selected_iifs), collapse = " "), 
                               pif = pif)
-        all_stfs = rbind(all_stfs, mypif)
+        all_stfs = rbind(all_stfs, temp_pif)
       }
       parameters[index_item, ] = NA
       # contiene le distanze tra la target e la tif stf (quelle che vanno confrontate con la pif)
@@ -434,6 +434,7 @@ isa = function(parameters, target) {
 }
 # Frank -------
 frank = function(parameters, target) {
+  theta = target$theta
   all_iifs = item_info(parameters, theta)
   token = TRUE
   while (token == TRUE) {

### 2025-02-04 tired.R

@@ -1,39 +1,406 @@
 # i'm just so tired, please have mercy (Cit. anyone during the administration of the MMPI)
 library(tidyverse)
 source("functions-new.R")
+rbinom(1000,1, IRT(theta = 3, a = 1, b = 3))
 
-# b = 1
-# a = 2
-# c = 0
-# e = .95
-# i_info(b,a,c,1, theta = seq(-3,3))
-# i_info1(b,a,.20,1, theta = seq(-3,3))
-# 
-# plot(seq(-3,3, length.out = 100), 
-#      i_info1(b,a,c,1, theta = seq(-3,3, length.out = 100)), type = "l")
-# lines(seq(-3,3, length.out = 100), 
-#      i_info1(b,a,0,.95, theta = seq(-3,3, length.out = 100)), type = "l", col = "red")
-
-
-# item bank, 12 items with their diffiuclty and discirmianton parameters
-set.seed(1312)
-q = data.frame(b = runif(12, -3, 3), 
-               a = runif(12, .9, 2), 
-               c = rep(0,12), e= rep(1, 12))
-rownames(q) = paste("item", 1:nrow(q), sep ="_")
-q
-theta = seq(-4, 4, length.out = 1000)
-# ICC dellìtem bank senza errore 
-plot(theta, IRT(theta, b= q[1, "b"], a = q[1, "a"]), type = "l")
-for (i in 2:nrow(q)) {
-  lines(theta, IRT(theta, b= q[i, "b"], a = q[i, "a"]), type = "l", col = i)
+nellie = function(parameters, target, speed = 0.01) {
+  if (is.null(target)) {
+    stop("I can't work without a target :)")
+  }
+  theta = target$theta
+  all_iifs = item_info(parameters, theta)
+  my_target = target
+  sel_item = NULL
+  token = TRUE
+  distances_tif = NULL
+  distances_pif = NULL
+  original_parameters = parameters
+  all_stfs = data.frame(matrix(nrow = 1, ncol = 3))
+  colnames(all_stfs) = c("nitems", "items", "pif")
+ # browser()
+  for (i in 0:nrow(parameters)) {
+    if (token == TRUE & i < nrow(parameters)) {
+      if (i == 0) {
+        my_target$tif_stf = 0
+      } else {
+        my_target$tif_stf = pif
+      }
+      my_target$distance = abs(my_target$mean_tif - my_target$tif_stf) 
+      
+      parameters$temp_theta = my_target[which(my_target$distance == max(my_target$distance)), "theta"]
[…]

### 2025-02-04 tiredEstimate.R

@@ -1,0 +1,365 @@
+# provo a simulare tutto da zero sulla stanchezza, facendo sia la selezione 
+# degli item sia i bias dei theta 
+library(TAM)
+library(tidyverse)
+source("functions-new.R")
+# riscrivo frank per la stanchezza 
+leon = function(parameters, target, speed = 0.01) {
+  theta = target$theta
+  all_iifs = item_info(parameters, theta)
+  original_parameters = parameters
+  start_e = parameters$e
+  token = TRUE
+  mod_e = 1
+  j = 0
+  while (token == TRUE) {
+    j = j +1
+    # qui potrei fare che itero per tutte le colonne che non sono NA del mio dataframe di item 
+    # creo gli indici degli item nell'insieme A (gli available items)
+    if (all(which(is.na(parameters[, 1])) == FALSE) ) {
+      item_indexes = 1:nrow(parameters)
+      iif_stf = numeric(length(target$theta))
+    } else {
+      item_indexes = which(!is.na(parameters[,1]))
+    }
+    # adesso il ciclo for itera negli item indexes e calcola la PIF
+    difference = rep(NA, nrow(parameters))
+    for (i in item_indexes) {
+      if (length(item_indexes) == nrow(parameters)) {
+        pif = data.frame(all_iifs[,i]) 
+      } else {
+        # qui devo mdoficare all_iifs nel senso che le devo ricalcolare 
+        # però considerando la stanchezza
+        # so dire esattamente 
+        # CAMBIA QUI METTENDO CHE PESCA LA E DEGLI ITEM ORIGIANLI IN ABSE ALLA LORO POSIZIONE DI SOMMNISTRAZIONE 
+        # PER CUI ALL'I-ESIMA ITERAZIONE PRENDE LA STANCHEZZA DELL'ITEM SOMMINISTRATO PER I-ESIMO
+       # original_parameters$e = exp(-speed*(ncol(iif_stf)+1))
+        original_parameters$e = start_e[j]
+        # qui ora si può ottimizzare 
+        all_iifs = item_info(original_parameters, theta)
+        pif = data.frame(cbind(iif_stf, all_iifs[,i]))
+        pif = data.frame(rowMeans(pif))
+      }
+      difference[i] = mean(abs(target$mean_tif - pif)[,1])  
+      # qui scelgo un item temporaneo che è quello con la distanza minima
+    }
[…]

### 2025-02-05 paper/algorithms.tex
cose

--- 2024-10-18 paper/algorithms.tex
@@
 
-\tikzstyle{startstop} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black]
-\tikzstyle{process} = [rectangle, minimum width=3cm, minimum height=1cm, text centered, draw=black]
-\tikzstyle{decision} = [diamond, minimum width=1.5cm, minimum height=0.5cm, text centered, draw=black]
+\tikzstyle{startstop} = [rectangle, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=red!30]
+\tikzstyle{process} = [rectangle, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=orange!30]
+\tikzstyle{decision} = [diamond, minimum width=3cm, minimum height=1cm, text centered, draw=black, fill=green!30]
 \tikzstyle{arrow} = [thick,->,>=stealth]
+
+% formattazione per APA 7
+
+\raggedbottom
+\titleformat*{\section}{\bfseries\centering}
+\titleformat*{\subsection}{\bfseries\flushleft}
+\titleformat*{\subsubsection}{\bfseries\itshape\flushleft}
+\titleformat*{\paragraph}{\bfseries}
+\titleformat*{\subparagraph}{\large\bfseries}
 
@@
 
-\maketitle
+\vspace*{10mm}
+\begin{center}
+	\begin{LARGE}
+	The Good, the Bad, and the Ugly: \\ New Item Response Theory based algorithms for the development of short test forms
+	\end{LARGE}
+
+	\vspace{5mm}
+	\begin{large}
+%		Ottavia M. Epifania, Pasquale Anselmi, and Egidio Robusto \\ 
+%		Department of Philosophy, Sociology, Education, and Applied Psychology, University of Padova
+	\end{large}
+\end{center}
+\vspace{15mm}
+\begin{center}
+	\textbf{Author Note}
+\end{center}
+\begin{small}
+
+%	Ottavia M. Epifania \includegraphics[width=0.06\linewidth]{orcid.png} https://orcid.org/0000-0001-8552-568X
+%	
+%	Pasquale Anselmi \includegraphics[width=0.06\linewidth]{orcid.png} https://orcid.org/0000-0003-2982-7178 
+%	
+%	Egidio Robusto \includegraphics[width=0.06\linewidth]{orcid.png} https://orcid.org/0000-0002-7583-2587
+
+	The authors have no conflict of interest to disclose.
+
+	Correspondence concerning this article should be addressed to: Ottavia M. Epifania, Department of Philosophy, Sociology, Education, and Applied Psychology, Via Venezia 14, Padova, Italy.
+	E-Mail: ottavia.epifania@unipd.it \\
+\end{small}
+
+\vfill
+
+%\end{document}
+
+\newpage
 
 \begin{abstract}
+	\onehalfspacing
+This manuscript presents Item Response Theory-based algorithms for the development of short test forms (STFs) from full-length tests.
+All algorithms aim at minimizing both the number of items included in the STF and the minimum average distance from a test information target that describes the desired characteristics of the STF, denoted as test information function target (TIF-target).
+The algorithms differ according to the method used for the item inclusion in the STF at each iteration, while they share the same termination criterion.
+The item selection is based on the ability of each item to reduce the distance from the TIF-target considering either one specific latent trait level defined at each iteration or the entire latent trait level.
+The algorithms stop when the last selected item does not contribute in reducing the distance from the TIF-target. 
+The performance of the algorithms is compared against that of a brute force algorithm, which selects the item combination best able to reduce the distance from the TIF-target among all the possible item combinations.
+Results of a simulation study show that the algorithm that selects the items according to their ability of reducing the distance from the TIF-target throughout the entire latent trait outperforms the other algorithms.
+Limitations of the study and future lines of research are discussed.
 
+\textbf{Keywords:} Item Response Theory; Information Functions; Algorithms; Short Test Forms
 \end{abstract}
@@
 
-\section{Bruto}
+\newpage
+\begin{center}
+	\textbf{The Good, the Bad, and the Ugly: New Item Response Theory-Based Algorithms for the Development of Short Test Forms}
+\end{center}
 
-$ \theta = \{ x \in \mathbb{R} \,|\, \theta_{min} \leq x \leq \theta_{max} \}$: Latent trait levels, where $\theta_{min}$ is the minimum value of $\theta$ and $\theta_{max}$ is its maximum value \add{(non sono sicura della x)}
+%Since Item Response Theory (IRT) provides detailed information on the measurement precision of each item across different levels of the latent trait, it constitutes an ideal framework for test development \cite<e.g.,>{baker2017, van1987absolute}.
+Moreover, it allows for the development of tests or short test forms  (STFs) from an item bank or from an existing test, respectively.
+Item Response Theory (IRT) offers detailed insights into the measurement precision of individual items across varying levels of the latent trait, making it an ideal framework for test development \cite<e.g.,>{baker2017, van1987absolute}.
+By leveraging its robust analytical capabilities, IRT facilitates the construction of tailored assessments, such as tests designed from item banks or the derivation of short test forms (STFs) from existing assessments.
+This flexibility ensures that tests can be optimized for specific purposes, populations, or contexts while maintaining precision and validity.
+The STFs developed from tests can be classified into two main types.
+ On the one hand, there are the adaptive STFs developed within the computerized adaptive testing framework, which tailor the item administration to maximize measurement precision for each respondent \cite<e.g.,>{magis}.
+Therefore, the items may differ from one respondent to another.
+On the other hand, static STFs are composed of the same subset of items, which is chosen to maximize the measurement precision across all the administered respondents.
+%The information on the measurement precision of each item can be exploited for the creation of ad-hoc STFs by selecting only those items that most precisely measure specific levels of the latent trait, in line with the aim of the assessment.
+This article presents three new IRT-based algorithms for the development of STFs. 
+All algorithms attempt at recreating the desired characteristics of a test, as defined through a target information function, by iteratively selecting the items that reduce as much as possible the distance between the information function of the STF and the target one.
+In this application, the focus is on the development of static STFs from full-length tests, although the introduced algorithms also apply to the development of static tests from item banks.
+%The methods used for selecting the items at each iteration differentiate the algorithms.
+Specifically, they select the items according to the item's ability of reducing the distance from the TIF-target considering either a single latent trait level defined at each iteration or the entire latent trait.
 
-$||\theta||$: cardinality of the latent trait
+In common IRT procedures \cite<e.g.,>{chiesi, colledani2018, silvia}, the items  are selected for inclusion in the STF according to their measurement precision with respect to different levels of the latent trait that are of interest for the assessment.
+To pursue this aim, the information functions of all the items of the full-length test are inspected, and the items with the information functions best able to comply with the desired characteristics of the STF are selected for inclusion.
+Although this procedure offers high degrees of freedom (e.g., the number of items in the STF can be not specified in advance), it strongly relies on the expertise and subjectivity of the researchers, which lead to issues related to
+replicability.   
+Moreover, since this procedure is not automated, it might be particularly demanding, especially if the full-length test comprises many items. 
+Recently, \citeA{pauci} introduced a procedure, denoted as $\theta$-target procedure, which integrates the principles of computerized adaptive testing (i.e., tailoring the item administration to specific latent trait levels) for the development of static STFs from full-length tests, thus allowing for its automation.
+The newly introduced procedure grounds the item selection on the measurement precision of each item in the full-length test with respect to specific latent trait levels of interest, denoted as $\theta$ targets, which are defined a priori according to the aim of the assessment.
+The procedure selects an optimal item (i.e., the item that provides the highest measurement precision) for each of the identified $\theta$ targets. 
+Despite being promising, the discrete definition of the $\theta$ targets raises different issues that cannot be ignored. 
+Firstly, since an optimal item is selected for each of the $\theta$ targets, the actual number of $\theta$ targets determines the number of items included in the STFs. 
+As such, the more the STF is meant to precisely measure larger regions of the latent trait, the larger the number of selected $\theta$ targets and the larger the number of items that need to be included in the STF.
+Moreover, the functioning of the $\theta$-target procedure strongly depends on the availability in the item bank of informative items with respect to the defined $\theta$ targets.
+If the item bank does not contain informative items with respect to one or more $\theta$ targets, sub-optimal items might be included in the final item selection.
+As such, the STF might contain more items than actually needed or items that might not appropriately assess the levels of interest.
+Finally,  the $\theta$ targets are defined as discrete values to recreate a sort of ``overall'' information function of the STF, which is continuous by nature. 
+%The $\theta_{target}$s are defined a priori according to the specific aim with which the STF is developed.
+For instance, if the aim of the STF is to discriminate respondents below and above a certain cut-off (e.g., clinical diagnostic tests) the $\theta$s are defined around the cut-off point, such that only the most informative items for that region of the latent trait are included in the STF.
+Otherwise, if the aim is to maximize the information across the entire latent trait, the $\theta_{target}$s can be equally spread along the latent trait continuum.
+%Typically, the development of STF relies on the expertise of the researchers, in that that the items are manually chosen according to the measurement precision that they provide to address the final measurement precision one wants to obtain for the STF.
+While such a procedure provides large degrees of freedom in terms of item selection and does not require the definition of the number of items a priori, it strongly relies on the expertise of the researcher and might be at risk of not being reproducible.
+%While both types of STFs are based on the same principle, they differ in their focus.
+Adaptive STFs adjust to the individual respondent’s characteristics, maximizing measurement precision for that specific person.
+In contrast, static STFs aim to achieve overall precision across the entire group of respondents.
+Both approaches leverage the information from IRT models regarding the measurement precision of each item at various levels of the latent trait.
+In this light, it might be more convenient to directly refer to a continuous function describing the desired characteristics of the STF by means of a target information function to be recreated with the final selection of items in the STF \cite<e.g.,>{lordTif}.
+The specification of a TIF-target allows for shifting the focus on different regions of the latent trait, hence STFs addressing different aims can be developed. 
+\begin{figure}
+	\centering
+	\begin{subfigure}{0.45\linewidth}
+		\includegraphics[width=\textwidth]{img/target_n}
+		\caption{}
+		\label{fig:targetN}
+	\end{subfigure}
+	\begin{subfigure}{0.45\linewidth}
+		\includegraphics[width=\textwidth]{img/target_sk}
+		\caption{}
+		\label{fig:targetSK}
+	\end{subfigure}
+\caption{Examples of target information functions.
+Panel \ref{fig:targetN} illustrates a target information function aimed at obtaining a good measurement precision of latent trait levels between $-2$ and $2$.
+Panel \ref{fig:targetSK} illustrates a target information function focused on a specific level of the latent trait, $\theta = -2$.}
+	\label{fig:tartge-examples}
+\end{figure}
+For instance, Figure \ref{fig:tartge-examples} illustrates two TIF-targets, which have been specified for obtaining either  precise measurements of different levels of the latent trait. 
+Figure \ref{fig:targetN} illustrates a TIF target for obtaining a precise measurement of the $\theta$ levels between $-2$ and $2$.
+Figure \ref{fig:targetSK} illustrates a TIF target highly informative for $\theta$ levels around $-2$ standard deviation below the average population mean of 0 \cite<a cut off at 2 standard deviations below the population mean is a criterion sometimes used in diagnostic tests, see e.g., >{balboni, tasse2016}.
+%Specifically, Figure \ref{fig:targetN} depicts the TIF-target that allows for obtaining precise measurements across almost the entire latent trait, with a particular focus on the regions between $-2$ and $2$.
+Such a TIF-target might be employed when developing STFs for the assessment of psychological constructs that are normally distributed among the general population (e.g., intelligence).
+On the other hand, Figure \ref{fig:targetSK} depicts a TIF-target that is consistent for the development of a diagnostic STF, since its focus is on a specific $\theta$ level
 
-$\forall Q \in\mathcal{Q} = 2^B \setminus \{\emptyset, B\}$,
+\normalcolor
+Although the specification of the desired characteristics of the STF through a target information function is reasonable, its actual definition might not be straightforward.
+While there might be an idea concerning the shape of the target information function (i.e., the regions of the latent trait on which the highest measurement precision is desired), the definition of its height (i.e., the amount of information for different levels of the latent trait) might be troublesome \cite{van1989relative}.
+In this sense, if both the shape and height of the target information function can be defined, the test or STF development is performed with the idea of recreating an \emph{absolute information} \cite{stocking, van1987absolute}.
+Conversely, if only the shape of the target information function is known and can be defined, the test or STF development is performed with the idea of recreating the shape of a \emph{relative information} \cite{van1989relative}.
+
+%\subsection{Existing Procedures}
+
+%Adaptive STFs are . According to this procedure, the administration of each item depends on the responses registered at the previous items. 
+%At each iteration, a temporary estimate of the latent trait level of the respondent is computed based on the responses registered up to that point, and the next administered item is the one that can maximize the information for that level.
+%As such, each respondent can be administered with a different subset of items, which aims at maximizing the measurement precision for each respondent.
+
+%The latent trait levels on which the static STFs focus the most might change and should be defined in advance.
+For instance, if the STF is aimed ad the assessment of clinical population with medium-low latent trait levels, the items composing the STF should be mostly located in those regions.
+The STF may not be optimal in terms of maximizing measurement precision for each individual respondent.
+However, it would still ensure adequate measurement precision for respondents within those specific latent trait levels, providing reliable measurement for those groups.
+
+%Although adaptive STFs are undoubtedly convenient since they allow for obtaining precise estimates of the latent trait level of each respondent by tailoring the item administration, they might be problematic in some contexts.
+For instance, they require the implementation of adaptive algorithms on ad-hoc platforms for the administration, which might not be always accessible or they might be difficult to use with some target populations (e.g., the elderly).
+Moreover, fairness issues might be raised in evaluation contexts where it is important to administered all respondents with the same subset of items.
+
+This manuscript presents three new IRT-based algorithms for the development of STFs, which ground the item selection on the definition of the general desired characteristics of the STF as expressed by a target test information function.
+The continuous definition of the desired characteristics allows for overcoming the issues related to the a priori specification of $\theta$ targets, hence releasing the constraint on the optimal number of items.
+As the  target information function is empirically defined with a specific shape and height, these algorithms attempt at finding the item selection to include in the STF that is best able to reduce the distance from an absolute information.
+All algorithms consider the distance between the target information function and the information function obtained on the items selected up to that iteration with the aim of bridging the gap between the two information functions (i.e., bringing the information function of the STF as close as possible to the target one).
+As it will be further illustrated, they differ according to how they consider the distance between the information functions and hence on how they consider the items for inclusion in the STF.
+The performance of the algorithms is evaluated in a simulation study, where it is compared against that of a brute force algorithm.
+Since the brute force algorithm selects the item combination best able to reduce the distance from the target information function among all the possible item combinations of different length, its item selection is considered as the gold standard.
+
+\normalcolor
+
+% This contribution is focused on the development of STFs from full-length tests.
+Nonetheless, the presented algorithms can be also used for the development of informative tests developed from item banks.
+
+The manuscript is organized as follows.
+The next section illustrates the IRT model used as reference in this work, along with the definition of the related information functions.
+The proposed algorithms are then presented, followed by a simulation study that compares their performance in STFs development.
+The manuscript concludes with final remarks.
+
+%Come limitazione il fatto che il numero dei theta target influenza molto il numero di item da inserire, tanto che più theta target ci sono più item devono essere includi nella forma breve ma forse più importante il fatto che è basata su valori puntuali del tratto latente quando forse sarebbe più comodo definer una tif generale da riprodurre (riprendere il discorso di Tif relativa e Tif assoluta e dire chiaramente che in questo caso ci muoviamo nel caso di una tif assoluta visto che viene definita un'altezza dell'infromazione ma che in futuro ci contreeremo sulla tif relativa)
+
+\section*{Item Response Theory and Information Functions}
+Different IRT models are available for the analyses of dichotomous responses, which differentiate according to the characteristics of the items that they take into account. 
+In this application, 
+the 2-Parameter Logistic model \cite<2-PL;>{birnbaum1968} is used as a reference, which considers item difficulty and item discrimination.
+According to this model, the probability of observing a positive response by person $p$ on item $i$ is formalized as:
+
+\begin{equation}
+	P(x_{pi} = 1|\theta_p, b_i, a_i) = \dfrac{\exp [a_i(\theta_p - b_i)]}{1 + \exp [a_i(\theta_p - b_i)]},
+\end{equation}
+where $\theta_p$ is the ability parameter of person $p$ (i.e., the latent trait level of $p$), $b_i$ is the difficulty parameter of item $i$ (i.e., the location of $i$ on the latent trait), and $a_i$ is the discrimination parameter of item $i$ (i.e., the ability of $i$ to distinguish respondents with different levels of $\theta$).
+The probability of observing a positive response changes as the distance between the ability of the person $\theta_p$ and the location of the item on the latent trait $b_i$ changes, such as it is of the 50\% when the ability of person $p$ matches the difficulty of item $i$.
+
+The precision with which each item measures different levels of the latent trait is described by the \emph{item information function}, $\text{IIF}_i = a_i^2P(\theta, b_i, a_i)[1- P(\theta, b_i, a_i)]$.
+In the 2-PL, the IIF reaches its maximum when $\theta_p = b_i$.
+The precision with which the test as a whole measures the entire latent trait is expressed by the \emph{test information function}, which is the sum of the IIFs of all the items in a test or item bank, $\text{TIF} = \sum_{i \in B} \text{IIF}_i$ (where $B$ is the set of items in a test or in an item bank).
+Given the dependency between the location of the items on the latent trait, their discrimination parameters, and their informativeness with respect to different latent trait levels,  the shape and height of the TIF depends on the spread of the items along the latent trait continuum.
+ Since the TIF is the sum of the IIFs, the higher the number of items in  test, the higher the TIF.
+Alternatively, a mean TIF can be computed by averaging for the number of items.
+As it will be further illustrated, the computation of the mean TIF might be more convenient when developing STFs.
+
+\normalcolor
+
+\section*{The Algorithms}
+
+The three introduced algorithms aim at approximating as best as possible the desired characteristics of a test, as expressed by a target information function (TIF-target), by selecting the items best able to reduce the distance between the information function of the STF and the target one.
+Two of the algorithms (item locating algorithm -- ILA -- and item selecting algorithm -- ISA --) can be seen as the natural evolution of the $\theta$-target procedure in that they ground the item selection on the characteristics of each item with respect to a specific $\theta$ target, which is defined at each iteration as the latent trait level where the maximum distance between the two information functions is observed.
+The third one (Frank) overcomes the definition of the $\theta$ targets altogether by considering the entire latent trait for the item inclusion at each iteration.
+As such, it accounts for the measurement precision of each item with respect to the entire latent trait and to the TIF-target.
+All three algorithms attempt at bridging the gap between the TIF-target and the temporary information function obtained from the items selected up to that iteration. 
+By grounding the item selection on a specific $\theta$ target, ILA and ISA bring the two information functions closer considering only one latent trait level at the time. 
+On the other hand, by grounding the item selection on its contribution to the temporary information function, Frank bridges the gap between the two functions considering the entire latent trait. 
+%However, ILA and ISA attempt at bridging the gap between the two information functions considering one discrete level at the time, the $\theta$ target, while Frank considers the entire latent trait. 
+%As such, ILA and ISA select the best item according to one specific point of the latent trait, while Frank  selects the item that allows for bridging the gap between the information functions throughout the entire latent trait.
+%\color{red} Forse questa parte si può togliere 
+%In ILA and ISA, the $\theta$ targets are defined at each iteration as the level of the latent trait for which the maximum distance between the information function obtained from the items selected up to that iteration and the target information function is observed.
+%Differently from the $\theta$-target procedure, the number of items does not need to be defined a priori and the algorithms automatically searches for the levels of the latent trait that need to be addressed at each iteration.
+The main issue of ILA and ISA pertains the items selection grounded on discrete levels of the latent trait, instead of considering its continuous nature.
+%Frank aims at overcoming this issue by considering the continuous nature of the target information function.
+At each iteration, it explores the distance between the target information function and the information function obtained with the items selected up to that iteration, and selects the item that is best able to bridge the gap between the target and the temporary information function considering the entire latent trait.
+\normalcolor
+
+The ability of ILA, ISA, and Frank to approximate an absolute TIF-target is evaluated by comparing their performance against that of a brute force algorithm.
+This algorithm
+ tries every possible combination of items without repetition and selects the one best able to bridge the gap between the two information functions among all the possible item combinations attainable from the full-length test.
+As such, its resulting STF is considered as the gold standard.
+
+All algorithms but the brute force start with an empty item collection, $Q$, in which an item is included at each iteration until the termination criterion is met.
+%Since each algorithm starts with an empty set and adds one item at each iteration, the mean TIF is computed at each iteration by considering the number of items in the current set $Q$.
+Before any item can be included in $Q$, the termination criterion tests its usefulness in reducing the distance from the TIF-target by concurrently considering the TIF-target, the TIF obtained from the STF with the last item considered for inclusion (i.e., provisional item), and the TIF obtained from the STF without this last item.
+%At each iteration, the termination criterion tests whether other items should be added in the STF by considering the distance between the TIF-target, the TIF obtained by adding the last item considered for inclusion (i.e., provisional item), and the TIF obtained without this item.
+If the distance between the former two is greater than or equal to the distance between the latter two, the provisional item is not included in the STF and the algorithm stops.
+Vice versa, the item is included and the algorithms proceeds to a new iteration.
+The reasoning is as follows.
+If the distance between the TIF-target and the STF including the provisional item is greater than or equal to the difference between the TIF-target and the STF without the provisional item, the provisional item does not contribute in reducing this distance.
+Since the provisional item is the best one among the available options according to the selection method of each algorithm and does not contribute to reduce the distance from the TIF-target, the algorithm stops.
+When the termination criterion is reached, the final item selection included in the STF is the one in $Q$ up to the last iteration, which does not include the provisional item.
+
+In what follows, the notation $||X||$ is used to denote the cardinality of a generic set $X$, $B$ denotes the set of items in the full-length test, $Q_x$ indicates the subset $Q_x \subset B$ of items included in the STF by each algorithm $x \in \{\text{Bruto}, \text{ILA}, \text{ISA}, \text{Frank}\}$, and $\text{TIF}^*$ indicates the TIF-target.
+The TIF-target is used to express the desired characteristics of the STF in terms of absolute information across the latent trait.
+Since the focus of the manuscript is on the development of STFs from full-length tests, $Q_x$ is taken to be a proper subset of the items in the test, such that it is not possible to obtain a STF that contains all the items of the test.
+If the algorithms are applied for the generation of informative tests from an item bank, $Q_x$ can be the subset of $B$, and all the items can be included in the test.
+
+%\add{current number of items in the STF, va ben definito da qualche parte.
+nei cofnronit si parla di una stf che è in divenire a partire  da un insieme vuoto di item e che la media è calcolata sulla base del numero di item che sono presenti in quel momento anella STF}
+
+The brute force algorithm (i.e., Bruto) does not have a proper termination criterion given that it generates all the possible STFs of different length and then chooses the one that allows for minimizing the distance from the $\text{TIF}^*$.
+It follows that Bruto does not have iterations either.
+%For all other algorithms, the termination criterion is the same. 
+%Specifically, it tests whether the last provisional item (i.e., the item that is being evaluated for the inclusion in the STF at the current iteration) is useful in reducing the distance from the $\text{TIF}^*$.
+%If the distance between the $\text{TIF}^*$ and the provisional TIF that includes the last provisional item (denoted as $\text{pTIF}$) is greater than or equal to the distance between the $\text{TIF}^*$ and the TIF obtained without the provisional item, this is deemed as not useful in reducing the distance from the $\text{TIF}^*$ and the algorithm stops.
+The subset of items would hence be the one at the previous iteration, excluding the provisional item.
+%If the same comparison is false, the provisional item is deemed as useful in reducing the distance from the $\text{TIF}^*$, it is included in the subset of items and a new iteration starts. 
+%Not having a termination criterion, Bruto does not have iterations either.
+Indeed, Bruto generates all the possible STFs of different lengths considering different combination of items, and it chooses the one that is best able to reduce the distance from the $\text{TIF}^*$.
+%Bruto is the only algorithm for which the number of iterations is known in advance, since it compares the TIF attainable from all the possible combinations of items of different length from an item bank \add{non so se sia corretto parlare di number of iterations}.
+The number of iterations performed by the other algorithms cannot be known in advance since they iteratively compare the TIF obtained by including the provisional item with the $\text{TIF}^*$ until the termination criterion is met.
+The only constraints on the number of iterations pertains the lower and upper bound. 
+ Specifically, since all the algorithms start from an empty set of items, they are forced to perform at least two iterations such that at least one item can be included in the STF.
+Moreover, the upper constraint is logically imposed by the number of items in the full-length test, such that the maximum number of iterations is equal to the cardinality of the full-length test.
+Importantly, if the algorithms reach the last iteration and the termination criterion is not met, it is considered as a failure in the their ability to find a STF able to reproduce the $\text{TIF}^*$.
+
+ Finally, since the TIF is usually obtained by summing the IIFs together, the more the items in a test, the higher the TIF. 
+ As such, when the TIF is used as criterion for deciding the best subset of items to include in a STF, the risk is to favor STFs that include more items. 
+ To avoid this risk, the mean TIF of the STF is used in the comparison against the TIF-target. In what follows, the mean  TIF is simply indicated as TIF.
+
+\subsection*{Bruto}
+
+Bruto compares the TIF of all the possible item combinations attainable from the items in $B$ against the $\text{TIF}^*$ and selects the item combination best able to reduce the average distance from the $\text{TIF}^*$, as follows:
+
+%\begin{tikzpicture}[node distance=2cm]
+%	
+%	% Nodes
+%	\node (start) [startstop] {Start: $\forall Q \in\mathcal{Q} = 2^B \setminus \{\emptyset, B\}$};
+%	\node (step1) [process, below of=start] {Step 1: Compute $\mathbf{TIF}^Q = \frac{\sum_{i \in Q} IIF_i}{||Q||}$};
+%	\node (step2) [process, below of=step1] {Step 2: Compute $\overline{\Delta}_{\mathbf{TIF}^Q} = \mathit{mean}(|\mathbf{TIF}^* - \mathbf{TIF}^Q|)$};
+%	\node (end) [startstop, below of=step2] {End: $Q_{bruto} = \arg \min_{Q \in \mathcal{Q}} \overline{\Delta}_{\mathbf{TIF}^Q}$};
+%	
+%	% Arrows
+%	\draw [arrow] (start) -- (step1);
+%	\draw [arrow] (step1) -- (step2);
+%	\draw [arrow] (step2) -- (end);
+%	
+%\end{tikzpicture}
+
+$\forall Q \in\mathcal{Q} = 2^B \setminus \{\emptyset, B\}$, compute
 
 \begin{enumerate}
-	\item $\mathbf{TIF}^{Q} =  \frac{\sum_{i \in Q} IIF_i}{||Q||}$
-	\item $\overline{\Delta}_{\mathbf{TIF}^{Q}} =  \mathit{mean}(|\mathbf{TIF}^* - \mathbf{TIF}^{Q}|)$  \add{ho dei dubbi su questa notazione.
-la media è calcolata attraverso i valori di theta}.
-In alternativa a questa notazione: $\overline{\Delta}_{\mathbf{TIF}^{Q}} = \frac{|\mathbf{TIF}^* - \mathbf{TIF}^{Q}|}{||\theta||}$
-
+	\item $TIF^{Q} =  \frac{\sum_{i \in Q} IIF_i}{||Q||}$ and
+	\item $\overline{\Delta}_{\text{TIF}^{Q}} =  \mathit{mean}(|TIF^* - TIF^{Q}|)$. 
 \end{enumerate}
 
-$Q_{bruto} = \arg \min_{Q \in \mathcal{Q}} \overline{\Delta}_{\mathbf{TIF}^{Q}}$
+Then, $Q_{bruto} = \arg \min_{Q \in \mathcal{Q}} \overline{\Delta}_{\mathbf{TIF}^{Q}}$.
 
-\section{Item Locating Algorithm}
+For all the possible item combinations in $\mathcal{Q}$ that are attainable from the item bank $B$ (excluding the empty set and the full set of items), Bruto computes: (1.) the mean TIF, $TIF^Q$ and (2.)
+the average distance $\overline{\Delta}_{\text{TIF}^Q}$ between the $\text{TIF}^*$ and the $\text{TIF}^Q$.
+Then, the final subset of items of the STF, $Q_{bruto}$, is the one that allows for obtaining the least value of $\overline{\Delta}_{\text{TIF}^{Q}}$, hence for minimizing the distance from the $\text{TIF}^*$.
 
-\add{Siccome la filosofia di ILA e ISA è molto simile sarebbe carino trovare loro un nome comune e poi declinarle nelle loro specificità. ci pensiamo}
+Given that Bruto attempts all the possible item combinations in $\mathcal{Q}$, it ensures to find the one that is best able to minimize the average distance from the $\text{TIF}^*$.
+% that aims at the selection of best combination of items to recreate a given $TIF^*$  by comparing the TIF-target with the TIF obtained with all the possible combinations of items of different lengths that are obtainable from an item bank $B$.
+The total number of item combinations of different lengths $\mathcal{Q}$ is equal to the power set of the item bank minus the empty set and the full set of items.
+For each item combination $Q \in \mathcal{Q}$, the mean TIF $TIF^Q$ is computed, and is compared against the TIF-target.
+Specifically, the average distance between the TIF-target and $TIF^Q$ is computed and the item combination selected by Bruto is the one among all item combinations that allows fro minimizing the distance between $TIF^*$ and $TIF^Q$.
 
-\textbf{Set up: }
+\subsection*{Item Locating Algorithm}
 
-$B$: Item bank
+At each iteration $k$, the item locating algorithm (ILA) selects the item that minimizes the distance on the latent trait from a specific $\theta$ target (denoted as $\theta_{target}$), as follows:
 
-$Q^k \subset B$: Set of item indexes selected for inclusion in the STF up to iteration $k$
-
-$\mathbf{TIF}^*$: TIF target
-
-$D$: Item selected at each iteration
-
-$\mathbf{PIF}_D^k = \frac{\sum_{i\in Q^k \cup \{D^k\}} IIF_i}{||Q^k \cup \{D\}||}$, provisional mean tif at iteration $k$, including the item selected in $D^k$
-
-$||Q^k||$: cardinality of $Q^k$ at iteration $k$
-
-At $k = 0$: $\mathbf{PIF}_D^0 = (0, 0, \ldots, 0)$, $Q^0 = \emptyset$, $D^0 = \emptyset$,
-
+At $k = 0$: $\text{TIF}^0(\theta) = 0 \, \forall \theta$, $Q^0 = \emptyset$. For $k \geq 0$,
 \begin{enumerate}
-	\item $\theta_{target} := \arg \max |\mathbf{TIF}^* - \mathbf{PIF}_D^{k}|$
-	\item $D^k = \arg \min_{i \in B\setminus Q^k} |\theta_{target} - b_i|$
-	\item $\mathbf{PIF}_D^k = \frac{\sum_{i \in Q^k \cup \{D\}} IIF_i}{||Q^k \cup \{D\}||}$
-	\item Termination Criterion: $|\mathbf{TIF}^* - \mathbf{PIF}_D^k| < |\mathbf{TIF}^* - \mathbf{TIF}^{k}|$: 
+	\item $\theta_{target} := \arg \max |\text{TIF}^* - \text{TIF}^{k}|$
+	\item $i^* := \arg \min_{i \in B\setminus Q^{k}} |\theta_{target} - b_i|$
+	\item $\text{pTIF}_{i^*} = \frac{TIF^k + IIF_{i^*}}{||Q^{k}|| + 1}$ %$\mathbf{pTIF}_{i^*}= \frac{\sum_{i \in Q^{k} \cup \{i^*\}} IIF_i}{||Q^{k} \cup \{i^*\}||}$ $=$ 
+	\item Termination Criterion: $|\text{TIF}^* - \text{pTIF}_{i^*}| \geq |\text{TIF}^* - \text{TIF}^{k}|$: 
 	\begin{itemize}
-		\item TRUE: $k := k +1$, $Q^{k} = Q^{k-1} \cup \{D\}$, iterates 1-5 (\add{Ho scritto $k-1$ perché siccome ho scritto all'inizio che $k$ si aggiorna e diventa $k+1$ mi sembrava sensato})
-		\item FALSE: The item in $D$ does not contribute to reduce the distance from the TIF target, hence: $Q_{ISA} = Q^k$
+		\item FALSE:  $Q^{k+1} = Q^{k} \cup \{i^*\}$, $\text{TIF}^{k+1} = \text{pTIF}_{i^*}$, iterates 1-4 
+		\item TRUE: Stop, %The item in $i^*$ does not contribute to reduce the distance from the TIF-target, hence: 
+		$Q_{ILA} = Q^k$
 	\end{itemize}
@@
 
-\section{Item Selecting Algorithm}
+ILA starts at iteration $k=0$, where $Q^0 = \emptyset$ and $\text{TIF}^0(\theta)$ is 0 for all the values of $\theta$. 
+At each iteration: (1.) the $\theta_{target}$ is defined as the latent trait level for which the highest distance between the $\text{TIF}^*$ and the $\text{TIF}^k$ is observed; (2.) The item $i \in B\setminus Q^k$ for which the minimum distance from the $\theta_{target}$ is observed is considered as the provisional item $i^*$; (3.) A provisional TIF, $\text{pTIF}_{i^*}$ is computed as the average TIF considering the items in $Q^k$ and item $i^*$, with the condition $i \in B\setminus Q^k$ ensuring that the items are selected only once; and (4.)
+The termination criterion tests whether the provisional item $i^*$ is useful for reducing the distance from the $\text{TIF}^*$.
+Specifically, if the distance between the $\text{TIF}^*$ and the $\text{pTIF}_{i^*}$ (TRUE) is greater than or equal to the distance between the $\text{TIF}^*$ and the $\text{TIF}^k$ (i.e., the TIF obtained by considering the item in $Q^k$, without item $i^*$), the item in $i^*$ does not help in reducing the distance from the $\text{TIF}^*$.
+As such, ILA stops, and  the subset of items selected by ILA, $Q_{ILA}$, is the one in $Q^k$.
+Conversely (FALSE), if the distance between the $\text{TIF}^*$ and the $\text{pTIF}_{i^*}$ is lower than that between the $\text{TIF}^*$ and the $\text{TIF}^k$, then the item in $i^*$ is useful in reducing the distance from the TIF-target, it is included in the set of selected items, and a new iteration starts, $Q^{k+1} = Q^k \cup \{i^*\}$
 
-Same as ILA but based on the Item Information Functions.
+%In this sense, ILA is based on the distances between the locations of the items on the latent trait (the difficulty parameter $b_i$) and the $\theta_{target}$. 
+%The $\theta_{target}$ corresponds to the level of the latent trait for which the maximum distance between the $TIF^*$ and the TIF containing the subset of items selected up to that the iteration, $Q^k \subset B$, is observed.
+%The termination criterion tests whether the average distance between the $TIF^*$ and the provisional TIF obtained including the last selected item $i^*$ (denoted as $pTIF_{i^*}$) is greater than or equal to the distance between the $TIF^*$ and the TIF obtained from the items in $Q^k$.
+If this is true, it means that the last selected item $i^*$ does not help in reducing the distance from the $TIF^*$, hence ILA stops and the final set of items is the one without item $i^*$, such that $Q_{ILA} = Q^k$.
+%Otherwise, if the termination criterion is not met, the last selected item is included in the set $Q$, such that $Q^{k+1} = Q^k \cup \{i^*\}$, and a new iteration starts.
 
-\color{blue}
+\subsection*{Item Selecting Algorithm}
 
-Set up same as ILA: 
-$B$: Item bank
+The item selecting algorithm (ISA) follows the same procedure as ILA.
+However, ILA and ISA differentiate according to the method with which the provisional items $i^*$ are considered for inclusion at each iteration.
+While ILA selects the item that minimizes the distance on the latent trait from the $\theta_{target}$, ISA selects the item that maximizes the IIF with respect to the $\theta_{target}$, as follows:
 
-$Q^k \subset B$: Set of item indexes selected for inclusion in the STF up to iteration $k$
-
-$\mathbf{TIF}^*$: TIF target
-
-$D$: Item selected at each iteration
-
-$\theta_{target}$: theta target selected at each iteration
-
-$\mathbf{PIF}_D^k = \frac{\sum_{i\in Q^k \cup \{D\}} IIF_i}{||Q^k \cup \{D\}||}$, provisional mean tif at iteration $k$, including the item selected in $D$
-
-$||Q^k \cup \{D\}||$: cardinality of $Q^k \cup \{D\}$ at iteration $k$
-
-\normalcolor
-
-At $k = 0$: $\mathbf{PIF}_D^0 = (0, 0, \ldots, 0)$, $Q^0 = \emptyset$, $D^0 = \emptyset$,
+At $k = 0$: $\text{TIF}^0(\theta) = 0 \, \forall \theta$, $Q^0 = \emptyset$. For $k \geq 0$,
 
 \begin{enumerate}
-	\item $\theta_{target} := \arg \max |\mathbf{TIF}^* - \mathbf{PIF}_D^{k}|$
-	\item $IIF_{i \in B \setminus Q^k} = a_i^2P(\theta_{target}, a_i, b_i)[1-P(\theta_{target}, a_i, b_i)]$
-	\item $D := \arg \min_{i \in B\setminus Q^k} |\theta_{target} - IIF_i|$
-	\item $\mathbf{PIF}_{D^k} = \frac{\sum_{i \in Q^k \cup \{D\}} IIF_i}{||Q^k \cup \{D\}||}$
-	\item Termination Criterion: $|\mathbf{TIF}^* - \mathbf{PIF}_D^k| < |\mathbf{TIF}^* - \mathbf{TIF}^{k}|$: 
+	\item $\theta_{target} := \arg \max |\text{TIF}^* - \text{TIF}^{k}|$
+%	\item $IIF_{i \in B \setminus Q^k}(\theta_{target}) = a_i^2P(\theta_{target}, a_i, b_i)[1-P(\theta_{target}, a_i, b_i)]$
+	\item $i^* := \arg \max_{i \in B\setminus Q^k} \text{IIF}_i(\theta_{target})$
+	\item $\text{pTIF}_{i^*} = \frac{TIF^k + \text{IIF}_{i^*}}{||Q^{k}|| + 1}$
+	\item Termination Criterion: $|\text{TIF}^* - \text{pTIF}_{i^*}| \geq |\text{TIF}^* - \mathbf{TIF}^{k}|$: 
 	\begin{itemize}
-		\item TRUE: $k := k +1$, $Q^{k} = Q^{k-1} \cup \{D\}$, iterates 1-5 (\add{Ho scritto $k-1$ perché siccome ho scritto all'inizio che $k$ si aggiorna e diventa $k+1$ mi sembrava sensato})
-		\item FALSE: The item in $D$ does not contribute to reduce the distance from the TIF target, hence: $Q_{ISA} = Q^k$
+		\item FALSE:  $Q^{k+1} = Q^{k} \cup \{i^*\}$, $\text{TIF}^{k+1} = \text{pTIF}_{i^*}$, iterates 1-4 
+\item TRUE: Stop, %The item in $i^*$ does not contribute to reduce the distance from the TIF-target, hence: 
+$Q_{ISA} = Q^k$
 	\end{itemize}
 \end{enumerate}
+Since the procedure is the same as that described for ILA, it will not be discussed further.
+The only difference concerns the second step of the algorithm (2.), that is the inclusion of the items $i \in B \setminus Q^k$ in $\{i^*\}$.
+At each iteration, the provisional item $i^*$ that is considered for inclusion in $Q^k$ is the one that maximizes the IIF for the specific $\theta_{target}$.
 
-\section{Frank}
+\subsection*{Frank}
 
-The setup is like the one of ILA and ISA:
+Instead of grounding the item selection at each iteration on a single latent trait level (i.e., the $\theta_{target}$) as ILA and ISA do, Frank considers the entire latent trait for the item selection, in that it selects the item whose IIF is best able to reduce the distance from the $\text{TIF}^*$ along the entire latent trait, as follows:
 
-$B$: Item bank
-
-$Q^k$: set of items selected at iteration $k$
-
-$D$: provisional item selected at each iteration
-
-\add{$\mathbf{PIF}$: provisional mean tif}
-
-At $k =0$, $\mathbf{PIF}^0 = (0, 0, \ldots, 0)$, $Q^0 = \emptyset$, iterate
+At $k = 0$: $\text{TIF}^0(\theta) = 0 \, \forall \theta$, $Q^0 = \emptyset$. For $k \geq 0$,
 
 \begin{enumerate}
-	\item  $A^k = B \setminus Q^k$ (sets of available items at iteration $k$)
-	\item $\forall i \in A^k$, $\mathbf{PIF}_{i}^k = \frac{\mathbf{TIF}^k + \mathbf{IIF}_{i}}{||Q^k||+1}$
-	\item $D = \arg \min_{i \in A^k} |\mathbf{TIF}^* - \mathbf{PIF}_i^k|$
-	\item Termination criterion: $|\mathbf{TIF}^* - \mathbf{PIF}_D^{k}| < |\mathbf{TIF}^* - \mathbf{TIF}^{k-1}|$: 
+	\item  $A^k = B \setminus Q^k$ 
+	\item $\forall i \in A^k$, $pTIF_{i}^k = \frac{\text{TIF}^k + \text{IIF}_{i}}{||Q^k||+1}$
+	\item $i^* = \arg \min_{i \in A^k} |\text{TIF}^* - \text{pTIF}_i|$
+	\item Termination criterion: $|\text{TIF}^* - \text{pTIF}_{i^*}| \geq |\text{TIF}^* - \text{TIF}^{k}|$: 
 	\begin{itemize}
-		\item  If true, $k := k + 1,$ $Q^{k} = Q^{k-1} \cup \{D\}$, restart from 1 \add{C'è il meno 1 per la stessa ragione scritta per ILA e ISA}
-
-		\item  If false, stops, $Q_{Frank} = Q^k$
+		\item FALSE:  $Q^{k+1} = Q^{k} \cup \{i^*\}$, $TIF^{k+1} = pTIF_{i^*}$, iterates 1-4 
+\item TRUE: Stop, %The item in $i^*$ does not contribute to reduce the distance from the TIF-target, hence: 
+$Q_{Frank} = Q^k$
 
@@
 
+When Frank starts ($k = 0$), the subset of items $Q^0$ is empty and the $\text{TIF}^0$ is 0 for all the $\theta$ levels. 
+At each iteration $k$: (1.) a set of available items is generated as the items in the item bank that have not been included in the STF yet, $A^k = B \setminus Q^k$; (2.)
+An average provisional TIF, $\text{pTIF}$, is computed by adding the IIF of each of the items in the set of the available items $A^k$, one at the time, to the TIF obtained from the items in $Q^k$ (The denominator is obtained by adding 1 to the cardinality of $Q^k$); (3.) Among all the items in $A^k$, the one that allows for minimizing the distance between $\text{pTIF}$ and $\text{TIF}^*$ is included in $i^*$; (4.)
+The termination criterion is tested. 
+If the distance between the $\text{TIF}^*$ and the $\text{pTIF}_{i^*}$ is greater than or equal to the distance between the $\text{TIF}^*$ and the $\text{TIF}^k$ (i.e., the TIF obtained from the items in the subset $Q^k$, without item $i^*$) (TRUE), then the item $i^*$ does not contribute in the reduction of the distance from the $\text{TIF}^*$, the algorithm stops, and the final item selection is the one without the item in $i^*$, $Q_{frank} = Q^k$.
+Conversely (FALSE), the item in $i^*$ does contribute in the reduction of the distance from the $\text{TIF}^*$, hence it is included in the set of items and a new iteration starts, $Q^{k+1} = Q^k \cup \{i^*\}$.
+
+%Specifically, at each iteration $k$ a set of available items is created as the items that are in the item bank and that have not been selected for inclusion in the STF yet, $A^k = B \setminus Q^k$.
+Then, for every item in $A^k$, a $pTIF$ is computed by adding the IIF
+%of each item (one at a time) to the $TIF$ obtained from the items in $Q^k$ (i.e., the subset of items selected up to that iteration).
+The item whose IIF allows for reducing the distance from the $TIF^*$ is included in $i^*$ and the termination criterion (the same as that for ILA and ISA) is checked.
+If the average distance between the $TIF^*$ and the $pTIF$ obtained by including the last selected items in $i^*$ is greater than or equal to average distance between the $TIF^*$ and the TIF obtained from the set $Q^k$ of the items selected up to that iteration without item $i^*$, then the algorithm stops and the final item selection is the one at the previous iteration, without the item in $i^*$, such that $Q_{Frank} = Q^k$.
+Otherwise, if the termination criterion is not met, the item in $i^*$ is included in the set of items, $Q^{k+1} = Q^k \cup i^*$, and the algorithm starts a new iteration.
+
+\section*{Simulation Study}
+
+\subsection*{Simulation Design}
+The performance of the algorithms was compared in 100 replications. 
+For each replication a full-length test $B$ ($||B|| = 11$) was generated by randomly drawing the difficulty $b_i^*$ and discrimination $a_i^*$ parameters from uniform distributions, $\mathcal{U}(-3,3)$ and $\mathcal{U}(0.9, 2)$, respectively.
+The $\text{TIF}^*$ was generated by randomly selecting some of the items from the full-length test $B$, which is also the set from which the items are selected for inclusion in the STF by each of the algorithms.
+If the item parameters are not modified for the generation of the $\text{TIF}^*$, there is the risk  of having implausible instances where the TIF of the STF perfectly reproduces the $\text{TIF}^*$.
+On the other hand, if the item parameters are slightly modified to obtain the $\text{TIF}^*$, a more realistic and ecological scenario is obtained where the items selected for the inclusion in the STF can approximate the $\text{TIF}^*$ without reaching a perfect overlap.
+% it poses the risk for the algorithms to result in the same exact selection of items, and that the TIF of the STF could exactly reproduce the TIF-target, which is a pretty unrealistic situation.
+By modifying the parameters of the items used for generating the TIF-target, it is possible to avoid the not so plausible situation of perfect overlap between the TIF-target and the that of the STF, while having a more ecological scenario where the TIF obtained from the STF approximate but not does not overlap the $\text{TIF}^*$.
+To reproduce this last ecological scenario, the difficulty $b_i^*$ and discrimination $a_i^*$ parameters of the items randomly selected for the generation of the $\text{TIF}^*$ were modified by adding values  $b_i^+$ and $a_i^+$ randomly drawn from uniform distributions, $\mathcal{U}(-0.20, 0.20)$.
+A constraint was made on the discrimination parameters to avoid negative discrimination parameters. Specifically, if a discrimination parameter was found to be negative, it was multiplied by $-1$. 
+%\alert{va detto perché non abbiamo creato la TIF-target dalla item bank, perché può succedere che la tif della stf può approssimare alla TIF-target ma non coincidere.
+avendo invece gli item che generano la TIF-target nell'item bank, il rischio è che gli algortimi arrivino ad identifcare esattamente quella selezione degli item, andando a creare una situazione desierata ma irrelastica.
+modificando invece i parametri degli item selezionati a acso dalla itemn bank è possibile ottenere una situazione più verosimile dove la tif della stf può approssimare ma non  riprodurre perfettamete la TIF-target}
+For instance, suppose that Items 1, 2, 3 with parameters $b_1^* =-1.0$, $b_2^* =0.0$, $b_3^* = 1.0$ and $a_1^* =0.90$, $a_2^* =1.0$, $a_3^* = 1.50$ are extracted from $B$ and that the random values $b_1^+ =-0.15$ $b_2^+ =0.02$ $b_3^+ = 0.18$ and $a_1^+ = 0.10$ $a_2^+ = -0.18$ $a_3^+ = 0.01$ are randomly drawn to be added to the original item parameters, then the $\text{TIF}^*$ is computed based on the $b_1^* + b_1^+ = -1.15$ , $b_2^* + b_2^+ = 0.02$, $b_3^* + b_3^+ = 1.18$ and $a_1^* + a_1^+ = 1.00$, $a_2^* + a_2^+ = 0.82$, $a_3^* + a_3^+ = 1.51$ modified parameters.
+
+\subsection*{Comparison Analyses}
+At each replication, Bruto, ILA, ISA, and Frank were applied.
+The algorithms were compared in terms of computational time and proportion of successes in finding an item selection able to reproduce the $\text{TIF}^*$.
+A failure is registered anytime an algorithm runs out of items from $B$ without finding a STF able to reduce the mean distance from the $\text{TIF}^*$.
+
+Given that Bruto tries every possible item combination $Q \in \mathcal{Q}$, the item selection $Q_{\text{Bruto}}$ is the one best able to minimize the average mean distance from the $\text{TIF}^*$ among all the possible item combinations.
+%Bruto is the algorithm best able to retrieve the item selection $Q_{\text{Bruto}}$, among all the possible item combinations $\mathcal{Q}$ that minimizes the distance from the $\text{TIF}^*$. 
+All the item selections generated by Bruto can be ordered in terms of increasing average distance from the $\text{TIF}^*$, $\forall (Q, Q') \in \mathcal{Q}, Q \preceq Q' \Rightarrow mean(|TIF^* - TIF_Q| \leq |TIF^* - TIF_{Q'}|)$.
+The positions of the item selections $Q_x, x \in \{\text{ILA}, \text{ISA}, \text{Frank}\}$ can be found among the ranking of the STFs developed by Bruto, and their respective percentile rank can be computed.
+The percentile ranks of the item selections obtained with the other algorithms are considered for comparing their performance in terms of average distance from the $\text{TIF}^*$ among all the possible item combinations.
+
+Considering the item selection in $Q_{\text{Bruto}}$ as the gold standard, the symmetric distance from $Q_{\text{Bruto}}$ of the item selections $Q_x$, $x \in \{\text{ILA}, \text{ISA}, \text{Frank}\}$ can be computed.
+The symmetric distance is the cardinality of the set obtained from the union between the set of items that are selected by $x$ but not by Bruto and the set of items that are selected by Bruto but not by $x$,
+$Q_x \Delta Q_{Bruto} = ||\{ \{Q_x \setminus Q_{Bruto}\} \cup \{Q_{Bruto} \setminus Q_{x}\} \}||$.
+A symmetric distance of 0 indicates that Bruto and $x$ selected the same exact set of items, and the lower the value, the better in terms of ability of $x$ to select the same set of items from $B$ as Bruto.
+Take for instance an item pool $B = \{1,2,3,\ldots,11\}$ ($||B|| = 11$). 
+By applying Bruto, ILA, and Frank, the following item selections are obtained:  $Q_{\text{Bruto}} = \{1,2,3,6,9, 10\}$, $Q_{ILA} = \{1,4,5,7,9\}$, $Q_{Frank} = \{1,2,3,9\}$, with $||Q_{\text{Bruto}}|| = 6$, $||Q_{\text{Ila}}|| = 5$, and $||Q_{\text{Frank}}|| = 4$.
+%The results can be summarized as illustrated in Table \ref{tab:symmetric-example}, where the first column denotes the item in $B$, and the other columns are logical vectors composed of 1 (i.e., the item has been selected for inclusion by the algorithm) and 0 (i.e., the item has not been selected for inclusion by the algorithm).
+% 
+% \add{Togli la tabella, applica direttamente la formula sugliinsieme che hai definitio prima}
+%\begin{table}[!h]
+%	\centering
+%	\caption{\label{tab:symmetric-example} Items selected by Bruto, ILA, and Frank from an item bank $B$ of 11 items.}
+%	\begin{tabular}{c c c c }
+%		\hline
+%		Item	&	$Q_{bruto}$	&	$Q_{ila}$	&		$Q_{frank}$	\\
+%		\hline
+%		1	&	1	&	1	&			1	\\
+%		2	&	1	&	0	&			1	\\
+%		3	&	1	&	0	&			1	\\
+%		4	&	0	&	1	&			0	\\
+%		5	&	0	&	1	&			0	\\
+%		6	&	1	&	0	&			0	\\
+%		7	&	0	&	1	&			0	\\
+%		8	&	0	&	0	&			0	\\
+%		9	&	1	&	1	&			1	\\
+%		10	&	1	&	0	&			0	\\
+%		11	&	0	&	0	&			0	\\
+%		\hline
+%	\end{tabular}
+%\end{table}
+The symmetric distances between the item selection provided by Bruto and those provided by the two other algorithms are $Q_{\text{ILA}} \Delta Q_{Bruto} = ||\{ \{Q_{\text{ILA}} \setminus Q_{Bruto}\} \cup \{Q_{Bruto} \setminus Q_{\text{ILA}}\} \}|| = ||\{ \{4,5,7\} \cup \{2,3,6,10\} \}|| = 7$ and $Q_{Frank} \Delta Q_{Bruto} = ||\{ \{Q_{\text{Frank}} \setminus Q_{Bruto}\} \cup \{Q_{Bruto} \setminus Q_{\text{ILA}}\} \}||= ||\{ \{\emptyset\} \cup \{6,10\} \}|| =2$, hence suggesting that Frank showed a better performance in selecting and excluding the same items as Bruto than ILA.
+Precisely, the fact that $Q_{\text{Frank}\setminus Q_{Bruto}} = \emptyset$ implies that $Q_{Frank} \subset Q_{Bruto}$.
+%\add{forse va fatto un discorso sul fatto che è molto influenzata dalla cardinalità dei sottoinsiemi e dal fatto che una sia il sottoinsieme dell'altra.}
+
+Although the symmetric distance provides an overall overview on the ability of the algorithms to retrieve the item selection of Bruto, it cannot disentangle whether the algorithm failed to select items from $B$ that were included by Bruto (underselection) or whether the algorithm failed to exclude the same items as Bruto from $B$ (overselection).
+This information can be obtained by computing ad hoc statistics from the contingency table between $Q_x$ and $Q_{Bruto}$:
+
+\begin{table}[!h]
+	\centering
+	\begin{tabular}{c |c| c| c | c}
+		\multicolumn{2}{c}{}	& \multicolumn{2}{c}{$Q_{Bruto}$} & \\
+			\cline{3-4}
+		\multicolumn{2}{c}{} & \multicolumn{
+			1}{|c}{$q \in B \setminus Q_{Bruto}$} & \multicolumn{
+	1}{c|}{$q \in Q_{Bruto}$}& \\	
+		\cline{2-4}
+		$Q_x$ & $q \in B \setminus Q_{x}$ & $||B \setminus \{Q_x \cup Q_{\text{Bruto}}\}||$ & $||(Q_{Bruto} \setminus Q_x)||$ &  \\
+		& $q \in Q_x$ & $||(Q_{x} \setminus Q_{Bruto})||$ & $||\{Q_x \cap Q_{Bruto}\}||$ & \\
+		\cline{2-4}
+	\end{tabular}
+\end{table}
+
+The main diagonal of the contingency table contains the number of items that have been excluded by both $x$ and Bruto ($||B \setminus ( Q_x \cup Q_{\text{Bruto}})||$) and the number of items that have been included by both ($||Q_x \cap Q_{\text{Bruto}}||$).
+The secondary diagonal contains the discrepancies between the selections provided by $x$ and Bruto, specifically: (i) the number of items that have been excluded by $x$ but have been selected by Bruto ($||(B \setminus Q_x) \cup Q_{\text{Bruto}}||$), and (ii) the number of items that have been excluded by Bruto and selected by $x$ ($||(B \setminus Q_{\text{Bruto}}) \cup Q_{x}||$).
+The statistics that can be computed from this contingency table are: (i) Specificity, the proportion of items that have been excluded by both Bruto and $x$ ($||\{B \setminus (Q_x \cup Q_{bruto})\}||/||\{B \setminus Q_{Bruto}\}||$), (ii) sensitivity, the proportion of items that have been selected by both Bruto and $x$ ($||\{Q_x \cap Q_{Bruto}\}||/ ||Q_{bruto}||$), and (iii) accuracy, the degree to which the item selections of Bruto and $x$ overlaps ($||\{(Q_x \cap Q_{bruto}) \cup B \setminus (Q_x \cup Q_{bruto})\}||/ ||B||$).
+
+%From this contingency table it is possible to compute the specificity, the sensitivity and the accuracy of $x$ with respect to Bruto, which are defined as follows:
+%
+%
+%\begin{itemize}
+%	\item  Specificity:  $||\{B \setminus (Q_x \cup Q_{bruto})\}||/||\{B \setminus Q_{Bruto}\}||$: The items that have been selected by neither Bruto nor $x$
+%	
+%	\item  Sensitivity: $||\{Q_x \cap Q_{Bruto}\}||/ ||Q_{bruto}||$: The items that have been selected by both Bruto and $x$
+%	
+%	\item Accuracy: $||\{(Q_x \cap Q_{bruto}) \cup B \setminus (Q_x \cup Q_{bruto})\}||/ ||B||$: The mean of specificty and accuracy, the items that have been selected by both Bruto and $x$ and those that have been discarded by both.
+%\end{itemize}
+
+The accuracy, sensitivity, specificity indexes range between 0 and 1, where 1 indicates a perfect correspondence between the item selections of $x$ and Bruto.
+The accuracy is 1 if both specificity and sensitivity are 1, which means that $Q_x = Q_{bruto}$ (i.e., $x$ selected the same items from $B$ and excluded the same items from $B$ as Bruto).
+A decrease in the accuracy might occur in different scenarios: (i) a decrease in both the specificity and sensitivity, (ii) a decrease in the sensitivity but not in the specificity, and (iii) a decrease in the specificity but not in the sensitivity.
+To compute these statistics form the item selections $Q_{\text{Bruto}}$, $Q_{\text{ILA}}$, and $Q_{\text{Frank}}$, two contingencies tables can be obtained, one comparing ILA vs.
+Bruto (top panel, $Q_{\text{ILA} \times Q_{\text{Bruto}}}$), and one comparing Frank vs.
+Bruto (top panel, $Q_{\text{Frank} \times Q_{\text{Bruto}}}$).
+
+	\begin{center} % Centering the content inside the minipage
+		\begin{tabular}{c |c| c c| c|}
+		\multicolumn{2}{c}{}	& \multicolumn{2}{c}{$Q_{Bruto}$} & \multicolumn{1}{c}{} \\
+\cline{3-4}
+\multicolumn{2}{c}{} & \multicolumn{
+	1}{|c}{$q \in B \setminus Q_{Bruto}$} & \multicolumn{
+	1}{c|}{$q \in Q_{Bruto}$}& \multicolumn{1}{c}{} \\	
+\cline{2-5}   
+			$Q_{Ila}$ & $q \in B \setminus Q_{\text{ILA}}$ & 2 & 4 &  6\\
+			& $q \in Q_{\text{ILA}}$ & 3 & 2 & 5 \\
+			\cline{2-5}
+			& & 5& 6 & 11\\
+			\cline{2-5}
+		\end{tabular}
+	\end{center}
+
+	\begin{center} % Centering the content inside the minipage
+		\begin{tabular}{c |c| c c| c|}
+		\multicolumn{2}{c}{}	& \multicolumn{2}{c}{$Q_{Bruto}$} & \multicolumn{1}{c}{}\\
+\cline{3-4}
+\multicolumn{2}{c}{} & \multicolumn{
+	1}{|c}{$q \in B \setminus Q_{Bruto}$} & \multicolumn{
+	1}{c|}{$q \in Q_{Bruto}$}& \multicolumn{1}{c}{} \\	
+\cline{2-5}    
+			$Q_{Frank}$ & $q \in B \setminus Q_{\text{Frank}}$ & 5 & 2 & 7  \\
+			& $q \in Q_{\text{Frank}}$  & 0 & 4 & 4\\
+			\cline{2-5}
+			& & 5& 6 & 11 \\
+				\cline{2-5}
+		\end{tabular}
+	\end{center}
+
+The specificity of ILA vs.
+Bruto is \\ $||\{B \setminus (Q_{\text{ILA}} \cup Q_{Bruto})\}||/||\{B \setminus Q_{Bruto}\}|| = ||\{8,11\}||/||\{4,5,7,8,11\}|| = 2/5 = .40$, the sensitivity is $||\{Q_{ILA} \cap Q_{Bruto}\}||/ ||Q_{bruto}|| = ||\{1,9\}/\{1,2,4,6,9,10\}|| = 2/6 = .33$, and the accuracy is $(2+2)/11 = .37$.
+In a similar vein, the specificity, sensitivity, and accuracy of Frank vs.
+Bruto are computed, resulting in $5/5 = 1$, $4/6 = .67$, and $(5+4)/11$, respectively.
+Overall, Frank provides a better accuracy than ILA, due to better specificity and sensitivity of the former than the latter one.
+Specifically, Frank has a specificity of 1, indicated that it excludes the same items as Bruto from the item selection.
+
+Finally, McNemar tests were run to test the differences in the accuracy, sensitivity and specificity of the algorithms with respect to Bruto across all the replications, with $\alpha = .05$.
+The McNemar test is based on an approximation of the $\chi^2$ probability distribution with 1 degree of freedom.
+The critical value is $\chi_{.95}^2 = 3.84$ and it is used to test the null hypothesis that the performance of the two considered algorithms with respect to the gold standard  are equal (i.e., the two algorithms have the same error rate).
+
+\normalcolor
+
+The simulation study was run in \texttt{R}, version XX on a Windows 10 PC (DETTAGLI TECNICI SULLA RAM E ALTRE COSE).
+
+\section*{Results}
+
+Table \ref{tab:desc} reports the computational time and proporton of successes in finding a STF for all the algorithms.
+
+\begin{table}[!h]
+	\centering 
+	\caption{\label{tab:desc} Computational time (minutes) and percentage of successes of the algorithms in finding an STF able to minimize the distance from the TIF-target.}
+	\begin{tabular}{l c c c}
+		\hline
+		Algorithm	&	Time Range	&	Mean Time	&	Percentage of successes	\\\hline
+		Bruto	&	10.5 - 12.5	&	10.8$\pm$0.287	&	100	\\
+		ILA	&	0.002 - 059	&	0.006$\pm$0.007	&	93	\\
+		ISA	& 0.002 - 0.055	&	0.007$\pm$0.008	&	82	\\
+		Frank	&	0.008 - 0.517	&	0.027$\pm$0.052	&	100	\\\hline
+		\multicolumn{4}{p{10cm}}{\emph{Note}: The computational time has been computed on the 100 replications. $||\mathcal{Q}|| = 2^{11} \setminus \{\emptyset, 11\} = 2,046$}
+	\end{tabular}
+\end{table}
+
+Not surprisingly, Bruto always found an item combination able to minimize the distance from the TIF-target, as well as Frank.
+On the other hand, ILA and ISA failed in the $7$\% and $18$\% of the replications.
+Interestingly, the 7 replications for which ILA was not able to recover a STF are included within the 18 failed replications of ISA.
+The 18 replications for which a STF could not be found according to ILA and ISA were excluded from the comparison with Bruto.
+The following results are hence based on the 82 replications for which all the algorithms could find a STF.
+
+Figure \ref{fig:percentile-rank} illustrates the percentile rank ($y$-axis) displayed in increasing distances between the STFs developed by Bruto in each of the 82 replications ($x$-axis) and those developed by  ILA (square), ISA (dot), and Frank (triangle).
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=\linewidth]{img/precentile-rank}
+	\caption{Percentile ranks of the distances from the STFs chosen by Bruto and the STFs produced by ILA (square), ISA (dot), and Frank (triangle).
+The horizontal dashed lines represent the 10\textsuperscript{th} and 50\textsuperscript{th} percentiles.}
+	\label{fig:percentile-rank}
+\end{figure}
+All the STFs developed by Frank were within the 50 percentile of distance, while the STFs developed by ILA and ISA exceeded the 50 percentile in the 22\% and 42\% of cases. 
+Frank resulted in STFs over the 10 percentile of distance in the 18\% of cases, ILA and ISA in the 44\% and 67\% of cases, respectively.
+
+The average symmetric distances from Bruto were:  $Q_{\text{ILA}}\Delta Q_{\text{Bruto}} = 2.70$, $Q_{\text{ISA}}\Delta Q_{\text{Bruto}} = 2.87$ and $Q_{\text{Frank}} \Delta Q_{\text{Bruto}}= 2.46$.
+The item selections of all the algorithms, on average, presented at least 2 items of difference from the selection provided by Bruto, with ISA showing the worst performance and Frank the best one.
+However, by only considering the symmetric distance it is not possible to ascertain whether these results were mostly ascribable to an over selection of items not included in bruto (lack of sensitivity) or an under selction of items included in Bruto (lack of sensitivity).
+To better understand the results on the symmetric distance, 
+Table \ref{tab:accuracy} reports the mean accuracy, sensitivity (i.e., items selected by Bruto and $x$), and specificity (i.e., items selected by neither Bruto nor $x$).
+
+\begin{table}[!h]
+	\centering
+	\caption{\label{tab:accuracy} Accuracy, sensitivity and specificity of the algorithms with respect to the best selection provided by Bruto.}
+	\begin{tabular}{l c c c}
+		\hline
+		Algorithm	&	Accuracy	&	Specificity	&	Sensitivity	\\\hline
+		ILA	&	0.56 $\pm$ 0.33	&	0.68 $\pm$ 0.39	&	0.43 $\pm$ 0.36	\\
+		ISA	&	0.54 $\pm$ 0.32	&	0.64 $\pm$ 0.38	&	0.41 $\pm$ 0.37	\\
+		Frank	&	0.59 $\pm$ 0.34	&	0.68 $\pm$ 0.38	&	0.50 $\pm$ 0.37	\\\hline
+
+	\end{tabular}
+\end{table}
+
+Across the 82 replications, Frank provided the highest average accuracy, followed by ILA and ISA. It is worth noting that the accuracy of all algorithms was below the 60\%. 
+The McNemar test suggested that, when compared against Bruto, Frank performed better than both ILA and ISA ($\chi^2 = 4.90$ and $\chi^2 = 10.58$, respectively), while no significant differences were found between ISA and ILA ($\chi^2 = 2.43$).
+To best understand the implications of the results on the accuracy of the algorithms (i.e., whether they are mostly due to an over inclusion of items or an over exclusion of items), the average specificity and sensitivity should be considered.
+Frank and ILA resulted in the same average specificity, while the sensitivity of ILA was lower than that of Frank.
+In other words, Frank and ILA, on average, had the same ability of not selecting the items for inclusion in the STF as Bruto.
+However, ILA was less able than Frank in selecting for the inclusion in the STF the same items as Bruto.
+The lower accuracy of ILA compared to Frank is hence mostly due to ILA's inability of selecting for inclusion the same items as Bruto.
+ISA showed the least accuracy and specificity of all the algorithms, although its sensitivity was in line with that of ILA.
+
+\section*{Final Remarks}
+
+This manuscript presented new IRT-based algorithms for the development of STFs.
+The functioning of the algorithms depends on the specification of the desired characteristics through the definition of a target information function.
+While all algorithms aim at reducing as much as possible the distance between the provisional information function of the STF and the target information function, they differentiate according to the methods employed for considering the items for inclusion in the STF at each iteration.
+Specifically, two algorithms (ILA and ISA) consider either the location or the informativeness of the items in the full-length test with respect to specific latent trait levels, while the third one (Frank) considers the ability of each item in the full-length test of getting the provisional and target information functions closer.
+
+The results of a simulation study where the performance of the algorithms has been compared against that of a brute force algorithm showed that Frank was the only one (besides the brute force one) to always retrieve a STF.
+Moreover, Frank is the algorithm best able to recreate the TIF-target and to get as close as possible to the item combination selected by the brute force algorithm.
+
+Even among the replications where all the algorithms identified a STF, Frank tended to identify the item selection that was closest, in terms of average distance, from that identified by the brute force algorithm.
+This result is not surprising given that Frank considers the contribution of each item in reducing the distance from the TIF-target across the entire latent trait rather than focusing on a specific level.
+By focusing on a specific level of the latent trait, like ILA and ISA do, and selecting the item that only helps in reducing the distance from the TIF-target for that level, the risk is that even items that are not close to the level, and hence do not help in bridging the gap from the TIF-target, can be selected for the evaluation.
+As such, not useful items (i.e., items that do not reduce the distance) might be included, leading to the termination criterion.
+On the other hand, Frank considers for the inclusion the item that contributes to reduce the distance from the TIF-target across all levels of the latent trait.
+
+%Given that the TIF is an additive function of the IIFs, it increases as the number of  items in the test increases. For this reason, the mean TIF was considered. 
+The TIF of a STF would always be lower than the TIF that could be obtained from the full-length test, meaning that generally a STF is less precise than the full-length test in measuring the latent trait.
+The true advantage of using a STF lies in the fact that respondents would get less tired, and their response accuracy should be maintained during the administration.
+This may be particularly useful when multiple tests are administered to reduce the overall cognitive burden on the respondents.
+This point should be further investigated in future simulation and empirical studies, where the tiredness of the respondents during the administration is accounted for by the algorithm for each administered item.
+
+%All algorithms share the same aim (i.e., reducing the distance from a target information function that describes the desired characteristics of a test) and the same termination criterion, but they differ according to the methods used for considering the items for inclusion  in the STF.
+%All algorithms aim at minimizing the distance from a predefined TIF-target that describes the desired characteristics of the STF. 
+%They differ according to the method used for the selection of the item for inclusion in the STF.  
+%Two algorithms ground the item selection on the ability of each item of reducing the distance from the TIF-target with respect to a single discrete $\theta$ value, denoted as $\theta_{\text{target}}$.
+In one case (i.e., item locating algorithm, ILA), the item whose location is the closest to the $\theta_{\text{target}}$ is included, while in other case (i.e., item selecting algorithm, ISA) the item that is most informative with respect to the $\theta_{\text{target}}$ is selected.
+%Another algorithm (i.e., Frank) considers the ability of each item of reducing the distance from the TIF-target with respect to the entire latent trait. 
+%Besides of the aim, the algorithms share the termination criterion.
+Specifically, at each iteration an item (i.e., provisional item) is selected from the full-length test according to the algorithm-specific method and is considered for the inclusion in the STF.
+%\alert{Non sono sicura della posizioen della spiegazione del criterio di terminazione}
+%The termination criterion tests whether other items should be added in the STF by considering the distance between the TIF-target, the TIF obtained by including the provisional item, and the TIF obtained by excluding the provisional item.
+If the distance between the former two is greater than or equal to the distance between the latter two, the provisional item is not included in the STF and the algorithm stops.
+Vice versa, the item is included and the algorithms proceeds to a new iteration.
+The reasoning is as follows.
+If the distance from the TIF-target of the STF including the provisional item is greater than or equal to the difference from the TIF-target of the STF without the provisional item, it means that the provisional item does not contribute in reducing this distance.
+Since the provisional item is the best one among the available options according to the selection method of each algorithm, but does not contribute to reduce the distance from the TIF-target, the algorithm stops, assuming that no further useful items remain.
+
+%Gonzalez forme breve IRT ML accuartezza forme bevi proprio nel prevedere una diagnosi.
+\newpage
+\bibliographystyle{apacite} 
+\doublespacing
+\bibliography{bibFile}
+
 \end{document}

### 2025-02-05 sis2025/LaTex+Package/styles/author.tex
cose

%%%%%%%%%%%%%%%%%%%% author.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% sample root file for your "contribution" to a proceedings volume
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%% Springer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{svproc}
%
% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%

% to typeset URLs, URIs, and DOIs
\usepackage{url}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\def\UrlFont{\rmfamily}

\begin{document}
\mainmatter              % start of a contribution
%
\title{How much is too much? Item Response Theory procedures to shorten tests}
%
\titlerunning{Hamiltonian Mechanics}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Ottavia M. Epifania\inst{1} and Livio Finos\inst{2}}
%
\authorrunning{Epifania \& Finos} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Ottavia M. Epifania, Livio Finos}
%
\institute{Department of Psychology and Cognitive Science, University of Trento, IT\\
\email{ottavia.epifania@unitn.it}
\and
Universit\'{e} de Paris-Sud,
Laboratoire d'Analyse Num\'{e}rique, B\^{a}timent 425,\\
F-91405 Orsay Cedex, France}

\maketitle              % typeset the title of the contribution

\begin{abstract}
The abstract should summarize the contents of the paper
using at least 70 and at most 150 words. It will be set in 9-point
font size and be inset 1.0 cm from the right and left margins.
There will be two blank lines before and after the Abstract. \dots
% We would like to encourage you to list your keywords within
% the abstract section using the \keywords{...} command.
\keywords{computational geometry, graph theory, Hamilton cycles}
\end{abstract}
%
\section{Fixed-Period Problems: The Sublinear Case}
%
With this chapter, the preliminaries are over, and we begin the search
for periodic solutions to Hamiltonian systems. All this will be done in
the convex case; that is, we shall study the boundary-value problem
\begin{eqnarray*}
  \dot{x}&=&JH' (t,x)\\
  x(0) &=& x(T)
\end{eqnarray*}
with $H(t,\cdot)$ a convex function of $x$, going to $+\infty$ when
$\left\|x\right\| \to \infty$.

%
\subsection{Autonomous Systems}
%
In this section, we will consider the case when the Hamiltonian $H(x)$
is autonomous. For the sake of simplicity, we shall also assume that it
is $C^{1}$.

We shall first consider the question of nontriviality, within the
general framework of
$\left(A_{\infty},B_{\infty}\right)$-subquadratic Hamiltonians. In
the second subsection, we shall look into the special case when $H$ is
$\left(0,b_{\infty}\right)$-subquadratic,
and we shall try to derive additional information.
%
\subsubsection{The General Case: Nontriviality.}
%
We assume that $H$ is
$\left(A_{\infty},B_{\infty}\right)$-sub\-qua\-dra\-tic at infinity,
for some constant symmetric matrices $A_{\infty}$ and $B_{\infty}$,
with $B_{\infty}-A_{\infty}$ positive definite. Set:
\begin{eqnarray}
\gamma :&=&{\rm smallest\ eigenvalue\ of}\ \ B_{\infty} - A_{\infty} \\
  \lambda : &=& {\rm largest\ negative\ eigenvalue\ of}\ \
  J \frac{d}{dt} +A_{\infty}\ .
\end{eqnarray}

Theorem~\ref{ghou:pre} tells us that if $\lambda +\gamma < 0$, the
boundary-value problem:
\begin{equation}
\begin{array}{rcl}
  \dot{x}&=&JH' (x)\\
  x(0)&=&x (T)
\end{array}
\end{equation}
has at least one solution
$\overline{x}$, which is found by minimizing the dual
action functional:
\begin{equation}
  \psi (u) = \int_{o}^{T} \left[\frac{1}{2}
  \left(\Lambda_{o}^{-1} u,u\right) + N^{\ast} (-u)\right] dt
\end{equation}
on the range of $\Lambda$, which is a subspace $R (\Lambda)_{L}^{2}$
with finite codimension. Here
\begin{equation}
  N(x) := H(x) - \frac{1}{2} \left(A_{\infty} x,x\right)
\end{equation}
is a convex function, and
\begin{equation}
  N(x) \le \frac{1}{2}
  \left(\left(B_{\infty} - A_{\infty}\right) x,x\right)
  + c\ \ \ \forall x\ .
\end{equation}

%
\begin{proposition}
Assume $H'(0)=0$ and $ H(0)=0$. Set:
\begin{equation}
  \delta := \liminf_{x\to 0} 2 N (x) \left\|x\right\|^{-2}\ .
  \label{eq:one}
\end{equation}

If $\gamma < - \lambda < \delta$,
the solution $\overline{u}$ is non-zero:
\begin{equation}
  \overline{x} (t) \ne 0\ \ \ \forall t\ .
\end{equation}
\end{proposition}
%
\begin{proof}
Condition (\ref{eq:one}) means that, for every
$\delta ' > \delta$, there is some $\varepsilon > 0$ such that
\begin{equation}
  \left\|x\right\| \le \varepsilon \Rightarrow N (x) \le
  \frac{\delta '}{2} \left\|x\right\|^{2}\ .
\end{equation}

It is an exercise in convex analysis, into which we shall not go, to
show that this implies that there is an $\eta > 0$ such that
\begin{equation}
  f\left\|x\right\| \le \eta
  \Rightarrow N^{\ast} (y) \le \frac{1}{2\delta '}
  \left\|y\right\|^{2}\ .
  \label{eq:two}
\end{equation}

\begin{figure}
\vspace{2.5cm}
\caption{This is the caption of the figure displaying a white eagle and
a white horse on a snow field}
\end{figure}

Since $u_{1}$ is a smooth function, we will have
$\left\|hu_{1}\right\|_\infty \le \eta$
for $h$ small enough, and inequality (\ref{eq:two}) will hold,
yielding thereby:
\begin{equation}
  \psi (hu_{1}) \le \frac{h^{2}}{2}
  \frac{1}{\lambda} \left\|u_{1} \right\|_{2}^{2} + \frac{h^{2}}{2}
  \frac{1}{\delta '} \left\|u_{1}\right\|^{2}\ .
\end{equation}

If we choose $\delta '$ close enough to $\delta$, the quantity
$\left(\frac{1}{\lambda} + \frac{1}{\delta '}\right)$
will be negative, and we end up with
\begin{equation}
  \psi (hu_{1}) < 0\ \ \ \ \ {\rm for}\ \ h\ne 0\ \ {\rm small}\ .
\end{equation}

On the other hand, we check directly that $\psi (0) = 0$. This shows
that 0 cannot be a minimizer of $\psi$, not even a local one.
So $\overline{u} \ne 0$ and
$\overline{u} \ne \Lambda_{o}^{-1} (0) = 0$. \qed
\end{proof}
%
\begin{corollary}
Assume $H$ is $C^{2}$ and
$\left(a_{\infty},b_{\infty}\right)$-subquadratic at infinity. Let
$\xi_{1},\allowbreak\dots,\allowbreak\xi_{N}$  be the
equilibria, that is, the solutions of $H' (\xi ) = 0$.
Denote by $\omega_{k}$
the smallest eigenvalue of $H'' \left(\xi_{k}\right)$, and set:
\begin{equation}
  \omega : = {\rm Min\,} \left\{\omega_{1},\dots,\omega_{k}\right\}\ .
\end{equation}
If:
\begin{equation}
  \frac{T}{2\pi} b_{\infty} <
  - E \left[- \frac{T}{2\pi}a_{\infty}\right] <
  \frac{T}{2\pi}\omega
  \label{eq:three}
\end{equation}
then minimization of $\psi$ yields a non-constant $T$-periodic solution
$\overline{x}$.
\end{corollary}
%

We recall once more that by the integer part $E [\alpha ]$ of
$\alpha \in \bbbr$, we mean the $a\in \bbbz$
such that $a< \alpha \le a+1$. For instance,
if we take $a_{\infty} = 0$, Corollary 2 tells
us that $\overline{x}$ exists and is
non-constant provided that:

\begin{equation}
  \frac{T}{2\pi} b_{\infty} < 1 < \frac{T}{2\pi}
\end{equation}
or
\begin{equation}
  T\in \left(\frac{2\pi}{\omega},\frac{2\pi}{b_{\infty}}\right)\ .
  \label{eq:four}
\end{equation}

%
\begin{proof}
The spectrum of $\Lambda$ is $\frac{2\pi}{T} \bbbz +a_{\infty}$. The
largest negative eigenvalue $\lambda$ is given by
$\frac{2\pi}{T}k_{o} +a_{\infty}$,
where
\begin{equation}
  \frac{2\pi}{T}k_{o} + a_{\infty} < 0
  \le \frac{2\pi}{T} (k_{o} +1) + a_{\infty}\ .
\end{equation}
Hence:
\begin{equation}
  k_{o} = E \left[- \frac{T}{2\pi} a_{\infty}\right] \ .
\end{equation}

The condition $\gamma < -\lambda < \delta$ now becomes:
\begin{equation}
  b_{\infty} - a_{\infty} <
  - \frac{2\pi}{T} k_{o} -a_{\infty} < \omega -a_{\infty}
\end{equation}
which is precisely condition (\ref{eq:three}).\qed
\end{proof}
%

\begin{lemma}
Assume that $H$ is $C^{2}$ on $\bbbr^{2n} \setminus \{ 0\}$ and
that $H'' (x)$ is non-de\-gen\-er\-ate for any $x\ne 0$. Then any local
minimizer $\widetilde{x}$ of $\psi$ has minimal period $T$.
\end{lemma}
%
\begin{proof}
We know that $\widetilde{x}$, or
$\widetilde{x} + \xi$ for some constant $\xi
\in \bbbr^{2n}$, is a $T$-periodic solution of the Hamiltonian system:
\begin{equation}
  \dot{x} = JH' (x)\ .
\end{equation}

There is no loss of generality in taking $\xi = 0$. So
$\psi (x) \ge \psi (\widetilde{x} )$
for all $\widetilde{x}$ in some neighbourhood of $x$ in
$W^{1,2} \left(\bbbr / T\bbbz ; \bbbr^{2n}\right)$.

But this index is precisely the index
$i_{T} (\widetilde{x} )$ of the $T$-periodic
solution $\widetilde{x}$ over the interval
$(0,T)$, as defined in Sect.~2.6. So
\begin{equation}
  i_{T} (\widetilde{x} ) = 0\ .
  \label{eq:five}
\end{equation}

Now if $\widetilde{x}$ has a lower period, $T/k$ say,
we would have, by Corollary 31:
\begin{equation}
  i_{T} (\widetilde{x} ) =
  i_{kT/k}(\widetilde{x} ) \ge
  ki_{T/k} (\widetilde{x} ) + k-1 \ge k-1 \ge 1\ .
\end{equation}

This would contradict (\ref{eq:five}), and thus cannot happen.\qed
\end{proof}
%
\paragraph{Notes and Comments.}
The results in this section are a
refined version of \cite{smit:wat};
the minimality result of Proposition
14 was the first of its kind.

To understand the nontriviality conditions, such as the one in formula
(\ref{eq:four}), one may think of a one-parameter family
$x_{T}$, $T\in \left(2\pi\omega^{-1}, 2\pi b_{\infty}^{-1}\right)$
of periodic solutions, $x_{T} (0) = x_{T} (T)$,
with $x_{T}$ going away to infinity when $T\to 2\pi \omega^{-1}$,
which is the period of the linearized system at 0.

\begin{table}
\caption{This is the example table taken out of {\it The
\TeX{}book,} p.\,246}
\begin{center}
\begin{tabular}{r@{\quad}rl}
\hline
\multicolumn{1}{l}{\rule{0pt}{12pt}
                   Year}&\multicolumn{2}{l}{World population}\\[2pt]
\hline\rule{0pt}{12pt}
8000 B.C.  &     5,000,000& \\
  50 A.D.  &   200,000,000& \\
1650 A.D.  &   500,000,000& \\
1945 A.D.  & 2,300,000,000& \\
1980 A.D.  & 4,400,000,000& \\[2pt]
\hline
\end{tabular}
\end{center}
\end{table}
%
\begin{theorem} [Ghoussoub-Preiss]\label{ghou:pre}
Assume $H(t,x)$ is
$(0,\varepsilon )$-subquadratic at
infinity for all $\varepsilon > 0$, and $T$-periodic in $t$
\begin{equation}
  H (t,\cdot )\ \ \ \ \ {\rm is\ convex}\ \ \forall t
\end{equation}
\begin{equation}
  H (\cdot ,x)\ \ \ \ \ {\rm is}\ \ T{\rm -periodic}\ \ \forall x
\end{equation}
\begin{equation}
  H (t,x)\ge n\left(\left\|x\right\|\right)\ \ \ \ \
  {\rm with}\ \ n (s)s^{-1}\to \infty\ \ {\rm as}\ \ s\to \infty
\end{equation}
\begin{equation}
  \forall \varepsilon > 0\ ,\ \ \ \exists c\ :\
  H(t,x) \le \frac{\varepsilon}{2}\left\|x\right\|^{2} + c\ .
\end{equation}

Assume also that $H$ is $C^{2}$, and $H'' (t,x)$ is positive definite
everywhere. Then there is a sequence $x_{k}$, $k\in \bbbn$, of
$kT$-periodic solutions of the system
\begin{equation}
  \dot{x} = JH' (t,x)
\end{equation}
such that, for every $k\in \bbbn$, there is some $p_{o}\in\bbbn$ with:
\begin{equation}
  p\ge p_{o}\Rightarrow x_{pk} \ne x_{k}\ .
\end{equation}
\qed
\end{theorem}
%
\begin{example} [{{\rm External forcing}}]
Consider the system:
\begin{equation}
  \dot{x} = JH' (x) + f(t)
\end{equation}
where the Hamiltonian $H$ is
$\left(0,b_{\infty}\right)$-subquadratic, and the
forcing term is a distribution on the circle:
\begin{equation}
  f = \frac{d}{dt} F + f_{o}\ \ \ \ \
  {\rm with}\ \ F\in L^{2} \left(\bbbr / T\bbbz; \bbbr^{2n}\right)\ ,
\end{equation}
where $f_{o} : = T^{-1}\int_{o}^{T} f (t) dt$. For instance,
\begin{equation}
  f (t) = \sum_{k\in \bbbn} \delta_{k} \xi\ ,
\end{equation}
where $\delta_{k}$ is the Dirac mass at $t= k$ and
$\xi \in \bbbr^{2n}$ is a
constant, fits the prescription. This means that the system
$\dot{x} = JH' (x)$ is being excited by a
series of identical shocks at interval $T$.
\end{example}
%
\begin{definition}
Let $A_{\infty} (t)$ and $B_{\infty} (t)$ be symmetric
operators in $\bbbr^{2n}$, depending continuously on
$t\in [0,T]$, such that
$A_{\infty} (t) \le B_{\infty} (t)$ for all $t$.

A Borelian function
$H: [0,T]\times \bbbr^{2n} \to \bbbr$
is called
$\left(A_{\infty} ,B_{\infty}\right)$-{\it subquadratic at infinity}
if there exists a function $N(t,x)$ such that:
\begin{equation}
  H (t,x) = \frac{1}{2} \left(A_{\infty} (t) x,x\right) + N(t,x)
\end{equation}
\begin{equation}
  \forall t\ ,\ \ \ N(t,x)\ \ \ \ \
  {\rm is\ convex\ with\  respect\  to}\ \ x
\end{equation}
\begin{equation}
  N(t,x) \ge n\left(\left\|x\right\|\right)\ \ \ \ \
  {\rm with}\ \ n(s)s^{-1}\to +\infty\ \ {\rm as}\ \ s\to +\infty
\end{equation}
\begin{equation}
  \exists c\in \bbbr\ :\ \ \ H (t,x) \le
  \frac{1}{2} \left(B_{\infty} (t) x,x\right) + c\ \ \ \forall x\ .
\end{equation}

If $A_{\infty} (t) = a_{\infty} I$ and
$B_{\infty} (t) = b_{\infty} I$, with
$a_{\infty} \le b_{\infty} \in \bbbr$,
we shall say that $H$ is
$\left(a_{\infty},b_{\infty}\right)$-subquadratic
at infinity. As an example, the function
$\left\|x\right\|^{\alpha}$, with
$1\le \alpha < 2$, is $(0,\varepsilon )$-subquadratic at infinity
for every $\varepsilon > 0$. Similarly, the Hamiltonian
\begin{equation}
H (t,x) = \frac{1}{2} k \left\|k\right\|^{2} +\left\|x\right\|^{\alpha}
\end{equation}
is $(k,k+\varepsilon )$-subquadratic for every $\varepsilon > 0$.
Note that, if $k<0$, it is not convex.
\end{definition}
%

\paragraph{Notes and Comments.}
The first results on subharmonics were
obtained by Rabinowitz in \cite{fo:kes:nic:tue}, who showed the existence of
infinitely many subharmonics both in the subquadratic and superquadratic
case, with suitable growth conditions on $H'$. Again the duality
approach enabled Clarke and Ekeland in \cite{may:ehr:stein} to treat the
same problem in the convex-subquadratic case, with growth conditions on
$H$ only.

Recently, Michalek and Tarantello (see \cite{fost:kes} and \cite{czaj:fitz})
have obtained lower bound on the number of subharmonics of period $kT$,
based on symmetry considerations and on pinching estimates, as in
Sect.~5.2 of this article.

%
% ---- Bibliography ----
%
\begin{thebibliography}{6}
%

\bibitem {smit:wat}
Smith, T.F., Waterman, M.S.: Identification of common molecular subsequences.
J. Mol. Biol. 147, 195?197 (1981). \url{doi:10.1016/0022-2836(81)90087-5}

\bibitem {may:ehr:stein}
May, P., Ehrlich, H.-C., Steinke, T.: ZIB structure prediction pipeline:
composing a complex biological workflow through web services.
In: Nagel, W.E., Walter, W.V., Lehner, W. (eds.) Euro-Par 2006.
LNCS, vol. 4128, pp. 1148?1158. Springer, Heidelberg (2006).
\url{doi:10.1007/11823285_121}

\bibitem {fost:kes}
Foster, I., Kesselman, C.: The Grid: Blueprint for a New Computing Infrastructure.
Morgan Kaufmann, San Francisco (1999)

\bibitem {czaj:fitz}
Czajkowski, K., Fitzgerald, S., Foster, I., Kesselman, C.: Grid information services
for distributed resource sharing. In: 10th IEEE International Symposium
on High Performance Distributed Computing, pp. 181?184. IEEE Press, New York (2001).
\url{doi: 10.1109/HPDC.2001.945188}

\bibitem {fo:kes:nic:tue}
Foster, I., Kesselman, C., Nick, J., Tuecke, S.: The physiology of the grid: an open grid services architecture for distributed systems integration. Technical report, Global Grid
Forum (2002)

\bibitem {onlyurl}
National Center for Biotechnology Information. \url{http://www.ncbi.nlm.nih.gov}

\end{thebibliography}
\end{document}

### 2025-02-05 sis2025/LaTex+Package/styles/paper-sis-template.tex
cose

%%%%%%%%%%%%%%%%%%%% author.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% sample root file for your "contribution" to a proceedings volume
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%% Springer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{svproc}
%
% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%

% to typeset URLs, URIs, and DOIs
\usepackage{url}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}
\def\UrlFont{\rmfamily}

\begin{document}
\mainmatter              % start of a contribution
%
\title{How much is too much? Item Response Theory procedures to shorten tests}
%
\titlerunning{Hamiltonian Mechanics}  % abbreviated title (for running head)
%                                     also used for the TOC unless
%                                     \toctitle is used
%
\author{Ottavia M. Epifania\inst{1} and Livio Finos\inst{2}}
%
\authorrunning{Epifania \& Finos} % abbreviated author list (for running head)
%
%%%% list of authors for the TOC (use if author list has to be modified)
\tocauthor{Ottavia M. Epifania, Livio Finos}
%
\institute{Department of Psychology and Cognitive Science, University of Trento, IT\\
\email{ottavia.epifania@unitn.it}
\and
Universit\'{e} de Paris-Sud,
Laboratoire d'Analyse Num\'{e}rique, B\^{a}timent 425,\\
F-91405 Orsay Cedex, France}

\maketitle              % typeset the title of the contribution

\begin{abstract}
The abstract should summarize the contents of the paper
using at least 70 and at most 150 words. It will be set in 9-point
font size and be inset 1.0 cm from the right and left margins.
There will be two blank lines before and after the Abstract. \dots
% We would like to encourage you to list your keywords within
% the abstract section using the \keywords{...} command.
\keywords{Item response theory, careless error, information functions, short test forms}
\end{abstract}
%
\section{Introduction}
%
As a general rule of thumb, the higher the number of items in a test, the better the measurement in terms of validity and reliability. However, there is a trade-off between the number of administered items and the response quality (giuro che ho della letteratura in merito). Quindi non torturiamo le persone che dopo di un po' non ne possono più. Item Response Theory (IRT) provides an ideal framework for shortening existing tests (or for developing tests from item banks) given the detailed information that they provide with respect to the measurement precision of each item considering different levels of the latent trait. In this contribution, we present a new algorithm for shortening tests that take into accounts the number of administered items by considering the ``tiredness'' of the respondents for each of the items included in the short test form (STF). The performance of the algorithm in retrieving an ideal target information function (i.e., the measurement precision that would be obtained by administering all the items in a test if the respondents would never get tired) is investigated in a simulation study. \color{red} il concetto c'è mancano le parole \normalcolor

\section{Item response theory e mortacci}

In Item Response Theory (IRT) models for dichotomous responses (e.g., correct vs. incorrect), the probability of observing a correct response on item $i$ by person $p$ depends on both the charcteristics of the respondent (as described by their latent trait level, $\theta_p$) and on the characteristics of the item, which can be described by different parameters. IRT models differentiate according to the number of parameters used for describing the characteristics of the items. According to the 4-parameter logistic model (4-PL), the probability of a correct can be formalized as:

\begin{equation}
	P(x_{pi}= 1| \theta_p, b_i, a_i, c_i, d_i) = c_i + (d_i -c_i) + \dfrac{\exp[a_i(\theta_p - b_i)]}{1 + \exp[a_i(\theta_p - b_i)]},
\end{equation}
where $\theta_p$ is the latent trait level of person $p$, $b_i$ is the location of the item on the latent trait (i.e., difficulty parameter, the higher the value, the higher the difficulty of the item), $a_i$ describes the ability of $i$ to discriminate between respondents with different latent trait levels (i.e.,discrimination parameter, the higher the value, the higher the discrimination ability of the item), and $c_i$ and $d_i$ describe the probability of observing a correct response when $\theta \to - \infty$ and $\theta \to +\infty$, respectively. 
When $\theta \to - \infty$, the probability of observing a correct response should tend to 0. Likewise, when $\theta \rightarrow +\infty$, the probability of observing a correct response should tend to 1. 
However, there might be instances where respondents with $\theta$ levels below the difficulty of the item, whom are hence expected not to respond correctly, might provide the correct response out of luck. The lucky guess parameter $c_i$ describes the probability of endorsing the item even if the $\theta$ level is below the difficulty of the item, such that the probability of observing a correct response for $\theta \to - \infty$ tends to $c_i$ instead of 0. 
The same but inverse consideration applies for the upper asymptote that describes the probability of giving the correct response for $\theta \to + \infty$. The $d_i$ parameter describes the probability of not endorsing the item given that the latent trait is above the location of the item, such that the probability of observing a correct response for $\theta \to + \infty$ tends to $d_i$ instead of 1.

By constraining $\forall i \in B, \, d_i = 1$ (where $B$ is the set of items in a set), the 3-Parameter logistic (3-PL) model is obtained. From 3-PL, the 2-parameter logistic model (2-PL) is obtained by constraining $\forall i \in B, \, c_i = 0$, and the 1-parameter logistic model (1-PL, equivalent to the Rasch model) is obtained by constraining $\forall i \in B, \, a_i = 1$.

\subsection{Information Functions}

\section{Simulation study}
Va detto da qualche parte che:

- La stanchezza dei soggetti viene operazionalizzata come probabilità di non careless error (va beh l'asintoto)

- la tif target è definita come forma ideale dell'informatività che si avrebbe se le persone non si stancassero mai

- la funzione di stanchezza è quella che mi ha dato chatgpt

- va descritto l'algoritmo e va descritto anche Frank (Frank ha solo un passaggio in meno rispetto a Leon perché non considera la stanchezza, basta descrivere leon e poi dire che Frank fa la stessa roba ma non mette la penalizzazione)

%\begin{table}
%\caption{This is the example table taken out of {\it The
%\TeX{}book,} p.\,246}
%\begin{center}
%\begin{tabular}{r@{\quad}rl}
%\hline
%\multicolumn{1}{l}{\rule{0pt}{12pt}
%                   Year}&\multicolumn{2}{l}{World population}\\[2pt]
%\hline\rule{0pt}{12pt}
%8000 B.C.  &     5,000,000& \\
%  50 A.D.  &   200,000,000& \\
%1650 A.D.  &   500,000,000& \\
%1945 A.D.  & 2,300,000,000& \\
%1980 A.D.  & 4,400,000,000& \\[2pt]
%\hline
%\end{tabular}
%\end{center}
%\end{table}
%%
%\begin{theorem} [Ghoussoub-Preiss]\label{ghou:pre}
%Assume $H(t,x)$ is
%$(0,\varepsilon )$-subquadratic at
%infinity for all $\varepsilon > 0$, and $T$-periodic in $t$
%\begin{equation}
%  H (t,\cdot )\ \ \ \ \ {\rm is\ convex}\ \ \forall t
%\end{equation}
%\begin{equation}
%  H (\cdot ,x)\ \ \ \ \ {\rm is}\ \ T{\rm -periodic}\ \ \forall x
%\end{equation}
%\begin{equation}
%  H (t,x)\ge n\left(\left\|x\right\|\right)\ \ \ \ \
%  {\rm with}\ \ n (s)s^{-1}\to \infty\ \ {\rm as}\ \ s\to \infty
%\end{equation}
%\begin{equation}
%  \forall \varepsilon > 0\ ,\ \ \ \exists c\ :\
%  H(t,x) \le \frac{\varepsilon}{2}\left\|x\right\|^{2} + c\ .
%\end{equation}
%
%Assume also that $H$ is $C^{2}$, and $H'' (t,x)$ is positive definite
%everywhere. Then there is a sequence $x_{k}$, $k\in \bbbn$, of
%$kT$-periodic solutions of the system
%\begin{equation}
%  \dot{x} = JH' (t,x)
%\end{equation}
%such that, for every $k\in \bbbn$, there is some $p_{o}\in\bbbn$ with:
%\begin{equation}
%  p\ge p_{o}\Rightarrow x_{pk} \ne x_{k}\ .
%\end{equation}
%\qed
%\end{theorem}
%%
%\begin{example} [{{\rm External forcing}}]
%Consider the system:
%\begin{equation}
%  \dot{x} = JH' (x) + f(t)
%\end{equation}
%where the Hamiltonian $H$ is
%$\left(0,b_{\infty}\right)$-subquadratic, and the
%forcing term is a distribution on the circle:
%\begin{equation}
%  f = \frac{d}{dt} F + f_{o}\ \ \ \ \
%  {\rm with}\ \ F\in L^{2} \left(\bbbr / T\bbbz; \bbbr^{2n}\right)\ ,
%\end{equation}
%where $f_{o} : = T^{-1}\int_{o}^{T} f (t) dt$. For instance,
%\begin{equation}
%  f (t) = \sum_{k\in \bbbn} \delta_{k} \xi\ ,
%\end{equation}
%where $\delta_{k}$ is the Dirac mass at $t= k$ and
%$\xi \in \bbbr^{2n}$ is a
%constant, fits the prescription. This means that the system
%$\dot{x} = JH' (x)$ is being excited by a
%series of identical shocks at interval $T$.
%\end{example}
%%
%\begin{definition}
%Let $A_{\infty} (t)$ and $B_{\infty} (t)$ be symmetric
%operators in $\bbbr^{2n}$, depending continuously on
%$t\in [0,T]$, such that
%$A_{\infty} (t) \le B_{\infty} (t)$ for all $t$.
%
%A Borelian function
%$H: [0,T]\times \bbbr^{2n} \to \bbbr$
%is called
%$\left(A_{\infty} ,B_{\infty}\right)$-{\it subquadratic at infinity}
%if there exists a function $N(t,x)$ such that:
%\begin{equation}
%  H (t,x) = \frac{1}{2} \left(A_{\infty} (t) x,x\right) + N(t,x)
%\end{equation}
%\begin{equation}
%  \forall t\ ,\ \ \ N(t,x)\ \ \ \ \
%  {\rm is\ convex\ with\  respect\  to}\ \ x
%\end{equation}
%\begin{equation}
%  N(t,x) \ge n\left(\left\|x\right\|\right)\ \ \ \ \
%  {\rm with}\ \ n(s)s^{-1}\to +\infty\ \ {\rm as}\ \ s\to +\infty
%\end{equation}
%\begin{equation}
%  \exists c\in \bbbr\ :\ \ \ H (t,x) \le
%  \frac{1}{2} \left(B_{\infty} (t) x,x\right) + c\ \ \ \forall x\ .
%\end{equation}
%
%If $A_{\infty} (t) = a_{\infty} I$ and
%$B_{\infty} (t) = b_{\infty} I$, with
%$a_{\infty} \le b_{\infty} \in \bbbr$,
%we shall say that $H$ is
%$\left(a_{\infty},b_{\infty}\right)$-subquadratic
%at infinity. As an example, the function
%$\left\|x\right\|^{\alpha}$, with
%$1\le \alpha < 2$, is $(0,\varepsilon )$-subquadratic at infinity
%for every $\varepsilon > 0$. Similarly, the Hamiltonian
%\begin{equation}
%H (t,x) = \frac{1}{2} k \left\|k\right\|^{2} +\left\|x\right\|^{\alpha}
%\end{equation}
%is $(k,k+\varepsilon )$-subquadratic for every $\varepsilon > 0$.
%Note that, if $k<0$, it is not convex.
%\end{definition}
%%
%
%\paragraph{Notes and Comments.}
%The first results on subharmonics were
%obtained by Rabinowitz in \cite{fo:kes:nic:tue}, who showed the existence of
%infinitely many subharmonics both in the subquadratic and superquadratic
%case, with suitable growth conditions on $H'$. Again the duality
%approach enabled Clarke and Ekeland in \cite{may:ehr:stein} to treat the
%same problem in the convex-subquadratic case, with growth conditions on
%$H$ only.
%
%Recently, Michalek and Tarantello (see \cite{fost:kes} and \cite{czaj:fitz})
%have obtained lower bound on the number of subharmonics of period $kT$,
%based on symmetry considerations and on pinching estimates, as in
%Sect.~5.2 of this article.

%
% ---- Bibliography ----
%
\begin{thebibliography}{6}
%

\bibitem {smit:wat}
Smith, T.F., Waterman, M.S.: Identification of common molecular subsequences.
J. Mol. Biol. 147, 195?197 (1981). \url{doi:10.1016/0022-2836(81)90087-5}

\bibitem {may:ehr:stein}
May, P., Ehrlich, H.-C., Steinke, T.: ZIB structure prediction pipeline:
composing a complex biological workflow through web services.
In: Nagel, W.E., Walter, W.V., Lehner, W. (eds.) Euro-Par 2006.
LNCS, vol. 4128, pp. 1148?1158. Springer, Heidelberg (2006).
\url{doi:10.1007/11823285_121}

\bibitem {fost:kes}
Foster, I., Kesselman, C.: The Grid: Blueprint for a New Computing Infrastructure.
Morgan Kaufmann, San Francisco (1999)

\bibitem {czaj:fitz}
Czajkowski, K., Fitzgerald, S., Foster, I., Kesselman, C.: Grid information services
for distributed resource sharing. In: 10th IEEE International Symposium
on High Performance Distributed Computing, pp. 181?184. IEEE Press, New York (2001).
\url{doi: 10.1109/HPDC.2001.945188}

\bibitem {fo:kes:nic:tue}
Foster, I., Kesselman, C., Nick, J., Tuecke, S.: The physiology of the grid: an open grid services architecture for distributed systems integration. Technical report, Global Grid
Forum (2002)

\bibitem {onlyurl}
National Center for Biotechnology Information. \url{http://www.ncbi.nlm.nih.gov}

\end{thebibliography}
\end{document}

### 2025-02-05 sis2025/paper-sis-2025.tex
cose

--- 2025-02-05 sis2025/LaTex+Package/styles/paper-sis-template.tex
@@
-%%%%%%%%%%%%%%%%%%%% author.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% sample root file for your "contribution" to a proceedings volume
-%
-% Use this file as a template for your own input.
-%
-%%%%%%%%%%%%%%%% Springer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\documentclass[12pt, a4paper, titilepage]{article}
 
-\documentclass{svproc}
-%
-% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-
-% to typeset URLs, URIs, and DOIs
-\usepackage{url}
-\usepackage{graphicx}
 \usepackage{amsmath}
-\usepackage[utf8]{inputenc}
-\usepackage{xcolor}
-\def\UrlFont{\rmfamily}
+%opening
+\title{How much is too much? Item Response Theory procedures to shorten tests}
+\author{Ottavia M. Epifania\textsuperscript{1} \& Livio Finos\textsuperscript{2}}
 
 \begin{document}
-\mainmatter              % start of a contribution
-%
-\title{How much is too much? Item Response Theory procedures to shorten tests}
-%
-\titlerunning{Hamiltonian Mechanics}  % abbreviated title (for running head)
-%                                     also used for the TOC unless
-%                                     \toctitle is used
-%
-\author{Ottavia M. Epifania\inst{1} and Livio Finos\inst{2}}
-%
-\authorrunning{Epifania \& Finos} % abbreviated author list (for running head)
-%
-%%%% list of authors for the TOC (use if author list has to be modified)
-\tocauthor{Ottavia M. Epifania, Livio Finos}
-%
-\institute{Department of Psychology and Cognitive Science, University of Trento, IT\\
-\email{ottavia.epifania@unitn.it}
-\and
-Universit\'{e} de Paris-Sud,
-Laboratoire d'Analyse Num\'{e}rique, B\^{a}timent 425,\\
-F-91405 Orsay Cedex, France}
 
-\maketitle              % typeset the title of the contribution
+\maketitle
 
 \begin{abstract}
-The abstract should summarize the contents of the paper
-using at least 70 and at most 150 words. It will be set in 9-point
-font size and be inset 1.0 cm from the right and left margins.
-There will be two blank lines before and after the Abstract. \dots
-% We would like to encourage you to list your keywords within
-% the abstract section using the \keywords{...} command.
-\keywords{Item response theory, careless error, information functions, short test forms}
+The horrors persist, but so do I
 \end{abstract}
-%
+
 \section{Introduction}
-%
-As a general rule of thumb, the higher the number of items in a test, the better the measurement in terms of validity and reliability.
-However, there is a trade-off between the number of administered items and the response quality (giuro che ho della letteratura in merito).
-Quindi non torturiamo le persone che dopo di un po' non ne possono più.
-Item Response Theory (IRT) provides an ideal framework for shortening existing tests (or for developing tests from item banks) given the detailed information that they provide with respect to the measurement precision of each item considering different levels of the latent trait.
-In this contribution, we present a new algorithm for shortening tests that take into accounts the number of administered items by considering the ``tiredness'' of the respondents for each of the items included in the short test form (STF).
-The performance of the algorithm in retrieving an ideal target information function (i.e., the measurement precision that would be obtained by administering all the items in a test if the respondents would never get tired) is investigated in a simulation study.
-\color{red} il concetto c'è mancano le parole \normalcolor
 
-\section{Item response theory e mortacci}
-
-In Item Response Theory (IRT) models for dichotomous responses (e.g., correct vs.
+In Item Response Theory (IRT) models for dichotmous responses (e.g., correct vs.
 incorrect), the probability of observing a correct response on item $i$ by person $p$ depends on both the charcteristics of the respondent (as described by their latent trait level, $\theta_p$) and on the characteristics of the item, which can be described by different parameters.
@@
 \end{equation}
-where $\theta_p$ is the latent trait level of person $p$, $b_i$ is the location of the item on the latent trait (i.e., difficulty parameter, the higher the value, the higher the difficulty of the item), $a_i$ describes the ability of $i$ to discriminate between respondents with different latent trait levels (i.e.,discrimination parameter, the higher the value, the higher the discrimination ability of the item), and $c_i$ and $d_i$ describe the probability of observing a correct response when $\theta \to - \infty$ and $\theta \to +\infty$, respectively.
-When $\theta \to - \infty$, the probability of observing a correct response should tend to 0.
+where $\theta_p$ is the latent trait level of person $p$, $b_i$ is the location of the item on the latent trait (i.e., difficulty parameter, the higher the value, the higher the difficulty of the item), $a_i$ describes the ability of $i$ to discriminate between respondents with different latent trait levels (i.e.,discrimination parameter, the higher the value, the higher the discrimination ability of the item), and $c_i$ and $d_i$ describe the probability of observing a correct response when $\theta \rightarrow - \infty$ and $\theta \rightarrow +\infty$, respectively.
+When $\theta \rightarrow - \infty$, the probability of observing a correct response should tend to 0.
 Likewise, when $\theta \rightarrow +\infty$, the probability of observing a correct response should tend to 1.
 However, there might be instances where respondents with $\theta$ levels below the difficulty of the item, whom are hence expected not to respond correctly, might provide the correct response out of luck.
-The lucky guess parameter $c_i$ describes the probability of endorsing the item even if the $\theta$ level is below the difficulty of the item, such that the probability of observing a correct response for $\theta \to - \infty$ tends to $c_i$ instead of 0.
-The same but inverse consideration applies for the upper asymptote that describes the probability of giving the correct response for $\theta \to + \infty$.
-The $d_i$ parameter describes the probability of not endorsing the item given that the latent trait is above the location of the item, such that the probability of observing a correct response for $\theta \to + \infty$ tends to $d_i$ instead of 1.
+The lucky guess parameter $c_i$ describes the probability of endorsing the item even if the $\theta$ level is below the difficulty of the item, such the probability of observing a correct response for $\theta \rightarrow - \infty$ tends to $c_i$ instead of 0.
+The same but inverse consideration applies for the upper asymptote that describes the probability of giving the correct response for $\theta \rightarrow + \infty$.
 
-By constraining $\forall i \in B, \, d_i = 1$ (where $B$ is the set of items in a set), the 3-Parameter logistic (3-PL) model is obtained.
-From 3-PL, the 2-parameter logistic model (2-PL) is obtained by constraining $\forall i \in B, \, c_i = 0$, and the 1-parameter logistic model (1-PL, equivalent to the Rasch model) is obtained by constraining $\forall i \in B, \, a_i = 1$.
+Parameter $c_i$ is the probability of lucky guess (i.e., the probability of observing a correct response)
 
-\subsection{Information Functions}
+\section{Simulation Study}
 
-\section{Simulation study}
-Va detto da qualche parte che:
+\subsection{Simulation Design}
 
-- La stanchezza dei soggetti viene operazionalizzata come probabilità di non careless error (va beh l'asintoto)
+\section{Results}
 
-- la tif target è definita come forma ideale dell'informatività che si avrebbe se le persone non si stancassero mai
+\section{Final Remarks}
 
-- la funzione di stanchezza è quella che mi ha dato chatgpt
-
-- va descritto l'algoritmo e va descritto anche Frank (Frank ha solo un passaggio in meno rispetto a Leon perché non considera la stanchezza, basta descrivere leon e poi dire che Frank fa la stessa roba ma non mette la penalizzazione)
-
-%\begin{table}
-%\caption{This is the example table taken out of {\it The
-%\TeX{}book,} p.\,246}
-%\begin{center}
-%\begin{tabular}{r@{\quad}rl}
-%\hline
-%\multicolumn{1}{l}{\rule{0pt}{12pt}
-%                   Year}&\multicolumn{2}{l}{World population}\\[2pt]
-%\hline\rule{0pt}{12pt}
-%8000 B.C.  &     5,000,000& \\
-%  50 A.D.  &   200,000,000& \\
-%1650 A.D.  &   500,000,000& \\
-%1945 A.D.  & 2,300,000,000& \\
-%1980 A.D.  & 4,400,000,000& \\[2pt]
-%\hline
-%\end{tabular}
-%\end{center}
-%\end{table}
-%%
-%\begin{theorem} [Ghoussoub-Preiss]\label{ghou:pre}
-%Assume $H(t,x)$ is
-%$(0,\varepsilon )$-subquadratic at
-%infinity for all $\varepsilon > 0$, and $T$-periodic in $t$
-%\begin{equation}
-%  H (t,\cdot )\ \ \ \ \ {\rm is\ convex}\ \ \forall t
-%\end{equation}
-%\begin{equation}
-%  H (\cdot ,x)\ \ \ \ \ {\rm is}\ \ T{\rm -periodic}\ \ \forall x
-%\end{equation}
-%\begin{equation}
-%  H (t,x)\ge n\left(\left\|x\right\|\right)\ \ \ \ \
-%  {\rm with}\ \ n (s)s^{-1}\to \infty\ \ {\rm as}\ \ s\to \infty
-%\end{equation}
-%\begin{equation}
-%  \forall \varepsilon > 0\ ,\ \ \ \exists c\ :\
-%  H(t,x) \le \frac{\varepsilon}{2}\left\|x\right\|^{2} + c\ .
-%\end{equation}
-%
-%Assume also that $H$ is $C^{2}$, and $H'' (t,x)$ is positive definite
-%everywhere. Then there is a sequence $x_{k}$, $k\in \bbbn$, of
-%$kT$-periodic solutions of the system
-%\begin{equation}
-%  \dot{x} = JH' (t,x)
-%\end{equation}
-%such that, for every $k\in \bbbn$, there is some $p_{o}\in\bbbn$ with:
-%\begin{equation}
-%  p\ge p_{o}\Rightarrow x_{pk} \ne x_{k}\ .
-%\end{equation}
-%\qed
-%\end{theorem}
-%%
-%\begin{example} [{{\rm External forcing}}]
-%Consider the system:
-%\begin{equation}
-%  \dot{x} = JH' (x) + f(t)
-%\end{equation}
-%where the Hamiltonian $H$ is
-%$\left(0,b_{\infty}\right)$-subquadratic, and the
-%forcing term is a distribution on the circle:
-%\begin{equation}
-%  f = \frac{d}{dt} F + f_{o}\ \ \ \ \
-%  {\rm with}\ \ F\in L^{2} \left(\bbbr / T\bbbz; \bbbr^{2n}\right)\ ,
-%\end{equation}
-%where $f_{o} : = T^{-1}\int_{o}^{T} f (t) dt$. For instance,
-%\begin{equation}
-%  f (t) = \sum_{k\in \bbbn} \delta_{k} \xi\ ,
-%\end{equation}
-%where $\delta_{k}$ is the Dirac mass at $t= k$ and
-%$\xi \in \bbbr^{2n}$ is a
-%constant, fits the prescription. This means that the system
-%$\dot{x} = JH' (x)$ is being excited by a
-%series of identical shocks at interval $T$.
-%\end{example}
-%%
-%\begin{definition}
-%Let $A_{\infty} (t)$ and $B_{\infty} (t)$ be symmetric
-%operators in $\bbbr^{2n}$, depending continuously on
-%$t\in [0,T]$, such that
-%$A_{\infty} (t) \le B_{\infty} (t)$ for all $t$.
-%
-%A Borelian function
-%$H: [0,T]\times \bbbr^{2n} \to \bbbr$
-%is called
-%$\left(A_{\infty} ,B_{\infty}\right)$-{\it subquadratic at infinity}
-%if there exists a function $N(t,x)$ such that:
-%\begin{equation}
-%  H (t,x) = \frac{1}{2} \left(A_{\infty} (t) x,x\right) + N(t,x)
-%\end{equation}
-%\begin{equation}
-%  \forall t\ ,\ \ \ N(t,x)\ \ \ \ \
-%  {\rm is\ convex\ with\  respect\  to}\ \ x
-%\end{equation}
-%\begin{equation}
-%  N(t,x) \ge n\left(\left\|x\right\|\right)\ \ \ \ \
-%  {\rm with}\ \ n(s)s^{-1}\to +\infty\ \ {\rm as}\ \ s\to +\infty
-%\end{equation}
-%\begin{equation}
-%  \exists c\in \bbbr\ :\ \ \ H (t,x) \le
-%  \frac{1}{2} \left(B_{\infty} (t) x,x\right) + c\ \ \ \forall x\ .
-%\end{equation}
-%
-%If $A_{\infty} (t) = a_{\infty} I$ and
-%$B_{\infty} (t) = b_{\infty} I$, with
-%$a_{\infty} \le b_{\infty} \in \bbbr$,
-%we shall say that $H$ is
-%$\left(a_{\infty},b_{\infty}\right)$-subquadratic
-%at infinity. As an example, the function
-%$\left\|x\right\|^{\alpha}$, with
-%$1\le \alpha < 2$, is $(0,\varepsilon )$-subquadratic at infinity
-%for every $\varepsilon > 0$. Similarly, the Hamiltonian
-%\begin{equation}
-%H (t,x) = \frac{1}{2} k \left\|k\right\|^{2} +\left\|x\right\|^{\alpha}
-%\end{equation}
-%is $(k,k+\varepsilon )$-subquadratic for every $\varepsilon > 0$.
-%Note that, if $k<0$, it is not convex.
-%\end{definition}
-%%
-%
-%\paragraph{Notes and Comments.}
-%The first results on subharmonics were
-%obtained by Rabinowitz in \cite{fo:kes:nic:tue}, who showed the existence of
-%infinitely many subharmonics both in the subquadratic and superquadratic
-%case, with suitable growth conditions on $H'$. Again the duality
-%approach enabled Clarke and Ekeland in \cite{may:ehr:stein} to treat the
-%same problem in the convex-subquadratic case, with growth conditions on
-%$H$ only.
-%
-%Recently, Michalek and Tarantello (see \cite{fost:kes} and \cite{czaj:fitz})
-%have obtained lower bound on the number of subharmonics of period $kT$,
-%based on symmetry considerations and on pinching estimates, as in
-%Sect.~5.2 of this article.
-
-%
-% ---- Bibliography ----
-%
-\begin{thebibliography}{6}
-%
-
-\bibitem {smit:wat}
-Smith, T.F., Waterman, M.S.: Identification of common molecular subsequences.
-J. Mol. Biol. 147, 195?197 (1981). \url{doi:10.1016/0022-2836(81)90087-5}
-
-\bibitem {may:ehr:stein}
-May, P., Ehrlich, H.-C., Steinke, T.: ZIB structure prediction pipeline:
-composing a complex biological workflow through web services.
-In: Nagel, W.E., Walter, W.V., Lehner, W. (eds.) Euro-Par 2006.
-LNCS, vol. 4128, pp. 1148?1158. Springer, Heidelberg (2006).
-\url{doi:10.1007/11823285_121}
-
-\bibitem {fost:kes}
-Foster, I., Kesselman, C.: The Grid: Blueprint for a New Computing Infrastructure.
-Morgan Kaufmann, San Francisco (1999)
-
-\bibitem {czaj:fitz}
-Czajkowski, K., Fitzgerald, S., Foster, I., Kesselman, C.: Grid information services
-for distributed resource sharing. In: 10th IEEE International Symposium
-on High Performance Distributed Computing, pp. 181?184. IEEE Press, New York (2001).
-\url{doi: 10.1109/HPDC.2001.945188}
-
-\bibitem {fo:kes:nic:tue}
-Foster, I., Kesselman, C., Nick, J., Tuecke, S.: The physiology of the grid: an open grid services architecture for distributed systems integration. Technical report, Global Grid
-Forum (2002)
-
-\bibitem {onlyurl}
-National Center for Biotechnology Information. \url{http://www.ncbi.nlm.nih.gov}
-
-\end{thebibliography}
 \end{document}

### 2025-02-05 grafici-esempi-paper.R

@@ -1,0 +1,46 @@
+source("functions-new.R")
+library(tidyverse)
+item_sk = data.frame(b = c(-2, -2), 
+                     a = c(1.9, 2), 
+                     c = c(0,0),
+                     e = c(1,1))
+item_n = data.frame(b = c(-2.6, -1.5, -1, 0,0, 1, 1.5, 2.6), 
+                     a = c(1.7, 1.7, 1.7, 1.7,1.7, 1.7, 1.7, 1.7), 
+                     c = rep(0,8),
+                     e = rep(1,8))
+i_sk = item_info(item_sk, theta = seq(-4,4, length.out = 1500))
+i_n = item_info(item_n, theta = seq(-4,4, length.out = 1500))
+
+myinfo = data.frame(theta = seq(-4,4, length.out = 1500), 
+                    tif_sk = rowSums(i_sk), 
+                    tif_n = rowSums(i_n))
+
+ggplot(myinfo, 
+       aes(x = theta, y = tif_sk)) + geom_line(linewidth=1.2) + 
+  ylab("TIF-Target") + xlab(expression(theta)) + 
+  theme_classic() + 
+  theme(axis.text.x = element_text(size = 24), 
+        axis.text.y = element_blank(), 
+        axis.ticks.y = element_blank(), 
+        axis.title = element_text(size = 26)) +
+  scale_x_continuous(limits = c(-4, 4), 
+                     breaks = seq(-4, 4, by = 2))
+# Save the plot as a PDF with US legal dimensions
+ggsave(paste0(getwd(),"/paper/img/target_sk.pdf"), 
+       width = 8.5, height = 14, units = "in", dpi = 300)
+
+ggplot(myinfo, 
+       aes(x = theta, y = tif_n)) + geom_line(linewidth=1.2) + 
+  ylab("TIF-Target") + xlab(expression(theta)) + 
+  theme_classic() + 
+  theme(axis.text.x = element_text(size = 24), 
+        axis.text.y = element_blank(), 
+        axis.ticks.y = element_blank(), 
+        axis.title = element_text(size = 26)) +
+  scale_x_continuous(limits = c(-4, 4), 
+                     breaks = seq(-4, 4, by = 2))
+
+ggsave(paste0(getwd(),"/paper/img/target_n.pdf"), 
+       width = 8.5, height = 14, units = "in", dpi = 300)
+
+

### 2025-02-05 sis-2025.R

@@ -1,0 +1,131 @@
+# sis 2025 ------
+library(tidyverse)
+source("functions-new.R")
+leon = function(parameters, target, speed = 0.01) {
+  theta = target$theta
+  all_iifs = item_info(parameters, theta)
+  original_parameters = parameters
+  start_e = parameters$e
+  token = TRUE
+  mod_e = 1
+  j = 0
+  while (token == TRUE) {
+    j = j +1
+    # qui potrei fare che itero per tutte le colonne che non sono NA del mio dataframe di item 
+    # creo gli indici degli item nell'insieme A (gli available items)
+    if (all(which(is.na(parameters[, 1])) == FALSE) ) {
+      item_indexes = 1:nrow(parameters)
+      iif_stf = numeric(length(target$theta))
+    } else {
+      item_indexes = which(!is.na(parameters[,1]))
+    }
+    # adesso il ciclo for itera negli item indexes e calcola la PIF
+    difference = rep(NA, nrow(parameters))
+    for (i in item_indexes) {
+      if (length(item_indexes) == nrow(parameters)) {
+        pif = data.frame(all_iifs[,i]) 
+      } else {
+        # qui devo mdoficare all_iifs nel senso che le devo ricalcolare 
+        # però considerando la stanchezza
+        # so dire esattamente 
+        # CAMBIA QUI METTENDO CHE PESCA LA E DEGLI ITEM ORIGIANLI IN ABSE ALLA LORO POSIZIONE DI SOMMNISTRAZIONE 
+        # PER CUI ALL'I-ESIMA ITERAZIONE PRENDE LA STANCHEZZA DELL'ITEM SOMMINISTRATO PER I-ESIMO
+        # original_parameters$e = exp(-speed*(ncol(iif_stf)+1))
+        original_parameters$e = start_e[j]
+        # qui ora si può ottimizzare 
+        all_iifs = item_info(original_parameters, theta)
+        pif = data.frame(cbind(iif_stf, all_iifs[,i]))
+        pif = data.frame(rowMeans(pif))
+      }
+      difference[i] = mean(abs(target$mean_tif - pif)[,1])  
+      # qui scelgo un item temporaneo che è quello con la distanza minima
+    }
+    mod_e = c(mod_e, unique(original_parameters$e))
+    # qui trovo l'item che minimizza e lo metto in d
+    d_index = which(difference == min(difference, na.rm = T))
[…]

### 2025-02-05 tiredEstimate.R

@@ -187,6 +187,17 @@ for (i in 1:nrow(dataFixed)) {
                                       c = tired_q[j, "c"],tired_q[j, "e"]))
   }
 }
+library(lme4)
+dataFixed$sbj = 1:nrow(dataFixed)
+
+long = pivot_longer(dataFixed, 
+             cols = !sbj)
+
+m1 = glmer(value ~ (1|name) + (1|sbj), data = long, family = "binomial")
+summary(m1)
+plot( true_theta, ranef(m1)$sbj[,1])
+abline(0,1)
+
 prop = data.frame(item = c(names(colMeans(dataFixed)),names(colMeans(dataFixed))), 
            prop = c(colMeans(dataFixed), colMeans(data)), 
            data = c(rep("Fixed", n_item), rep("Clean", n_item)))

### 2025-02-10 sis2025/LaTex+Package/styles/paper-sis-template.tex
sis

@@
 
+The meausemrement precision of each item with respect to different levels of the latent trait can be expressed with the so-called \emph{item information functions} (IIFs), which for the 4-PL is formalized as:
+
+\begin{center}
+	Formula del 4-PL
+\end{center}
+
+The informativeness of each item is strongly influenced by the location of the item on the latent trait with respect to a specific latent trait level $\theta$, its discirminativity, and the probability of lucky guess and careless error.
+In absence of lucky guess and careless error, the IIF reaches its maximum when the location of the item $b_i$ matches the latent trait level $\theta$, and it decreases as the distance between $b_i$ and $\theta$ increases.
+Moreover, the higher the discrimination of the item $a_i$, the more informative the item.
+However, when the lucky guess and careless error are taken into account, the informativeness of the item decreases, and, most importantly, the maximum of the IIF does not corresponds to the item location on the latent trait and it is generally lower.
+
+The \emph{test information function} (TIF) is the sum of the IIFs, such that its shape (i.e., its informativeness with respect to different levels of the latent trait) and its height (i.e., the amount of information for different levels of the latent trait) depend on the distribution of the items on the latent trait.
+The more the items with high discrimination and low lucky guess and careless error parameters are spread throughout the latent trait, the more the test would be informative of different regions.
+The more the items have lucky guesses and careless errors, the less the TIF.
+
 \section{Simulation study}
+In this study, we operationalized the tiredeness of the individuals as the probability of committing careless error ($1- d_i$ QUESTA è LA PROBABILITà DI NON CARELESS ERROR DEVO SPIEGARE MEGLIO, mi sto incansiandno basta che alla fine sia coerente), such that the more the items in a test, the higher the probability of committing careless mistakes.
+The careless error probability is instrinsically related to the rank of the item in the test, and it increases as the position of the item in the test increases.
+It increases exponentially with the function SCRIVERE LA FUNZIONE, such that the first administered item has $d_i = 1$ (i.e., does not have a probability of observing an incorrect response given the latent trait level $\theta$)
+
 Va detto da qualche parte che:

### 2025-02-13 sis2025/LaTex+Package/styles/paper-sis-template.tex
update sis

@@
 \section{Simulation study}
-In this study, we operationalized the tiredeness of the individuals as the probability of committing careless error ($1- d_i$ QUESTA è LA PROBABILITà DI NON CARELESS ERROR DEVO SPIEGARE MEGLIO, mi sto incansiandno basta che alla fine sia coerente), such that the more the items in a test, the higher the probability of committing careless mistakes.
+In this study, we operationalized the tiredeness of the individuals as the probability of committing careless error ($1- d_i$ QUESTA è LA PROBABILITà DI NON CARELESS ERROR DEVO SPIEGARE MEGLIO, mi sto incansiandno basta che alla fine sia coerente), such that the more the items in a test, the higher the probability of careless error.
 The careless error probability is instrinsically related to the rank of the item in the test, and it increases as the position of the item in the test increases.
-It increases exponentially with the function SCRIVERE LA FUNZIONE, such that the first administered item has $d_i = 1$ (i.e., does not have a probability of observing an incorrect response given the latent trait level $\theta$)
+It increases exponentially with the function SCRIVERE LA FUNZIONE, such that the first administered item has $d_i = 1$ (i.e., does not have a probability of observing an incorrect response given the latent trait level $\theta$).
+
+The procedure is replicated 100 times.
+At each replica, a test of $B$ of 50 items with difficulty ($b_i \sim \mathcal{U}(-3, 3)$) discrimination ($a_i \sim \mathcal{U}(.90, 2)$) parameters drawn from uniform distributions is generated.
+Lucky
+guess and careless error parameters are constant, $c_i = 0, \forall i \in B$ and $d_i = 0, \forall i \in B$.
+The $TIF^*$ is generated as the mean TIF of all items in $B$, which describes the ideal TIF that one would obtain if respondents are administered with all the items without getting tired.
+
+A new test $B'$ is generated by keeping the item parameters equal to those in $B$, with the only exception of the careless error parameters, which are included as related to the rank of the item in the item bank with the function SCRIVERE LA FUNZIONE.
+The assumption is that the first administered item does not have a careless error probability ($d_{\text{1st}} = 1$) and it increases as the administration goes on.
+As such, the careless error probabilities associated to the second and third administered items are, respectively, $.99$ and $.98$.
+In this application, the maximum careless error probability associated to the last administered item is $.61$.
+
+Frank and Léon are applied to generate a STF able to recreate the $TIF^*$.
+Both algorithm are applied considering the items in $B'$.
+While both algorithms are able to consider the careless error parameters in the computation of the IIFs, only Léon actually accounts for the number of items included in the STF.
+NON SO COSA STO DICENDO.
+devo controllare il codice perché ora non capisco.
+se anche frank calcola la iif considerando la careless error non capisco in che modo dovrebbe differenziarsi da leon ma effettivmente i risultati sono peggiori.
 
@@
 - va descritto l'algoritmo e va descritto anche Frank (Frank ha solo un passaggio in meno rispetto a Leon perché non considera la stanchezza, basta descrivere leon e poi dire che Frank fa la stessa roba ma non mette la penalizzazione)
+
+\section{Results}
+
+\begin{table}
+	\centering
+	\caption{\label{tab:summary} questa è una tabella, cominciamo}
+	\begin{tabular}{l ccc}
+		\hline
+	Procedure	&	M			&	Min	&	Max	\\\hline
+	All items	& $	0.07\pm	0.03$ &	$< 0.005$	&	0.13	\\
+	Frank	& $	0.03	\pm	0.03	$ &	$<0.001$	&	0.14	\\
+	Léon	& $	0.03	\pm	0.02	$ &	$<0.001$	&	0.1	\\
+	\hline	
+	\end{tabular}
+\end{table}
 

### 2025-02-13 sis-2025.R

@@ -99,7 +99,13 @@ resFrank = list()
 resLeon = list()
 # qui dentro devo mettere solo la TIF calcolata sui 50 item con stanchezza
 resAllitems = list()
-
+time = data.frame(iteration = 1:100, 
+                  start_all = numeric(100), 
+                  end_all = numeric(100), 
+                  start_frank = numeric(100), 
+                  end_frank = numeric(100), 
+                  start_leon = numeric(100), 
+                  end_leon = numeric(100))
 for (i in 1:100){
   set.seed(1312+i)
   q[[i]] = data.frame(b = runif(n_item, -3, 3), 
@@ -113,19 +119,110 @@ for (i in 1:100){
   q_tired[[i]] = q[[i]]
   q_tired[[i]]$e =  exp(-0.01*(0:(nrow(q_tired[[i]])-1)))
   temp_tired_iifs = item_info(q_tired[[i]], theta = theta)
+  time[i, "start_all"] = Sys.time()
   resAllitems[[i]] = data.frame(theta = theta, 
                                 tif_all = rowMeans(temp_tired_iifs))
+  time[i, "end_all"] = Sys.time()
   # applico frank e leon 
+  time[i, "start_frank"] = Sys.time()
   resFrank[[i]] = frank(q_tired[[i]], tif[[i]])
+  time[i, "end_frank"] = Sys.time()
+  time[i, "start_leon"] = Sys.time()
   resLeon[[i]] = leon(q_tired[[i]], tif[[i]])
-  print(cat(paste("Replication", i)))
+  time[i, "end_leon"] = Sys.time()
+  print(paste("Replication", i))
 }
 # cose che posso fare
 # guardare la differenza simmetrica tra gl item selezionati dai due algfortimi 
 # calcolare la distanza media dalla TIF target (forse questa è la cosa migliore)
 colnames(resFrank[[1]]$iif_stf)[order(colnames(resFrank[[1]]$iif_stf))]
+for (i in 1:20) {
+  plot(theta, tif[[i]]$mean_tif, type = "l", main = i)
+  lines(theta, resAllitems[[i]]$tif_all, 
+        type = "l", col = "red")
+  lines(theta, rowMeans(resFrank[[i]]$iif_stf),
+        type = "l", col = "green")
+  lines(theta, rowMeans(resLeon[[i]]$iif_stf), 
+        type = "l", col = "royalblue")
+}
 
[…]

### 2025-02-17 paper/algorithms.tex
sis update

@@
 	\begin{LARGE}
-	The Good, the Bad, and the Ugly: \\ New Item Response Theory based algorithms for the development of short test forms
+ New Item Response Theory based algorithms for the development of short test forms
 	\end{LARGE}
@@
 	\begin{large}
-%		Ottavia M. Epifania, Pasquale Anselmi, and Egidio Robusto \\ 
-%		Department of Philosophy, Sociology, Education, and Applied Psychology, University of Padova
+		\doublespacing
+		Ottavia M. Epifania\textsuperscript{1}, Pasquale Anselmi\textsuperscript{2}, and Egidio Robusto\textsuperscript{2} \\ 	\vspace{1.5mm}
+		\textsuperscript{1} Department of Psychology and Cognitive Science, University of Trento, IT \\ \vspace{1.5mm}
+	\textsuperscript{2}	Department of Philosophy, Sociology, Education, and Applied Psychology, University of Padova, IT
 	\end{large}
@@
 \end{center}
-\begin{small}
 
-%	Ottavia M. Epifania \includegraphics[width=0.06\linewidth]{orcid.png} https://orcid.org/0000-0001-8552-568X
-%	
-%	Pasquale Anselmi \includegraphics[width=0.06\linewidth]{orcid.png} https://orcid.org/0000-0003-2982-7178 
-%	
-%	Egidio Robusto \includegraphics[width=0.06\linewidth]{orcid.png} https://orcid.org/0000-0002-7583-2587
+	Ottavia M. Epifania \includegraphics[width=0.06\linewidth]{orcid.png} https://orcid.org/0000-0001-8552-568X
 
+	Pasquale Anselmi \includegraphics[width=0.06\linewidth]{orcid.png} https://orcid.org/0000-0003-2982-7178
+
+	Egidio Robusto \includegraphics[width=0.06\linewidth]{orcid.png} https://orcid.org/0000-0002-7583-2587
+
+	\vspace{5mm}
 	The authors have no conflict of interest to disclose.
 
-	Correspondence concerning this article should be addressed to: Ottavia M. Epifania, Department of Philosophy, Sociology, Education, and Applied Psychology, Via Venezia 14, Padova, Italy.
-	E-Mail: ottavia.epifania@unipd.it \\
-\end{small}
+	\vspace{5mm}
+
+	Correspondence concerning this article should be addressed to: Ottavia M. Epifania, Department of Psychology and Cognitive Science, Corso Bettini 84, Rovereto, Trento, Italy. \\
+	E-Mail: ottavia.epifania@unitn.it \\
 
@@
 
+\begin{center}
+	\textbf{ New Item Response Theory-Based Algorithms for the Development of Short Test Forms}
+\end{center}
+
+\vspace{5mm}
+
 \begin{abstract}
@@
 This manuscript presents Item Response Theory-based algorithms for the development of short test forms (STFs) from full-length tests.
-All algorithms aim at minimizing both the number of items included in the STF and the minimum average distance from a test information target that describes the desired characteristics of the STF, denoted as test information function target (TIF-target).
-The algorithms differ according to the method used for the item inclusion in the STF at each iteration, while they share the same termination criterion.
+All algorithms aim at minimizing both the number of items included in the STF and the minimum average distance from a target test information target (TIF) that describes the desired characteristics of the STF, denoted as TIF-target.
+The algorithms differ according to the method used for including an item in the STF at each iteration, while they share the same termination criterion.
 The item selection is based on the ability of each item to reduce the distance from the TIF-target considering either one specific latent trait level defined at each iteration or the entire latent trait level.
@@
 \begin{center}
-	\textbf{The Good, the Bad, and the Ugly: New Item Response Theory-Based Algorithms for the Development of Short Test Forms}
+	\textbf{ New Item Response Theory-Based Algorithms for the Development of Short Test Forms}
 \end{center}
@@
 Item Response Theory (IRT) offers detailed insights into the measurement precision of individual items across varying levels of the latent trait, making it an ideal framework for test development \cite<e.g.,>{baker2017, van1987absolute}.
-By leveraging its robust analytical capabilities, IRT facilitates the construction of tailored assessments, such as tests designed from item banks or the derivation of short test forms (STFs) from existing assessments.
+By leveraging its robust analytical capabilities, IRT facilitates the construction of tests designed from item banks or the derivation of short test forms (STFs) from existing assessments.
 This flexibility ensures that tests can be optimized for specific purposes, populations, or contexts while maintaining precision and validity.
@@
 Therefore, the items may differ from one respondent to another.
-On the other hand, static STFs are composed of the same subset of items, which is chosen to maximize the measurement precision across all the administered respondents.
+On the other hand, static STFs are composed of the same subset of items, which is chosen to maximize the measurement precision across all the respondents.
 %The information on the measurement precision of each item can be exploited for the creation of ad-hoc STFs by selecting only those items that most precisely measure specific levels of the latent trait, in line with the aim of the assessment.
@@
 In common IRT procedures \cite<e.g.,>{chiesi, colledani2018, silvia}, the items  are selected for inclusion in the STF according to their measurement precision with respect to different levels of the latent trait that are of interest for the assessment.
-To pursue this aim, the information functions of all the items of the full-length test are inspected, and the items with the information functions best able to comply with the desired characteristics of the STF are selected for inclusion.
-Although this procedure offers high degrees of freedom (e.g., the number of items in the STF can be not specified in advance), it strongly relies on the expertise and subjectivity of the researchers, which lead to issues related to
+To pursue this aim, the information functions of all the items in the full-length test are inspected, and the items with the information functions best able to comply with the desired characteristics of the STF are selected for inclusion.
+Although this procedure offers high degrees of freedom (e.g., the number of items in the STF does not need to be specified in advance), it strongly relies on the expertise and subjectivity of the researchers, which lead to issues related to
 replicability.   
@@
 \section*{Item Response Theory and Information Functions}
-Different IRT models are available for the analyses of dichotomous responses, which differentiate according to the characteristics of the items that they take into account. 
+Different IRT models are available for the analysis of dichotomous responses, which differentiate according to the characteristics of the items that they take into account. 
 In this application, 
 the 2-Parameter Logistic model \cite<2-PL;>{birnbaum1968} is used as a reference, which considers item difficulty and item discrimination.
-According to this model, the probability of observing a positive response by person $p$ on item $i$ is formalized as:
+However, the presented approach can be applied to other IRT models that consider item discrimination.
+According to the 2-PL model, the probability of observing a positive response by person $p$ on item $i$ is formalized as:
 
@@
 \end{equation}
-where $\theta_p$ is the ability parameter of person $p$ (i.e., the latent trait level of $p$), $b_i$ is the difficulty parameter of item $i$ (i.e., the location of $i$ on the latent trait), and $a_i$ is the discrimination parameter of item $i$ (i.e., the ability of $i$ to distinguish respondents with different levels of $\theta$).
-The probability of observing a positive response changes as the distance between the ability of the person $\theta_p$ and the location of the item on the latent trait $b_i$ changes, such as it is of the 50\% when the ability of person $p$ matches the difficulty of item $i$.
+where $\theta_p$ is the ability parameter of person $p$ (i.e., the latent trait level of $p$), $b_i$ is the difficulty parameter of item $i$ (i.e., the location of $i$ on the latent trait), and $a_i$ is the discrimination parameter of item $i$ (i.e., the ability of $i$ to distinguish between respondents with different levels of $\theta$).
+The probability of observing a positive response changes as the distance between the ability of the person $\theta_p$ and the location of the item on the latent trait $b_i$ changes.
+This probability is .50 when the ability of person $p$ matches the difficulty of item $i$.
 
-The precision with which each item measures different levels of the latent trait is described by the \emph{item information function}, $\text{IIF}_i = a_i^2P(\theta, b_i, a_i)[1- P(\theta, b_i, a_i)]$.
-In the 2-PL, the IIF reaches its maximum when $\theta_p = b_i$.
-The precision with which the test as a whole measures the entire latent trait is expressed by the \emph{test information function}, which is the sum of the IIFs of all the items in a test or item bank, $\text{TIF} = \sum_{i \in B} \text{IIF}_i$ (where $B$ is the set of items in a test or in an item bank).
-Given the dependency between the location of the items on the latent trait, their discrimination parameters, and their informativeness with respect to different latent trait levels,  the shape and height of the TIF depends on the spread of the items along the latent trait continuum.
- Since the TIF is the sum of the IIFs, the higher the number of items in  test, the higher the TIF.
+Let $B$ denote the set of items in a test or in an item bank.
+The precision with which each item $i \in B$ measures different levels of the latent trait is described by the \emph{item information function}, $\text{IIF}_i = a_i^2P(x_{pi} = 1|\theta, b_i, a_i)[1- P(x_{pi} = 1|\theta, b_i, a_i)]$.
+In the 2-PL model, the IIF reaches its maximum when $\theta_p = b_i$.
+The precision with which the test as a whole measures the entire latent trait is expressed by the \emph{test information function}, which is the sum of the IIFs of all the items in a test or item bank, $\text{TIF} = \sum_{i \in B} \text{IIF}_i$.
+The shape and height of the TIF depends on the spread of the items along the latent
+trait continuum and on their discriminability.
+ Since the TIF is the sum of the IIFs, the higher the number of items in the test, the higher the TIF.
 Alternatively, a mean TIF can be computed by averaging for the number of items.
@@
 
-The three introduced algorithms aim at approximating as best as possible the desired characteristics of a test, as expressed by a target information function (TIF-target), by selecting the items best able to reduce the distance between the information function of the STF and the target one.
-Two of the algorithms (item locating algorithm -- ILA -- and item selecting algorithm -- ISA --) can be seen as the natural evolution of the $\theta$-target procedure in that they ground the item selection on the characteristics of each item with respect to a specific $\theta$ target, which is defined at each iteration as the latent trait level where the maximum distance between the two information functions is observed.
+The three introduced algorithms aim at approximating as best as possible the desired characteristics of a test, as expressed by a target information function (TIF-target), by selecting the items best able to reduce the distance between the information function of the provisional STF (pSTF) and the target one.
+Two of the algorithms (denoted as item locating algorithm -- ILA -- and item selecting algorithm -- ISA --) can be seen as the natural evolution of the $\theta$-target procedure in that they ground the item selection on the characteristics of each item with respect to a specific $\theta$ target, which is defined at each iteration as the latent trait level where the distance between the two information functions is maximum.
 The third one (Frank) overcomes the definition of the $\theta$ targets altogether by considering the entire latent trait for the item inclusion at each iteration.
@@
 By grounding the item selection on a specific $\theta$ target, ILA and ISA bring the two information functions closer considering only one latent trait level at the time. 
-On the other hand, by grounding the item selection on its contribution to the temporary information function, Frank bridges the gap between the two functions considering the entire latent trait. 
+On the other hand, by grounding the item selection on the contribution of each item to the temporary information function, Frank bridges the gap between the two functions considering the entire latent trait.
 %However, ILA and ISA attempt at bridging the gap between the two information functions considering one discrete level at the time, the $\theta$ target, while Frank considers the entire latent trait. 
@@
 
-The simulation study was run in \texttt{R}, version XX on a Windows 10 PC (DETTAGLI TECNICI SULLA RAM E ALTRE COSE).
+The simulation study was run in \texttt{R} \cite<Version 4.4.1.;>{rsoft} on a computer with an Intel Core i3-7100 @ 3.90 GHz processor, 8 GB of RAM, and a 64-bit Windows operating system.
 

### 2025-02-17 paper/coverLetter.tex
sis update

\documentclass[12pt]{letter}
\usepackage{geometry}
\geometry{left=1in, right=1in, top=1in, bottom=1in}

\begin{document}

	\begin{letter}{Editor-in-Chief of the Thoery \& Methodology Section\\ Psychometrika}

		\opening{Dear Theory \& Methodology Editors,}

		My co-authors and I are enclosing a submission entitled ``New Item Response Theory-based Algorithms for the Development of Short Test Forms'' for consideration in the Theory \& Methodology section of Psychometrika. 
		This manuscript presents novel methodologies grounded in Item Response Theory for constructing short test forms while maintaining psychometric integrity. The study contributes to the literature by introducing efficient algorithms that optimize item selection based on theoretical and empirical considerations.

		The manuscript is 22 pages long, including the title page, figures, tables, and references. We affirm that this work has not been published previously and is not under consideration for publication elsewhere. Additionally, all authors declare that there are no conflicts of interest to disclose.

		We believe that our findings will be of interest to researchers and practitioners in psychometrics, educational measurement, and related fields. We appreciate your time and consideration and look forward to your feedback.

		The manuscript has not be submitted elsewhere.

		The authors have no conflict of interest to disclose.

			Please do not hesitate to contact me should you require any further information.
%		\closing{Sincerely,\\ Your Name\\ Your Affiliation\\ Your Email Address\\ Your Corresponding Address}

	\end{letter}

\end{document}

### 2025-02-17 sis2025/LaTex+Package/styles/paper-sis-template.tex
sis update

--- 2025-02-05 sis2025/LaTex+Package/styles/paper-sis-template.tex
@@
 %
-\titlerunning{Hamiltonian Mechanics}  % abbreviated title (for running head)
+\titlerunning{IRT-based algorithms}  % abbreviated title (for running head)
 %                                     also used for the TOC unless
@@
 As a general rule of thumb, the higher the number of items in a test, the better the measurement in terms of validity and reliability.
-However, there is a trade-off between the number of administered items and the response quality (giuro che ho della letteratura in merito).
-Quindi non torturiamo le persone che dopo di un po' non ne possono più.
-Item Response Theory (IRT) provides an ideal framework for shortening existing tests (or for developing tests from item banks) given the detailed information that they provide with respect to the measurement precision of each item considering different levels of the latent trait.
-In this contribution, we present a new algorithm for shortening tests that take into accounts the number of administered items by considering the ``tiredness'' of the respondents for each of the items included in the short test form (STF).
-The performance of the algorithm in retrieving an ideal target information function (i.e., the measurement precision that would be obtained by administering all the items in a test if the respondents would never get tired) is investigated in a simulation study.
-\color{red} il concetto c'è mancano le parole \normalcolor
+However, there is a trade-off between the number of administered items and the response quality.
+As such, the trade-off between the number of administered items and the tiredness of the respondents should be kept in mind to obtain reliable and precise measurement tools.
+Item Response Theory (IRT) provides an ideal framework for shortening existing tests (or for developing tests from item banks) given the detailed information that they provide of the measurement precision of each item with respect to different levels of the latent trait.
+In this contribution, we present a new IRT-based algorithm for developing short test forms (STFs) from existing tests, denoted as Léon.
+This algorithm accounts for the tiredness of the respondents during the item inclusion process, such that it attempts at minimizing the number of selected items while accounting for the tiredness of the respondents in order to maximize the measurement precision (as expressed by the test information function, TIF) of the STF.
+The ability of Léon of developing STFs able to approximate the TIF that would be obtained by administering all the items under the assumption that respondents would never get tired is investigated in a simulation study.
+Specifically, Léon's ability is compared against that of another algorithm for developing STFs, which does not account for the tiredness of the respondents.
 
-\section{Item response theory e mortacci}
+\section{Item Response Theory and Information Functions}
 
-In Item Response Theory (IRT) models for dichotomous responses (e.g., correct vs.
+In IRT models for dichotomous responses (e.g., correct vs.
 incorrect), the probability of observing a correct response on item $i$ by person $p$ depends on both the charcteristics of the respondent (as described by their latent trait level, $\theta_p$) and on the characteristics of the item, which can be described by different parameters.
 IRT models differentiate according to the number of parameters used for describing the characteristics of the items.
-According to the 4-parameter logistic model (4-PL), the probability of a correct can be formalized as:
+According to the 4-parameter logistic model (4-PL), the probability of a correct response can be formalized as:
 
-\begin{equation}
+\begin{equation}{eq:4pl}
 	P(x_{pi}= 1| \theta_p, b_i, a_i, c_i, d_i) = c_i + (d_i -c_i) + \dfrac{\exp[a_i(\theta_p - b_i)]}{1 + \exp[a_i(\theta_p - b_i)]},
@@
 However, there might be instances where respondents with $\theta$ levels below the difficulty of the item, whom are hence expected not to respond correctly, might provide the correct response out of luck.
-The lucky guess parameter $c_i$ describes the probability of endorsing the item even if the $\theta$ level is below the difficulty of the item, such that the probability of observing a correct response for $\theta \to - \infty$ tends to $c_i$ instead of 0.
-The same but inverse consideration applies for the upper asymptote that describes the probability of giving the correct response for $\theta \to + \infty$.
+The lucky guess parameter $c_i$ describes this probability, such that the probability of observing a correct response for $\theta \to - \infty$ tends to $c_i$ instead of 0.
+The same but inverse consideration applies when $\theta \to + \infty$.
 The $d_i$ parameter describes the probability of not endorsing the item given that the latent trait is above the location of the item, such that the probability of observing a correct response for $\theta \to + \infty$ tends to $d_i$ instead of 1.
 
-By constraining $\forall i \in B, \, d_i = 1$ (where $B$ is the set of items in a set), the 3-Parameter logistic (3-PL) model is obtained.
-From 3-PL, the 2-parameter logistic model (2-PL) is obtained by constraining $\forall i \in B, \, c_i = 0$, and the 1-parameter logistic model (1-PL, equivalent to the Rasch model) is obtained by constraining $\forall i \in B, \, a_i = 1$.
+By constraining $\forall i \in B, \, d_i = 1$ (where $B$ is the set of items in a test) in equation \ref{eq:4pl}, the 3-Parameter logistic (3-PL) model is obtained.
+From the 3-PLmodel, the 2-Parameter logistic model (2-PL) is obtained by constraining $\forall i \in B, \, c_i = 0$, and the 1-parameter logistic model (1-PL, equivalent to the Rasch model) is obtained by constraining $\forall i \in B, \, a_i = 1$.
 
@@
 
+The meausemrement precision of each item with respect to different levels of the latent trait can be expressed by the so-called \emph{item information functions} (IIFs), which for the 4-PL is formalized as:
+
+\begin{equation}{eq:iif}
+	IIF_i = \dfrac{a^2[P(\theta)-c_i]^2[d_i - P(\theta)]^2}{(d_i-c_i)^2 P(\theta)Q(\theta)}.
+\end{equation}
+The informativeness of each item is strongly influenced by the location of the item on the latent trait with respect to a specific latent trait level $\theta$, its discriminativity, and the probability of lucky guess and careless error.
+In absence of lucky guess and careless error, the IIF reaches its maximum when the location of the item $b_i$ matches the latent trait level $\theta$, and it decreases as the distance between $b_i$ and $\theta$ increases.
+Moreover, the higher the discrimination of the item $a_i$, the more informative the item.
+However, when the lucky guess and careless error are taken into account, the informativeness of the item decreases, and, most importantly, the maximum of the IIF does not corresponds to the item location on the latent trait and it is generally lower.
+
+The \emph{test information function} (TIF) is the sum of the IIFs, such that its shape (i.e., its informativeness with respect to different levels of the latent trait) and its height (i.e., the amount of information for different levels of the latent trait) depend on the distribution of the items along the latent trait.
+The more the items with high discrimination and low lucky guess and careless error parameters are spread throughout the latent trait, the more the test would be informative of different regions.
+The more the items have lucky guesses and careless errors, the less the TIF.
+
+\section{item Selection Algorithms}
+
+\subsection{Frank}
+
+%\color{red}
+%è qui che va detto che Frank calcola le iif di tutti gli item all'inizio e che poi vengono prese solo quelle degli item che sono disponibili in un dato momento, le IIF che sono in $A^k$
+%\normalcolor
+
+Frank considers the entire latent trait for the item selection, in that it selects the item whose IIF is best able to reduce the distance from the $\text{TIF}^*$ along the entire latent trait, as follows:
+
+At $k = 0$: $\forall i \in B$, $\text{IIF}_i$, $\text{TIF}^0(\theta) = 0 \, \forall \theta$, $Q^0 = \emptyset$. For $k \geq 0$,
+
+\begin{enumerate}
+	\item  $A^k = B \setminus Q^k$ 
+	\item $\forall i \in A^k$, $pTIF_{i}^k = \frac{\text{TIF}^k + \text{IIF}_{i}}{||Q^k||+1}$
+	\item $i^* = \arg \min_{i \in A^k} |\text{TIF}^* - \text{pTIF}_i|$
+	\item Termination criterion: $|\text{TIF}^* - \text{pTIF}_{i^*}| \geq |\text{TIF}^* - \text{TIF}^{k}|$: 
+	\begin{itemize}
+		\item FALSE:  $Q^{k+1} = Q^{k} \cup \{i^*\}$, $TIF^{k+1} = pTIF_{i^*}$, iterates 1-4 
+		\item TRUE: Stop, %The item in $i^*$ does not contribute to reduce the distance from the TIF-target, hence: 
+		$Q_{Frank} = Q^k$
+
+	\end{itemize}
+\end{enumerate}
+
+The first operation done by Frank at the beginning ($k=0$) is to compute the IIFs of all the items in $B$, considering the available item parameters.
+At $k = 0$, the subset of items $Q^0$ is empty and the $\text{TIF}^0$ is 0 for all the $\theta$ levels. 
+At each iteration $k$: (1.) a set of available items is generated as the items in the item bank that have not been included in the STF yet, $A^k = B \setminus Q^k$; (2.)
+An average provisional TIF, $\text{pTIF}$, is computed by adding the IIF of each of the items in the set of the available items $A^k$, one at the time, to the TIF obtained from the items in $Q^k$ (The denominator is obtained by adding 1 to the cardinality of $Q^k$); (3.) Among all the items in $A^k$, the one that allows for minimizing the distance between $\text{pTIF}$ and $\text{TIF}^*$ is included in $i^*$; (4.)
+The termination criterion is tested. 
+If the distance between the $\text{TIF}^*$ and the $\text{pTIF}_{i^*}$ is greater than or equal to the distance between the $\text{TIF}^*$ and the $\text{TIF}^k$ (i.e., the TIF obtained from the items in the subset $Q^k$, without item $i^*$) (TRUE), then the item $i^*$ does not contribute in the reduction of the distance from the $\text{TIF}^*$, the algorithm stops, and the final item selection is the one without the item in $i^*$, $Q_{frank} = Q^k$.
+Conversely (FALSE), the item in $i^*$ does contribute in the reduction of the distance from the $\text{TIF}^*$, hence it is included in the set of items and a new iteration starts, $Q^{k+1} = Q^k \cup \{i^*\}$.
+
 \section{Simulation study}
-Va detto da qualche parte che:
 
-- La stanchezza dei soggetti viene operazionalizzata come probabilità di non careless error (va beh l'asintoto)
+\subsection{Simulation design}
 
-- la tif target è definita come forma ideale dell'informatività che si avrebbe se le persone non si stancassero mai
+In this study, we operationalized the tiredeness of the individuals as the probability of committing careless error ($1- d_i$ QUESTA è LA PROBABILITà DI NON CARELESS ERROR DEVO SPIEGARE MEGLIO), such that the more the items in a test, the higher the probability of careless error.
+The careless error probability is instrinsically related to the rank of the item in the test, and it increases as the position of the item in the test increases.
+It increases exponentially as a function of the number of administered items, such that the first administered item has $d_i = 1$ (i.e., does not have a probability of observing an incorrect response given the latent trait level $\theta$).
 
-- la funzione di stanchezza è quella che mi ha dato chatgpt
+The procedure is replicated 100 times.
+At each replica, a test of $B$ of 50 items with difficulty ($b_i \sim \mathcal{U}(-3, 3)$) discrimination ($a_i \sim \mathcal{U}(.90, 2)$) parameters drawn from uniform distributions is generated.
+Lucky
+guess and careless error parameters are constant, $c_i = 0, \forall i \in B$ and $d_i = 0, \forall i \in B$.
+The $TIF^*$ is generated as the mean TIF of all items in $B$, which describes the ideal TIF that one would obtain if respondents are administered with all the items without getting tired.
 
-- va descritto l'algoritmo e va descritto anche Frank (Frank ha solo un passaggio in meno rispetto a Leon perché non considera la stanchezza, basta descrivere leon e poi dire che Frank fa la stessa roba ma non mette la penalizzazione)
+A new test $B'$ is generated by keeping the item parameters equal to those in $B$, with the only exception of the careless error parameters, which are included as related to the rank of the item in the item bank with an exponential function.
+The assumption is that the first administered item does not have a careless error probability ($d_{1^{st}} = 1$), but it increases as the administration goes on.
+As such, the careless error probabilities associated to the second and third administered items are, respectively, $d_{2^{nd}} = .99$ and $d_{3^{rd}}.98$.
+In this application, the maximum careless error probability associated to the last administered item is $d_{50^{th}} = .61$.
 
+\color{blue}
+Frank and Léon are applied to generate a STF able to recreate the $TIF^*$.
+Both algorithm are applied considering the items in $B'$.
+While both algorithms are able to consider the careless error parameters in the computation of the IIFs, only Léon actually accounts for the number of items included in the STF.
+
+La differenza è che Frank calcola tutte le iif degli tiem all'inizio, consdierando la careless error legata alla posizione dell'item così come viene generata inizialmente dalla funzione. 
+Léon invece calcola la iif ad ogni itereazione (per questo è più lento) mettendo dentro la careless error che è legata alla posizione dell'item.
+Nel senso, se Léon per ora ha selezionato 3 item e deve valutare se metterne un quarto, le iif degli item che sono rimasti verrà calcolata considerando la careless error in $B'$ dell'item somministrato per quarto.
+\normalcolor
+
+\subsection{Comparison}
+
+The ability of Frank and Léon in reducing the distance from the $TIF^*$ (i.e., the TIF obtained from all the items in $B$) has been considered. 
+Moreover, the TIF of the items in $B'$ has been computed as well and compared against those of the STFs resulting from the application of Frank and Léon. 
+The rationale is as follows. The more the item in a test, the higher the information for different regions of the latent trait. 
+However, administering too many items might be an highly demanding task, such that the respondent might get tired and their response accuracy might decrease during the administration, such that the last administered items might include error variance not related to the construct under investigation.
+In this light, it should be more convenient to administer less but highly informative items, able to approximate a specific TIF target, than to administer the entire test to obtain precise measurements of the latent trait.
+
+\section{Results}
+
+%Table \ref{tab:summary} illustrates the mean distance of $TIF_x$, $x \in \{B', Q_{\text{Frank}}, Q_{Leon}\}$ from $TIF^*$, computed across the 100 replications. 
+%
 %\begin{table}
-%\caption{This is the example table taken out of {\it The
-%\TeX{}book,} p.\,246}
-%\begin{center}
-%\begin{tabular}{r@{\quad}rl}
-%\hline
-%\multicolumn{1}{l}{\rule{0pt}{12pt}
-%                   Year}&\multicolumn{2}{l}{World population}\\[2pt]
-%\hline\rule{0pt}{12pt}
-%8000 B.C.  &     5,000,000& \\
-%  50 A.D.  &   200,000,000& \\
-%1650 A.D.  &   500,000,000& \\
-%1945 A.D.  & 2,300,000,000& \\
-%1980 A.D.  & 4,400,000,000& \\[2pt]
-%\hline
-%\end{tabular}
-%\end{center}
+%	\centering
+%	\caption{\label{tab:summary} Average distance from the $\text{TIF}^*$.}
+%	\begin{tabular}{l ccc}
+%		\hline
+%	Procedure	&	M			&	Min	&	Max	\\\hline
+%	All items	& $	0.07\pm	0.03$ &	$< 0.005$	&	0.13	\\
+%	Frank	& $	0.03	\pm	0.03	$ &	$<0.001$	&	0.14	\\
+%	Léon	& $	0.03	\pm	0.02	$ &	$<0.001$	&	0.10	\\
+%	\hline	
+%	\end{tabular}
+%	\flushleft \emph{Note:} All items: TIF obtained considering all the items in $B'$; Frank: STFs obtained without considering the tiredness of the respondents in the item selection; Léon: STFs obtained by considering the tiredness of the respondents in the item selection.
 %\end{table}
-%%
-%\begin{theorem} [Ghoussoub-Preiss]\label{ghou:pre}
-%Assume $H(t,x)$ is
-%$(0,\varepsilon )$-subquadratic at
-%infinity for all $\varepsilon > 0$, and $T$-periodic in $t$
-%\begin{equation}
-%  H (t,\cdot )\ \ \ \ \ {\rm is\ convex}\ \ \forall t
-%\end{equation}
-%\begin{equation}
-%  H (\cdot ,x)\ \ \ \ \ {\rm is}\ \ T{\rm -periodic}\ \ \forall x
-%\end{equation}
-%\begin{equation}
-%  H (t,x)\ge n\left(\left\|x\right\|\right)\ \ \ \ \
-%  {\rm with}\ \ n (s)s^{-1}\to \infty\ \ {\rm as}\ \ s\to \infty
-%\end{equation}
-%\begin{equation}
-%  \forall \varepsilon > 0\ ,\ \ \ \exists c\ :\
-%  H(t,x) \le \frac{\varepsilon}{2}\left\|x\right\|^{2} + c\ .
-%\end{equation}
-%
-%Assume also that $H$ is $C^{2}$, and $H'' (t,x)$ is positive definite
-%everywhere. Then there is a sequence $x_{k}$, $k\in \bbbn$, of
-%$kT$-periodic solutions of the system
-%\begin{equation}
-%  \dot{x} = JH' (t,x)
-%\end{equation}
-%such that, for every $k\in \bbbn$, there is some $p_{o}\in\bbbn$ with:
-%\begin{equation}
-%  p\ge p_{o}\Rightarrow x_{pk} \ne x_{k}\ .
-%\end{equation}
-%\qed
-%\end{theorem}
-%%
-%\begin{example} [{{\rm External forcing}}]
-%Consider the system:
-%\begin{equation}
-%  \dot{x} = JH' (x) + f(t)
-%\end{equation}
-%where the Hamiltonian $H$ is
-%$\left(0,b_{\infty}\right)$-subquadratic, and the
-%forcing term is a distribution on the circle:
-%\begin{equation}
-%  f = \frac{d}{dt} F + f_{o}\ \ \ \ \
-%  {\rm with}\ \ F\in L^{2} \left(\bbbr / T\bbbz; \bbbr^{2n}\right)\ ,
-%\end{equation}
-%where $f_{o} : = T^{-1}\int_{o}^{T} f (t) dt$. For instance,
-%\begin{equation}
-%  f (t) = \sum_{k\in \bbbn} \delta_{k} \xi\ ,
-%\end{equation}
-%where $\delta_{k}$ is the Dirac mass at $t= k$ and
-%$\xi \in \bbbr^{2n}$ is a
-%constant, fits the prescription. This means that the system
-%$\dot{x} = JH' (x)$ is being excited by a
-%series of identical shocks at interval $T$.
-%\end{example}
-%%
-%\begin{definition}
-%Let $A_{\infty} (t)$ and $B_{\infty} (t)$ be symmetric
-%operators in $\bbbr^{2n}$, depending continuously on
-%$t\in [0,T]$, such that
-%$A_{\infty} (t) \le B_{\infty} (t)$ for all $t$.
-%
-%A Borelian function
-%$H: [0,T]\times \bbbr^{2n} \to \bbbr$
-%is called
-%$\left(A_{\infty} ,B_{\infty}\right)$-{\it subquadratic at infinity}
-%if there exists a function $N(t,x)$ such that:
-%\begin{equation}
-%  H (t,x) = \frac{1}{2} \left(A_{\infty} (t) x,x\right) + N(t,x)
-%\end{equation}
-%\begin{equation}
-%  \forall t\ ,\ \ \ N(t,x)\ \ \ \ \
-%  {\rm is\ convex\ with\  respect\  to}\ \ x
-%\end{equation}
-%\begin{equation}
-%  N(t,x) \ge n\left(\left\|x\right\|\right)\ \ \ \ \
-%  {\rm with}\ \ n(s)s^{-1}\to +\infty\ \ {\rm as}\ \ s\to +\infty
-%\end{equation}
-%\begin{equation}
-%  \exists c\in \bbbr\ :\ \ \ H (t,x) \le
-%  \frac{1}{2} \left(B_{\infty} (t) x,x\right) + c\ \ \ \forall x\ .
-%\end{equation}
-%
-%If $A_{\infty} (t) = a_{\infty} I$ and
-%$B_{\infty} (t) = b_{\infty} I$, with
-%$a_{\infty} \le b_{\infty} \in \bbbr$,
-%we shall say that $H$ is
-%$\left(a_{\infty},b_{\infty}\right)$-subquadratic
-%at infinity. As an example, the function
-%$\left\|x\right\|^{\alpha}$, with
-%$1\le \alpha < 2$, is $(0,\varepsilon )$-subquadratic at infinity
-%for every $\varepsilon > 0$. Similarly, the Hamiltonian
-%\begin{equation}
-%H (t,x) = \frac{1}{2} k \left\|k\right\|^{2} +\left\|x\right\|^{\alpha}
-%\end{equation}
-%is $(k,k+\varepsilon )$-subquadratic for every $\varepsilon > 0$.
-%Note that, if $k<0$, it is not convex.
-%\end{definition}
-%%
-%
-%\paragraph{Notes and Comments.}
-%The first results on subharmonics were
-%obtained by Rabinowitz in \cite{fo:kes:nic:tue}, who showed the existence of
-%infinitely many subharmonics both in the subquadratic and superquadratic
-%case, with suitable growth conditions on $H'$. Again the duality
-%approach enabled Clarke and Ekeland in \cite{may:ehr:stein} to treat the
-%same problem in the convex-subquadratic case, with growth conditions on
-%$H$ only.
-%
-%Recently, Michalek and Tarantello (see \cite{fost:kes} and \cite{czaj:fitz})
-%have obtained lower bound on the number of subharmonics of period $kT$,
-%based on symmetry considerations and on pinching estimates, as in
-%Sect.~5.2 of this article.
 
-%
+On average, Léon included more items in the STF than Frank did, $M_{Leon} = 6.75 \pm 3.06$, $M_{Frank} = 5.29 \pm 2.92$, $t = 3.45$, $df = 197.57$, $p < .001$. 
+\color{red}
+scrivere meglio 
+Given that leon account for the tiredness of the respondents during the item selection, it also considers the measurement precision of the STF given that the respondents do get tired during the administration, while Frank does not.
+As such, while preventing the over inclusion of items in the STF, Léon is also able to account for the measurement prevision, in the attempt of balancing the number of items with the measurement precision.
+\normalcolor
+
+Figure \ref{fig:points-alogirthms} illustrates the distance from $TIF_B$ of  $TIF_{B'}$ (green dots), $TIF_{Frank}$ (yellow triangles), and $TIF_{Leon}$ (brown squares) in each of the 100 replications, along with the average distance across the 100 replications (the horizontal line of the corresponding color).
+
+\begin{figure}[!h]
+	\centering
+	\includegraphics[width=\linewidth]{img/points-alogirthms}
+	\caption{Distance from $TIF_{B}$ of $TIF_{B'}$ (green dots), $TIF_{Frank}$ (yellow triangles), and $TIF_{Leon}$ (brown squares) in each of the 100 replications.
+The horizontal green, yellow, and brown lines are the average distance from $TIF_B$ of $TIF_{B'}$, $TIF_{Frank}$, and $TIF_{Leon}$, respectively}
+	\label{fig:points-alogirthms}
+\end{figure}
+
+Overall, $TIF_{B'}$s are the most distant from $TIF_B$, while $TIF_{Leon}$s are the closest ones.
+Interestingly, the latter ones present more variability around the mean ($\bar{\Delta}_{Leon} = 0.03	\pm	0.02$, $CV =0.67$) than the former ones ($\bar{\Delta}_{B'} = 0.07	\pm	0.03$, $CV =0.43$).
+Between $TIF_{B'}$ and $TIF_{Leon}$, $TIF_{Frank}$ is the less consistent in terms of distance from $TIF_{B}$, with ($\bar{\Delta}_{Frank} = 0.03	\pm	0.03$, $CV = 1.00$).
+
+E che cazzo devo dire ancora?
+
+\section{Final Remarks}
+
+This manuscript presented a first attempt at the development of an IRT-based algorithm, denoted as Léon, for the generation of informative and static STFs able to account for the tiredness of the respondents.
+In the item selection for inclusion in the STF, Léon considers the number of items included up to that iteration and adds a penalty in terms of higher probability of careless error, which increases as the number of items included in the STF increases.
+Its performance in approximating a TIF target, which is here conceptualized as the TIF that one would obtain considering the entire administration of the test if respondents would never get tired (i.e., without careless error) , is compared against that of another IRT-based algorithm, denoted as Frank.
+Differently from Léon, Frank does not add any penalization for the number of items included in the STF.
+Finally, the distance between the TIF obtained from the administration of the entire test with and without tiredness has been considered as well.
+
+The results of a simulation study suggest that the administration of fewer items selected also considering the tiredness of the respondents might provide better measurement tools  than administering the entire test and tiring out the respondents.
+
+Although the results are promising, there are several limitations that should be acknowledged.
+Firstly, this study is focused on the approximation of the TIF target.
+However, the final aim with which tests are administered is to estimate the latent trait of the respondents.
+The lack of the precision of estimation of the latent trait of the respondents represents the main limitation and future studies should focus on this issue.
+Secondly, the operalization of the tiredness of the respondents as an increase of the probability of committing careless error as the administration goes on is an arbitrary choice.
+
 % ---- Bibliography ----

### 2025-02-17 sis-2025.R

@@ -209,8 +209,8 @@ myRes = merge(myRes, mean_difference)
 ggplot(myRes, 
        aes(x = reorder(factor(iteration), difference), 
            y = difference, color = type, shape = type)) + 
-  geom_point(size = 2)  + 
-  theme_light() + xlab("Replication") + ylab(expression(paste("|TIF", "* - ",TIF[x], "|"))) + 
+  geom_point(size = 4)  + 
+  theme_classic() + xlab("Replication") + ylab(expression(paste("|TIF", "* - ",TIF[x], "|"))) + 
   scale_x_discrete(labels = c("All items", "Frank", "Léon")) +
   theme(axis.text = element_text(size = 26), 
         axis.text.x = element_blank(),
@@ -220,9 +220,24 @@ ggplot(myRes,
   geom_hline(aes(yintercept  = meandiff, color = type), 
              linewidth=2, linetype = 2)
 
+ggsave("C:/Users/Ottavia/Documents/GitHub/frank-and-friends/sis2025/LaTex+Package/styles/img/points-alogirthms.pdf", 
+       device = "pdf", width = 14, height = 8.5, units = "in")
+
+
 res_tot %>%  
   group_by(type) %>%  
   summarise(mean = round(mean(difference),2), 
             sd = round(sd(difference),2), 
             min = round(min(difference), 8), 
             max = round(max(difference), 2))
+
+# mi prendo la cardnialità di q frank e q leon 
+numberItems = data.frame(iteration = 1:100, 
+                         q_frank = numeric(100), 
+                         q_leon = numeric(100))
+for (i in 1:100) {
+  numberItems[i, "q_frank"] = ncol(resFrank[[i]]$iif_stf)
+  numberItems[i, "q_leon"] = ncol(resLeon[[i]]$iif_stf)
+}
+colMeans(numberItems)
+t.test(numberItems$q_leon, numberItems$q_frank)

### 2025-02-18 sis2025/LaTex+Package/styles/paper-sis-template.tex
update sis

@@
 
-\section{item Selection Algorithms}
+\section{Item Selection Algorithms}
+
+The two algorithms are based on the same principle, that is to reduce as much as possible the distance from a TIF target and the provisional TIF obtained from the items selected up to that point. 
+At each iteration, the item is selected according to its ability of bridging the gap between the two TIFs.
+The algorithms stop when the last item considered for inclusion in the STF does not contribute to bring the provisional TIF closer to the TIF target, that is when the distance between the TIF target and the provisional TIF with the last considered item is equal to or greater than the distance between the TIF target and the provisional TIF without the last considered items (i.e., termination criterion).
+
+In what follows, the TIF-target is represented by the TIF obtained on all the items in a test without careless error parameters, that is the TIF that would be obtained if respondents would never get tired during the administration.
+Given that the original set of items is denoted as $B$, the TIF-target obtained from this set is denoted as $\text{TIF}_B$.
+
+The parameters of the items in $B$ are defined through an $I \times 4$ matrix, where $I$ is the total number of items in $B$ ($||B||$) and the 4 columns contain the item parameters $b_i$, $a_i$, $c_i$, and $d_i$.
+Given that $B$ is the set of item without the effect of the tiredness (i.e., without careless parameters), $d_i = 1$, $\forall i \in \{1, \ldots, I\}$.
+To include the tiredness of the respondents, the vector of careless error parameters $d_i$ is modified with an exponential function, $d_i' = \exp(-\lambda r_i)$ (where $\lambda$ is the speed parameter that determines the steepness of the function and $r$ is the rank of the $i$-th item in the administration).
+The set of items with $d_i'$ is denoted $B'$.
 
@@
 
-Frank considers the entire latent trait for the item selection, in that it selects the item whose IIF is best able to reduce the distance from the $\text{TIF}^*$ along the entire latent trait, as follows:
+Frank considers the entire latent trait for the item selection, in that it selects the item whose IIF is best able to reduce the distance from the $\text{TIF}_B$ along the entire latent trait, as follows:
 
@@
 \begin{enumerate}
-	\item  $A^k = B \setminus Q^k$ 
+	\item  $A^k = B' \setminus Q^k$ 
 	\item $\forall i \in A^k$, $pTIF_{i}^k = \frac{\text{TIF}^k + \text{IIF}_{i}}{||Q^k||+1}$
-	\item $i^* = \arg \min_{i \in A^k} |\text{TIF}^* - \text{pTIF}_i|$
-	\item Termination criterion: $|\text{TIF}^* - \text{pTIF}_{i^*}| \geq |\text{TIF}^* - \text{TIF}^{k}|$: 
+	\item $i^* = \arg \min_{i \in A^k} |\text{TIF}_B - \text{pTIF}_i|$
+	\item Termination criterion: $|\text{TIF}_B - \text{pTIF}_{i^*}| \geq |\text{TIF}_B - \text{TIF}^{k}|$: 
 	\begin{itemize}
@@
 
-The first operation done by Frank at the beginning ($k=0$) is to compute the IIFs of all the items in $B$, considering the available item parameters.
+%The first operation done by Frank at the beginning ($k=0$) is to compute the IIFs of all the items in $B$, considering the available item parameters.
 At $k = 0$, the subset of items $Q^0$ is empty and the $\text{TIF}^0$ is 0 for all the $\theta$ levels. 
 At each iteration $k$: (1.) a set of available items is generated as the items in the item bank that have not been included in the STF yet, $A^k = B \setminus Q^k$; (2.)
-An average provisional TIF, $\text{pTIF}$, is computed by adding the IIF of each of the items in the set of the available items $A^k$, one at the time, to the TIF obtained from the items in $Q^k$ (The denominator is obtained by adding 1 to the cardinality of $Q^k$); (3.) Among all the items in $A^k$, the one that allows for minimizing the distance between $\text{pTIF}$ and $\text{TIF}^*$ is included in $i^*$; (4.)
+An average provisional TIF, $\text{pTIF}$, is computed by adding the IIF of each of the items in the set of the available items $A^k$, one at the time, to the TIF obtained from the items in $Q^k$ (The denominator is obtained by adding 1 to the cardinality of $Q^k$); (3.) Among all the items in $A^k$, the one that allows for minimizing the distance between $\text{pTIF}$ and $\text{TIF}_B$ is included in $i^*$; (4.)
 The termination criterion is tested. 
-If the distance between the $\text{TIF}^*$ and the $\text{pTIF}_{i^*}$ is greater than or equal to the distance between the $\text{TIF}^*$ and the $\text{TIF}^k$ (i.e., the TIF obtained from the items in the subset $Q^k$, without item $i^*$) (TRUE), then the item $i^*$ does not contribute in the reduction of the distance from the $\text{TIF}^*$, the algorithm stops, and the final item selection is the one without the item in $i^*$, $Q_{frank} = Q^k$.
-Conversely (FALSE), the item in $i^*$ does contribute in the reduction of the distance from the $\text{TIF}^*$, hence it is included in the set of items and a new iteration starts, $Q^{k+1} = Q^k \cup \{i^*\}$.
+If the distance between the $\text{TIF}_B$ and the $\text{pTIF}_{i^*}$ is greater than or equal to the distance between the $\text{TIF}_B$ and the $\text{TIF}^k$ (i.e., the TIF obtained from the items in the subset $Q^k$, without item $i^*$) (TRUE), then the item $i^*$ does not contribute in the reduction of the distance from the $\text{TIF}_B$, the algorithm stops, and the final item selection is the one without the item in $i^*$, $Q_{frank} = Q^k$.
+Conversely (FALSE), the item in $i^*$ does contribute in the reduction of the distance from the $\text{TIF}_B$, hence it is included in the set of items and a new iteration starts, $Q^{k+1} = Q^k \cup \{i^*\}$.
 

### 2025-02-18 sis2025/LaTex+Package/styles/paper-sis-template.tex
pietà

@@
 
-\begin{equation}{eq:4pl}
+\begin{equation}[eq:4pl]
 	P(x_{pi}= 1| \theta_p, b_i, a_i, c_i, d_i) = c_i + (d_i -c_i) + \dfrac{\exp[a_i(\theta_p - b_i)]}{1 + \exp[a_i(\theta_p - b_i)]},
@@
 
-\begin{equation}{eq:iif}
+\begin{equation}[eq:iif]
 	IIF_i = \dfrac{a^2[P(\theta)-c_i]^2[d_i - P(\theta)]^2}{(d_i-c_i)^2 P(\theta)Q(\theta)}.
@@
 
-The two algorithms are based on the same principle, that is to reduce as much as possible the distance from a TIF target and the provisional TIF obtained from the items selected up to that point. 
+The two algorithms are based on the same principle of reducing as much as possible the distance between a TIF target and a provisional TIF obtained from the items selected up to that point. 
 At each iteration, the item is selected according to its ability of bridging the gap between the two TIFs.
@@
 %\normalcolor
+\color{red}
+SOno arrivata qui devo ancora rivedere gli algoritmi
+\normalcolor
 
@@
 	\item  $A^k = B' \setminus Q^k$ 
-	\item $\forall i \in A^k$, $pTIF_{i}^k = \frac{\text{TIF}^k + \text{IIF}_{i}}{||Q^k||+1}$
+		\color{red}
+	\item $\forall i \in A^k$, $IIF_i$ computed according to Equation \ref{eq:iif}, and $pTIF_{i}^k = \frac{\text{TIF}^k + \text{IIF}_{i}}{||Q^k||+1}$
+	\normalcolor
 	\item $i^* = \arg \min_{i \in A^k} |\text{TIF}_B - \text{pTIF}_i|$

### 2025-02-18 sis2025/LaTex+Package/styles/paper-sis-template.tex
update sis

--- 2025-02-18 sis2025/LaTex+Package/styles/paper-sis-template.tex
@@
 
-\begin{equation}{eq:4pl}
+\begin{equation}\label{eq:4pl}
 	P(x_{pi}= 1| \theta_p, b_i, a_i, c_i, d_i) = c_i + (d_i -c_i) + \dfrac{\exp[a_i(\theta_p - b_i)]}{1 + \exp[a_i(\theta_p - b_i)]},
@@
 
-\begin{equation}{eq:iif}
+\begin{equation}\label{eq:iif}
 	IIF_i = \dfrac{a^2[P(\theta)-c_i]^2[d_i - P(\theta)]^2}{(d_i-c_i)^2 P(\theta)Q(\theta)}.
@@
 
-The two algorithms are based on the same principle, that is to reduce as much as possible the distance from a TIF target and the provisional TIF obtained from the items selected up to that point. 
-At each iteration, the item is selected according to its ability of bridging the gap between the two TIFs.
-The algorithms stop when the last item considered for inclusion in the STF does not contribute to bring the provisional TIF closer to the TIF target, that is when the distance between the TIF target and the provisional TIF with the last considered item is equal to or greater than the distance between the TIF target and the provisional TIF without the last considered items (i.e., termination criterion).
+In this study, we operationalized the tiredeness of the individuals as the probability of committing careless error, such that the more the items in a test, the higher the probability of careless error on the $i$-th item.
+The careless error probability is instrinsically related to the rank of the item in the test, and it increases exponentially as a function of the number of administered items.
+
+The two algorithms are based on the same principle of reducing as much as possible the distance between a TIF-target and a provisional TIF (pTIF) obtained from the items selected up to that point. 
+At each iteration, the item is included in the STF according to its ability of bridging the gap between the two TIFs. 
+The algorithms stop when the last item considered for inclusion in the STF does not contribute to bring the pTIF closer to the TIF-target, that is when the distance between the TIF-target and the pTIF with the last considered item is equal to or greater than the distance between the TIF-target and the pTIF without the last considered items (i.e., termination criterion).
 
@@
 
-The parameters of the items in $B$ are defined through an $I \times 4$ matrix, where $I$ is the total number of items in $B$ ($||B||$) and the 4 columns contain the item parameters $b_i$, $a_i$, $c_i$, and $d_i$.
+The parameters of the items in $B$ are defined through an $I \times 4$ matrix, where $I$ is the total number of items in $B$ ($||B||$, where $||X||$ denotes the cardinality of set $X$) and the 4 columns contain the item parameters $b_i$, $a_i$, $c_i$, and $d_i$.
 Given that $B$ is the set of item without the effect of the tiredness (i.e., without careless parameters), $d_i = 1$, $\forall i \in \{1, \ldots, I\}$.
@@
 The set of items with $d_i'$ is denoted $B'$.
+
+Since the TIF increases as the number of items in a test increases, the comparison between $TIF_B$ and the TIF of the STF obtained by the item selections provided by the two algorithms is based on the mean TIF (i.e., the TIF divided by the number of items in the STF).
+Nonetheless, in what follows the mean TIF will be simply referred to as $TIF_x$, with $x \in \{B, B', \text{Frank}, \text{Leon}\}$.
 
@@
 
-At $k = 0$: $\forall i \in B$, $\text{IIF}_i$, $\text{TIF}^0(\theta) = 0 \, \forall \theta$, $Q^0 = \emptyset$. For $k \geq 0$,
+\color{red}
+Non è propriamente così, frank calcola tutte le IIF all'inziio considerando i parametri degli item in $B'$ e se le porta avanti ma quindi dovrei creare un altro oggetto che contiene tutte le iif i?
+ci provo tanto ormai è tutto una merda
+\normalcolor
+
+At $k = 0$: $\mathbf{IIF} = $ $\forall i \in B$, $\text{IIF}_i$, $\text{TIF}^0(\theta) = 0 \, \forall \theta$, $Q^0 = \emptyset$. For $k \geq 0$,
 
 \begin{enumerate}
-	\item  $A^k = B' \setminus Q^k$ 
+	\item  $A^k = B \setminus Q^k$ 
+		\color{red}
 	\item $\forall i \in A^k$, $pTIF_{i}^k = \frac{\text{TIF}^k + \text{IIF}_{i}}{||Q^k||+1}$
+	\normalcolor
 	\item $i^* = \arg \min_{i \in A^k} |\text{TIF}_B - \text{pTIF}_i|$
@@
 \subsection{Simulation design}
-
-In this study, we operationalized the tiredeness of the individuals as the probability of committing careless error ($1- d_i$ QUESTA è LA PROBABILITà DI NON CARELESS ERROR DEVO SPIEGARE MEGLIO), such that the more the items in a test, the higher the probability of careless error.
-The careless error probability is instrinsically related to the rank of the item in the test, and it increases as the position of the item in the test increases.
-It increases exponentially as a function of the number of administered items, such that the first administered item has $d_i = 1$ (i.e., does not have a probability of observing an incorrect response given the latent trait level $\theta$).
 
@@
 \color{red}
-scrivere meglio 
 Given that leon account for the tiredness of the respondents during the item selection, it also considers the measurement precision of the STF given that the respondents do get tired during the administration, while Frank does not.
-As such, while preventing the over inclusion of items in the STF, Léon is also able to account for the measurement prevision, in the attempt of balancing the number of items with the measurement precision.
+As such, while preventing the over inclusion of items in the STF, Léon is also able to account for the measurement precision, in the attempt of balancing the number of items with the measurement precision.
 \normalcolor
@@
 	\centering
-	\includegraphics[width=\linewidth]{img/points-alogirthms}
+	\includegraphics[width=\linewidth]{img/box-plot-alogirthms}
 	\caption{Distance from $TIF_{B}$ of $TIF_{B'}$ (green dots), $TIF_{Frank}$ (yellow triangles), and $TIF_{Leon}$ (brown squares) in each of the 100 replications.

### 2025-02-18 sis-2025.R

@@ -97,15 +97,15 @@ tif = list()
 temp_iifs = NULL
 resFrank = list()
 resLeon = list()
+tempFrank = NULL
 # qui dentro devo mettere solo la TIF calcolata sui 50 item con stanchezza
 resAllitems = list()
-time = data.frame(iteration = 1:100, 
-                  start_all = numeric(100), 
-                  end_all = numeric(100), 
-                  start_frank = numeric(100), 
-                  end_frank = numeric(100), 
-                  start_leon = numeric(100), 
-                  end_leon = numeric(100))
+startAll = NULL
+endAll = NULL
+startFrank = NULL
+endFrank = NULL
+startLeon = NULL
+endLeon = NULL
 for (i in 1:100){
   set.seed(1312+i)
   q[[i]] = data.frame(b = runif(n_item, -3, 3), 
@@ -119,17 +119,30 @@ for (i in 1:100){
   q_tired[[i]] = q[[i]]
   q_tired[[i]]$e =  exp(-0.01*(0:(nrow(q_tired[[i]])-1)))
   temp_tired_iifs = item_info(q_tired[[i]], theta = theta)
-  time[i, "start_all"] = Sys.time()
+  # all items
+  startTemp = Sys.time()
   resAllitems[[i]] = data.frame(theta = theta, 
                                 tif_all = rowMeans(temp_tired_iifs))
-  time[i, "end_all"] = Sys.time()
-  # applico frank e leon 
-  time[i, "start_frank"] = Sys.time()
-  resFrank[[i]] = frank(q_tired[[i]], tif[[i]])
-  time[i, "end_frank"] = Sys.time()
-  time[i, "start_leon"] = Sys.time()
+  endTemp = Sys.time()
+  startAll = c(startAll, startTemp)
+  endAll = c(endAll, endTemp)
+  # Frank
+  startTemp = Sys.time()
+  resFrank[[i]] = frank(q[[i]], tif[[i]])
+  endTemp = Sys.time()
+  startFrank = c(startFrank, startTemp)
+  endFrank = c(endFrank, endTemp)
+  # ricalcola la tif mettendo la stanchezza degli item
+  tempIndex = as.numeric(gsub("item_", "", colnames(resFrank[[i]]$iif_stf)))
+  tempItem = q[[i]][tempIndex, ]
+  tempItem$e = exp(-0.01*(0:(nrow(tempItem)-1)))
+  tempIIFs = item_info(tempItem, theta = theta)
+  # Leon
[…]

### 2025-02-19 sis-2025.R
update code R

@@ -133,10 +133,15 @@ for (i in 1:100){
   startFrank = c(startFrank, startTemp)
   endFrank = c(endFrank, endTemp)
   # ricalcola la tif mettendo la stanchezza degli item
-  tempIndex = as.numeric(gsub("item_", "", colnames(resFrank[[i]]$iif_stf)))
+  if (ncol(resFrank[[i]]$iif_stf) > 1) {
+    tempIndex = as.numeric(gsub("item_", "", colnames(resFrank[[i]]$iif_stf)))
+  } else {
+    tempIndex =  as.numeric(gsub("item_", "", resFrank[[i]]$q_frank))
+  }
   tempItem = q[[i]][tempIndex, ]
   tempItem$e = exp(-0.01*(0:(nrow(tempItem)-1)))
   tempIIFs = item_info(tempItem, theta = theta)
+  resFrank[[i]]$iif_stf = tempIIFs
   # Leon
   startTemp = Sys.time()
   resLeon[[i]] = leon(q_tired[[i]], tif[[i]])

### 2025-02-19 sis2025/LaTex+Package/styles/paper-sis-template.tex
ho messo la roba del coso

@@
 However, there might be instances where respondents with $\theta$ levels below the difficulty of the item, whom are hence expected not to respond correctly, might provide the correct response out of luck.
-The lucky guess parameter $c_i$ describes this probability, such that the probability of observing a correct response for $\theta \to - \infty$ tends to $c_i$ instead of 0.
+The pseudoguessing parameter $c_i$ describes this probability, such that the probability of observing a correct response on $i$ for $\theta \to - \infty$ tends to $c_i$ instead of 0.
 The same but inverse consideration applies when $\theta \to + \infty$.
-The $d_i$ parameter describes the probability of not endorsing the item given that the latent trait is above the location of the item, such that the probability of observing a correct response for $\theta \to + \infty$ tends to $d_i$ instead of 1.
+The $d_i$ parameter describes the probability of endorsing the item given that the latent trait is above the location of the item, such that the probability of observing a correct response on $i$ for $\theta \to + \infty$ tends to $d_i$ instead of 1.
 
@@
 
+\color{blue}
+In this study, we operationalized the tiredeness of the individuals as the probability of committing careless error as the administration goes on, hence as a function of the number of items in a test and their relative position.
+This probability is instrinsically related to the rank of the item in the test, and it increases exponentially as a function of the number of administered items.
+As such, the  the careless error parameter in Equation \ref{eq:4pl}, which usually a property of the item per se expressed as $d_i$, in this case becomes a property of the item rank $r = \{1, \ldots, R\}$ in the test, $d_r$.
+\color{red}
+devo andare a prendere le robe per scrivere la relazione d'ordine perché c'è il vincolo che $d_{r-1} < d_r$
+\normalcolor
+
 \subsection{Information Functions}
 
-The meausemrement precision of each item with respect to different levels of the latent trait can be expressed by the so-called \emph{item information functions} (IIFs), which for the 4-PL is formalized as:
+The meausemrement precision of each item with respect to different levels of the latent trait can be expressed by the so-called \emph{item information functions} (IIFs), which for the 4-PL is typically formalized as:
 
@@
 
+\color{blue}
+Again, given that in this application the tiredness of the respondents has been conceptualized as the probability of observing careless errors as the administration goes on, the $d$ parameter in Equation \ref{eq:iif} is a property related to its order of presnetation in the test $r$, and it is hence denoted as $d_r$ with $r = \{1, \ldots, R\}$.
+\normalcolor
+
 \section{Item Selection Algorithms}
-
-In this study, we operationalized the tiredeness of the individuals as the probability of committing careless error, such that the more the items in a test, the higher the probability of careless error on the $i$-th item.
-The careless error probability is instrinsically related to the rank of the item in the test, and it increases exponentially as a function of the number of administered items.
 

### 2025-02-24 sis2025/LaTex+Package/styles/paper-sis-template.tex
update sis

@@
 \def\UrlFont{\rmfamily}
+\newcommand{\ottavia}[1]{\textcolor{red}{#1}}
+\newcommand{\livio}[1]{\textcolor{blue}{#1}}
 
@@
 \and
-Universit\'{e} de Paris-Sud,
-Laboratoire d'Analyse Num\'{e}rique, B\^{a}timent 425,\\
-F-91405 Orsay Cedex, France}
+{\color{red}Department of Statistics, University of Padova, IT} \\}
 
@@
 \begin{abstract}
-The abstract should summarize the contents of the paper
-using at least 70 and at most 150 words. It will be set in 9-point
-font size and be inset 1.0 cm from the right and left margins.
-There will be two blank lines before and after the Abstract. \dots
+\ottavia{da rivedere}
+Although a larger number of test items improves measurement validity, the effect of respondents’ fatigue on the response quality should be acknowledged for developing reliable measurement tools.
+This contribution presents an item response theory-based algorithm (denoted as Léon) able to shorten existing tests by concurrently accounting for the measurement precision of the abbreviated test and the tiredness of the respondents, which is here conceptualized as the probability of observing careless errors as the number of administered items increases.
+A simulation study compares the performance of Léon of approximating the measurement precision that would be obtained from the full-length test without the effect of the tiredness against that of another algorithm that does not account for the tiredness of the respondents.
+Although on average the two algorithms select the same number of items, Léon provides a better approximation to the measurement precision of the full-length test than the other algorithm.
 % We would like to encourage you to list your keywords within
@@
 %
+
+\ottavia{a me questa introduzione piace, mi dispiace toglierla}
 As a general rule of thumb, the higher the number of items in a test, the better the measurement in terms of validity and reliability.
@@
 As such, the trade-off between the number of administered items and the tiredness of the respondents should be kept in mind to obtain reliable and precise measurement tools.
-Item Response Theory (IRT) provides an ideal framework for shortening existing tests (or for developing tests from item banks) given the detailed information that they provide of the measurement precision of each item with respect to different levels of the latent trait.
+Item Response Theory (IRT, baker2017) provides an ideal framework for shortening existing tests (or for developing tests from item banks) given the detailed information that they provide of the measurement precision of each item with respect to different levels of the latent trait.
 In this contribution, we present a new IRT-based algorithm for developing short test forms (STFs) from existing tests, denoted as Léon.
@@
 Specifically, Léon's ability is compared against that of another algorithm for developing STFs, which does not account for the tiredness of the respondents.
+\color{red} The tiredness of the respondents has been here conceptualized as the careless error related to the rank of the items during the administration.
+\normalcolor
 
@@
 This probability is instrinsically related to the rank of the item in the test, and it increases exponentially as a function of the number of administered items.
-As such, the  the careless error parameter in Equation \ref{eq:4pl}, which usually a property of the item per se expressed as $d_i$, in this case becomes a property of the item rank $r = \{1, \ldots, R\}$ in the test, $d_r$.
-\color{red}
-devo andare a prendere le robe per scrivere la relazione d'ordine perché c'è il vincolo che $d_{r-1} < d_r$
+As such, the  the careless error parameter in Equation \ref{eq:4pl}, which usually a property of the item per se expressed as $d_i$, in this case becomes a property of the item rank $r = \{1, \ldots, R\}$ in the test, $d_r$, with the constraint that $d_{r-1} < d_r$.
 \normalcolor
@@
 \color{blue}
-Again, given that in this application the tiredness of the respondents has been conceptualized as the probability of observing careless errors as the administration goes on, the $d$ parameter in Equation \ref{eq:iif} is a property related to its order of presnetation in the test $r$, and it is hence denoted as $d_r$ with $r = \{1, \ldots, R\}$.
+Again, given that in this application the tiredness of the respondents has been conceptualized as the probability of observing careless errors as the administration goes on, the $d$ parameter in Equation \ref{eq:iif} is a property related to its order of presentation in the test $r$, and it is hence denoted as $d_r$ with $r = \{1, \ldots, R\}$.
 \normalcolor
@@
 
-Since the TIF increases as the number of items in a test increases, the comparison between $TIF_B$ and the TIF of the STF obtained by the item selections provided by the two algorithms is based on the mean TIF (i.e., the TIF divided by the number of items in the STF).
-Nonetheless, in what follows the mean TIF will be simply referred to as $TIF_x$, with $x \in \{B, B', \text{Frank}, \text{Leon}\}$.
+Since the TIF increases as the number of items in a test increases, the comparison between $\text{TIF}_B$ and the TIF of the STF obtained by the item selections provided by the two algorithms is based on the mean TIF (i.e., the TIF divided by the number of items in the STF).
+Nonetheless, in what follows the mean TIF will be simply referred to as $\text{TIF}_x$, with $x \in \{B, B', \text{Frank}, \text{\text{Léon}}\}$.
 
@@
 		\color{red}
-	\item $\forall i \in A^k$, $pTIF_{i}^k = \frac{\text{TIF}^k + \text{IIF}_{i}}{||Q^k||+1}$
+	\item $\forall i \in A^k$, $p\text{TIF}_{i}^k = \frac{\text{TIF}^k + \text{IIF}_{i}}{||Q^k||+1}$
 	\normalcolor
@@
 	\begin{itemize}
-		\item FALSE:  $Q^{k+1} = Q^{k} \cup \{i^*\}$, $TIF^{k+1} = pTIF_{i^*}$, iterates 1-4 
+		\item FALSE:  $Q^{k+1} = Q^{k} \cup \{i^*\}$, $TIF^{k+1} = p\text{TIF}_{i^*}$, iterates 1-4 
 		\item TRUE: Stop, %The item in $i^*$ does not contribute to reduce the distance from the TIF-target, hence: 
@@
 Lucky
-guess and careless error parameters are constant, $c_i = 0, \forall i \in B$ and $d_i = 0, \forall i \in B$.
-The $TIF^*$ is generated as the mean TIF of all items in $B$, which describes the ideal TIF that one would obtain if respondents are administered with all the items without getting tired.
+guess and careless error parameters are constant, $c_i = 0, \forall i \in B$ and $d_i = \, \forall i \in B$.
+The $\text{TIF}_B$ is obtained as the average TIF  from the items in $B$, and describes the measurement precision that would be obtained if respondents were administered with all the items without getting tired.
 
@@
 \color{blue}
-Frank and Léon are applied to generate a STF able to recreate the $TIF^*$.
-Both algorithm are applied considering the items in $B'$.
-While both algorithms are able to consider the careless error parameters in the computation of the IIFs, only Léon actually accounts for the number of items included in the STF.
-
-La differenza è che Frank calcola tutte le iif degli tiem all'inizio, consdierando la careless error legata alla posizione dell'item così come viene generata inizialmente dalla funzione. 
-Léon invece calcola la iif ad ogni itereazione (per questo è più lento) mettendo dentro la careless error che è legata alla posizione dell'item.
+At each replication, Frank and Léon generate a STF for approximating $\text{TIF}_B$.
+%La differenza è che Frank calcola tutte le iif degli tiem all'inizio, consdierando la careless error legata alla posizione dell'item così come viene generata inizialmente dalla funzione. 
+%Léon invece calcola la iif ad ogni itereazione (per questo è più lento) mettendo dentro la careless error che è legata alla posizione dell'item.
 Nel senso, se Léon per ora ha selezionato 3 item e deve valutare se metterne un quarto, le iif degli item che sono rimasti verrà calcolata considerando la careless error in $B'$ dell'item somministrato per quarto.
@@
 
-The ability of Frank and Léon in reducing the distance from the $TIF^*$ (i.e., the TIF obtained from all the items in $B$) has been considered. 
+The performance of Léon has been compared 
+The ability of Frank and Léon in reducing the distance from the $\text{TIF}_B$ has been considered. 
 Moreover, the TIF of the items in $B'$ has been computed as well and compared against those of the STFs resulting from the application of Frank and Léon. 
@@
 
-%Table \ref{tab:summary} illustrates the mean distance of $TIF_x$, $x \in \{B', Q_{\text{Frank}}, Q_{Leon}\}$ from $TIF^*$, computed across the 100 replications. 
+%Table \ref{tab:summary} illustrates the mean distance of $\text{TIF}_x$, $x \in \{B', Q_{\text{Frank}}, Q_{\text{Léon}}\}$ from $TIF^*$, computed across the 100 replications. 
 %
@@
 
-On average, Léon included more items in the STF than Frank did, $M_{Leon} = 6.75 \pm 3.06$, $M_{Frank} = 5.29 \pm 2.92$, $t = 3.45$, $df = 197.57$, $p < .001$. 
-\color{red}
-Given that leon account for the tiredness of the respondents during the item selection, it also considers the measurement precision of the STF given that the respondents do get tired during the administration, while Frank does not.
+On average, Léon and Frank included the same of items included more items in the STF than Frank did, $M_{\text{Léon}} = 6.75 \pm 3.06$, $M_{\text{Frank}} = 6.31 \pm 2.40$, $t = 1.13$, $df = 187.59$, $p = .26$, suggesting that accounting for the tiredness of the respondents does not influence the number of items included in the STF.
+%\color{red}
+%Given that leon account for the tiredness of the respondents during the item selection, it also considers the measurement precision of the STF given that the respondents do get tired during the administration, while Frank does not.
 As such, while preventing the over inclusion of items in the STF, Léon is also able to account for the measurement precision, in the attempt of balancing the number of items with the measurement precision.
-\normalcolor
+%\normalcolor
 
-Figure \ref{fig:points-alogirthms} illustrates the distance from $TIF_B$ of  $TIF_{B'}$ (green dots), $TIF_{Frank}$ (yellow triangles), and $TIF_{Leon}$ (brown squares) in each of the 100 replications, along with the average distance across the 100 replications (the horizontal line of the corresponding color).
-
+Figure \ref{fig:points-alogirthms} illustrates the distributions of the distances from $\text{TIF}_B$ of  $\text{TIF}_{B'}$ (green dots), $\text{TIF}_{Frank}$ (yellow triangles), and $\text{TIF}_{\text{Léon}}$ (brown squares).
 \begin{figure}[!h]
@@
 	\includegraphics[width=\linewidth]{img/box-plot-alogirthms}
-	\caption{Distance from $TIF_{B}$ of $TIF_{B'}$ (green dots), $TIF_{Frank}$ (yellow triangles), and $TIF_{Leon}$ (brown squares) in each of the 100 replications.
-The horizontal green, yellow, and brown lines are the average distance from $TIF_B$ of $TIF_{B'}$, $TIF_{Frank}$, and $TIF_{Leon}$, respectively}
+	\caption{Distance from $\text{TIF}_{B}$ of $\text{TIF}_{B'}$ (green dots), $\text{TIF}_{Frank}$ (yellow triangles), and $\text{TIF}_{\text{Léon}}$ (brown squares) in each of the 100 replications.
+The horizontal green, yellow, and brown lines are the average distance from $\text{TIF}_B$ of $\text{TIF}_{B'}$, $\text{TIF}_{Frank}$, and $\text{TIF}_{\text{Léon}}$, respectively}
 	\label{fig:points-alogirthms}
@@
 
-Overall, $TIF_{B'}$s are the most distant from $TIF_B$, while $TIF_{Leon}$s are the closest ones.
-Interestingly, the latter ones present more variability around the mean ($\bar{\Delta}_{Leon} = 0.03	\pm	0.02$, $CV =0.67$) than the former ones ($\bar{\Delta}_{B'} = 0.07	\pm	0.03$, $CV =0.43$).
-Between $TIF_{B'}$ and $TIF_{Leon}$, $TIF_{Frank}$ is the less consistent in terms of distance from $TIF_{B}$, with ($\bar{\Delta}_{Frank} = 0.03	\pm	0.03$, $CV = 1.00$).
-
-E che cazzo devo dire ancora?
+Overall, $\text{TIF}_{B'}$s are the most distant from $\text{TIF}_B$, while $\text{TIF}_{\text{Léon}}$s are the closest ones.
+Frank falls in between the two, also presenting the least consistent performance across the replications.
 

### 2025-02-24 sis2025/LaTex+Package/styles/paper-sis-template.tex
voglio morire

@@
 
-\color{red}
-Non è propriamente così, frank calcola tutte le IIF all'inziio considerando i parametri degli item in $B'$ e se le porta avanti ma quindi dovrei creare un altro oggetto che contiene tutte le iif i?
-ci provo tanto ormai è tutto una merda
-\normalcolor
-
 At $k = 0$: $\mathbf{IIF} = $ $\forall i \in B$, $\text{IIF}_i$, $\text{TIF}^0(\theta) = 0 \, \forall \theta$, $Q^0 = \emptyset$. For $k \geq 0$,
@@
 guess and careless error parameters are constant, $c_i = 0, \forall i \in B$ and $d_i = \, \forall i \in B$.
-The $\text{TIF}_B$ is obtained as the average TIF  from the items in $B$, and describes the measurement precision that would be obtained if respondents were administered with all the items without getting tired.
-
-A new test $B'$ is generated by keeping the item parameters equal to those in $B$, with the only exception of the careless error parameters, which are included as related to the rank of the item in the item bank with an exponential function.
-The assumption is that the first administered item does not have a careless error probability ($d_{1^{st}} = 1$), but it increases as the administration goes on.
-As such, the careless error probabilities associated to the second and third administered items are, respectively, $d_{2^{nd}} = .99$ and $d_{3^{rd}}.98$.
-In this application, the maximum careless error probability associated to the last administered item is $d_{50^{th}} = .61$.
+The $\text{TIF}_B$ (i.e., the TIF-target) is obtained as the average TIF  from the items in $B$, and describes the measurement precision that would be obtained if respondents were administered with all the items without getting tired.
 
 \color{blue}
-At each replication, Frank and Léon generate a STF for approximating $\text{TIF}_B$.
+A new test, $B'$, is generated at each replication, where $b_i' = b_i$, $a_i' = a_i$, $c_i = 0$, $\forall i \in B'$, and $d_i' = \exp(-\lambda r_i)$, with $\lambda = 0.01$ and $r = \{0, \ldots I -1\}$.
+
+At each replication, Frank and Léon generate a STF for approximating the $\text{TIF}_B$.
+Moreover, the average TIF is computed considering the item with the tiredness effect in $B'$, denoted as $\text{TIF}_{B'}$.
 %La differenza è che Frank calcola tutte le iif degli tiem all'inizio, consdierando la careless error legata alla posizione dell'item così come viene generata inizialmente dalla funzione. 
@@
 
-The performance of Léon has been compared 
-The ability of Frank and Léon in reducing the distance from the $\text{TIF}_B$ has been considered. 
-Moreover, the TIF of the items in $B'$ has been computed as well and compared against those of the STFs resulting from the application of Frank and Léon. 
-The rationale is as follows. The more the item in a test, the higher the information for different regions of the latent trait. 
-However, administering too many items might be an highly demanding task, such that the respondent might get tired and their response accuracy might decrease during the administration, such that the last administered items might include error variance not related to the construct under investigation.
-In this light, it should be more convenient to administer less but highly informative items, able to approximate a specific TIF target, than to administer the entire test to obtain precise measurements of the latent trait.
+The average distance from $\text{TIF}_B$ of the STFs generated by Frank and Léon at each iteration, as well as of the test obtained from $B'$ has been considered as a criterion for evaluating the ability of Léon of generating informative STFs while accounting for the tiredness of the respondents, $\Delta_x = |\text{TIF}_B - \text{TIF}_{Q_x}|$, with $x \in \{B', \text{Frank}, \text{Léon}\}$.
+Trivially, when the $\text{TIF}_\{B'\}$ is considered, $Q = B'$.
+
+To better understand whether acknowledging the tiredness of the respondents influences the number of items included in $Q$, the cardinalities of the STFs generated by Frank and Léon, $||Q_{\text{Frank}}||$ and $||Q_{\text{Léon}}||$, respectively, have been compared.
+
+%Moreover, the TIF of the items in $B'$ has been computed as well and compared against those of the STFs resulting from the application of Frank and Léon. 
+%The rationale is as follows. The more the item in a test, the higher the information for different regions of the latent trait. 
+%However, administering too many items might be an highly demanding task, such that the respondent might get tired and their response accuracy might decrease during the administration, such that the last administered items might include error variance not related to the construct under investigation.
+%In this light, it should be more convenient to administer less but highly informative items, able to approximate a specific TIF target, than to administer the entire test to obtain precise measurements of the latent trait.
 

### 2025-02-24 sis2025/LaTex+Package/styles/paper-sis-template.tex
ho aggiunto la bibliografia

@@
 %
-
-\ottavia{a me questa introduzione piace, mi dispiace toglierla}
 As a general rule of thumb, the higher the number of items in a test, the better the measurement in terms of validity and reliability.
@@
 As such, the trade-off between the number of administered items and the tiredness of the respondents should be kept in mind to obtain reliable and precise measurement tools.
-Item Response Theory (IRT, baker2017) provides an ideal framework for shortening existing tests (or for developing tests from item banks) given the detailed information that they provide of the measurement precision of each item with respect to different levels of the latent trait.
+Item Response Theory (IRT, see, e.g., \cite{baker}) provides an ideal framework for shortening existing tests (or for developing tests from item banks) given the detailed information that they provide of the measurement precision of each item with respect to different levels of the latent trait.
 In this contribution, we present a new IRT-based algorithm for developing short test forms (STFs) from existing tests, denoted as Léon.
 This algorithm accounts for the tiredness of the respondents during the item inclusion process, such that it attempts at minimizing the number of selected items while accounting for the tiredness  of the respondents in order to maximize the measurement precision (as expressed by the test information function, TIF) of the STF.
-The ability of Léon of developing STFs able to approximate the TIF that would be obtained by administering all the items under the assumption that respondents would never get tired is investigated in a simulation study.
-Specifically, Léon's ability is compared against that of another algorithm for developing STFs, which does not account for the tiredness of the respondents.
-\color{red} The tiredness of the respondents has been here conceptualized as the careless error related to the rank of the items during the administration.
-\normalcolor
+%The ability of Léon of developing STFs able to approximate the TIF that would be obtained by administering all the items under the assumption that respondents would never get tired is investigated in a simulation study.
+%Specifically, Léon's ability is compared against that of another algorithm for developing STFs, which does not account for the tiredness of the respondents. 
+\color{red} The tiredness of the respondents has been here conceptualized as the careless error related to the rank of the items during the administration. \normalcolor
 
@@
 IRT models differentiate according to the number of parameters used for describing the characteristics of the items.
-According to the 4-parameter logistic model (4-PL), the probability of a correct response can be formalized as:
+According to the 4-parameter logistic model (4-PL, \cite{barton:4pl}), the probability of a correct response can be formalized as:
 
@@
 \end{equation}
-where $\theta_p$ is the latent trait level of person $p$, $b_i$ is the location of the item on the latent trait (i.e., difficulty parameter, the higher the value, the higher the difficulty of the item), $a_i$ describes the ability of $i$ to discriminate between respondents with different latent trait levels (i.e.,discrimination parameter, the higher the value, the higher the discrimination ability of the item), and $c_i$ and $d_i$ describe the probability of observing a correct response when $\theta \to - \infty$ and $\theta \to +\infty$, respectively.
+where $\theta_p$ is the latent trait level of person $p$, $b_i$ is the location of the item on the latent trait (i.e., difficulty parameter, the higher the value, the higher the difficulty of the item), $a_i$ describes the ability of $i$ to discriminate between respondents with different latent trait levels (i.e., discrimination parameter, the higher the value, the higher the discrimination ability of the item), and $c_i$ and $d_i$ describe the probability of observing a correct response when $\theta \to - \infty$ and $\theta \to +\infty$, respectively.
 When $\theta \to - \infty$, the probability of observing a correct response should tend to 0.
@@
 The $d_i$ parameter describes the probability of endorsing the item given that the latent trait is above the location of the item, such that the probability of observing a correct response on $i$ for $\theta \to + \infty$ tends to $d_i$ instead of 1.
+\ottavia{In other words, $d_i$ represents the upper asymptote for each item.
+The careless error probability is $1 - d_i$.}
 
-By constraining $\forall i \in B, \, d_i = 1$ (where $B$ is the set of items in a test) in equation \ref{eq:4pl}, the 3-Parameter logistic (3-PL) model is obtained.
-From the 3-PLmodel, the 2-Parameter logistic model (2-PL) is obtained by constraining $\forall i \in B, \, c_i = 0$, and the 1-parameter logistic model (1-PL, equivalent to the Rasch model) is obtained by constraining $\forall i \in B, \, a_i = 1$.
+By constraining $\forall i \in B, \, d_i = 1$ (where $B$ is the set of items in a test) in equation \ref{eq:4pl}, the 3-Parameter logistic (3-PL, \cite{lord:3pl}) model is obtained.
+From the 3-PL model, the 2-Parameter logistic model (2-PL, \cite{birnbaum}) is obtained by constraining $\forall i \in B, \, c_i = 0$, and the 1-parameter logistic model (1-PL, equivalent to the Rasch model) is obtained by constraining $\forall i \in B, \, a_i = 1$.
 
 \color{blue}
-In this study, we operationalized the tiredeness of the individuals as the probability of committing careless error as the administration goes on, hence as a function of the number of items in a test and their relative position.
-This probability is instrinsically related to the rank of the item in the test, and it increases exponentially as a function of the number of administered items.
-As such, the  the careless error parameter in Equation \ref{eq:4pl}, which usually a property of the item per se expressed as $d_i$, in this case becomes a property of the item rank $r = \{1, \ldots, R\}$ in the test, $d_r$, with the constraint that $d_{r-1} < d_r$.
+In this study, we operationalized the tiredness of the individuals as the careless error probability $1 - d_i$, which increases as the administration goes on.
+As $1 - d_i$ increases, the upper aymptote $d_i$ decreases.
+This probability is instrinsically related to the rank of the item in the test.
+As such, the careless error parameter in Equation (\ref{eq:4pl}), which usually a property of the item per se expressed as $d_i$, in this case becomes a property of the item rank $r = \{1, \ldots, R\}$ in the test, $d_r$, with the constraint $d_{r-1} < d_r$.
 \normalcolor
@@
 
-The meausemrement precision of each item with respect to different levels of the latent trait can be expressed by the so-called \emph{item information functions} (IIFs), which for the 4-PL is typically formalized as:
+The measurement precision of each item with respect to different levels of the latent trait can be expressed by the so-called \emph{item information functions} (IIFs), which for the 4-PL is typically formalized as \cite{magis:iif}:
 
 \begin{equation}\label{eq:iif}
-	IIF_i = \dfrac{a^2[P(\theta)-c_i]^2[d_i - P(\theta)]^2}{(d_i-c_i)^2 P(\theta)Q(\theta)}.
+	\text{IIF}_i = \dfrac{a^2[P(\theta)-c_i]^2[d_i - P(\theta)]^2}{(d_i-c_i)^2 P(\theta)Q(\theta)}.
 \end{equation}
@@
 Moreover, the higher the discrimination of the item $a_i$, the more informative the item.
-However, when the lucky guess and careless error are taken into account, the informativeness of the item decreases, and, most importantly, the maximum of the IIF does not corresponds to the item location on the latent trait and it is generally lower.
+When the lucky guess and careless error are taken into account, the informativeness of the item decreases, and, most importantly, the maximum of the IIF does not corresponds to the item location on the latent trait and it is generally lower.
 
@@
 The more the items with high discrimination and low lucky guess and careless error parameters are spread throughout the latent trait, the more the test would be informative of different regions.
-The more the items have lucky guesses and careless errors, the less the TIF.
+The more the items have lucky guesses and careless errors, the lower the TIF.
 
@@
 
-The two algorithms are based on the same principle of reducing as much as possible the distance between a TIF-target and a provisional TIF (pTIF) obtained from the items selected up to that point. 
+The two algorithms are based on the same principle of reducing as much as possible the distance between a target TIF (TIF-target, describes the desired characteristics of the STFs in terms of measurement precision) and a provisional TIF (pTIF) obtained from the items selected up to that point.
 At each iteration, the item is included in the STF according to its ability of bridging the gap between the two TIFs. 
-The algorithms stop when the last item considered for inclusion in the STF does not contribute to bring the pTIF closer to the TIF-target, that is when the distance between the TIF-target and the pTIF with the last considered item is equal to or greater than the distance between the TIF-target and the pTIF without the last considered items (i.e., termination criterion).
+The algorithms stop when the last item considered for inclusion does not contribute to bring the pTIF closer to the TIF-target, that is when the distance between the TIF-target and the pTIF with the last considered item is equal to or greater than the distance between the TIF-target and the pTIF without the last considered items (i.e., termination criterion).
 
@@
 The parameters of the items in $B$ are defined through an $I \times 4$ matrix, where $I$ is the total number of items in $B$ ($||B||$, where $||X||$ denotes the cardinality of set $X$) and the 4 columns contain the item parameters $b_i$, $a_i$, $c_i$, and $d_i$.
-Given that $B$ is the set of item without the effect of the tiredness (i.e., without careless parameters), $d_i = 1$, $\forall i \in \{1, \ldots, I\}$.
+Given that $B$ is the set of item without the effect of the tiredness, $d_i = 1$, $\forall i \in \{1, \ldots, I\}$.
 To include the tiredness of the respondents, the vector of careless error parameters $d_i$ is modified with an exponential function, $d_i' = \exp(-\lambda r_i)$ (where $\lambda$ is the speed parameter that determines the steepness of the function and $r$ is the rank of the $i$-th item in the administration).
@@
 Since the TIF increases as the number of items in a test increases, the comparison between $\text{TIF}_B$ and the TIF of the STF obtained by the item selections provided by the two algorithms is based on the mean TIF (i.e., the TIF divided by the number of items in the STF).
-Nonetheless, in what follows the mean TIF will be simply referred to as $\text{TIF}_x$, with $x \in \{B, B', \text{Frank}, \text{\text{Léon}}\}$.
+Nonetheless, in what follows the mean TIF will be simply referred to as $\text{TIF}_{Q_x}$, with $x \in \{B, B', \text{Frank}, \text{\text{Léon}}\}$.
 
@@
 
-At $k = 0$: $\mathbf{IIF} = $ $\forall i \in B$, $\text{IIF}_i$, $\text{TIF}^0(\theta) = 0 \, \forall \theta$, $Q^0 = \emptyset$. For $k \geq 0$,
+At $k = 0$: $\text{IIF}_i$, $\text{TIF}^0(\theta) = 0 \, \forall \theta$, $Q^0 = \emptyset$. For $k \geq 0$,
 
@@
 	\item  $A^k = B \setminus Q^k$ 
-		\color{red}
 	\item $\forall i \in A^k$, $p\text{TIF}_{i}^k = \frac{\text{TIF}^k + \text{IIF}_{i}}{||Q^k||+1}$
-	\normalcolor
-	\item $i^* = \arg \min_{i \in A^k} |\text{TIF}_B - \text{pTIF}_i|$
+	\item $i^* = \arg \min_{i \in A^k} |\text{TIF}_B - \text{pTIF}_i|$, with $c_i = 0$ and $d_i$, $\forall i \in B$
 	\item Termination criterion: $|\text{TIF}_B - \text{pTIF}_{i^*}| \geq |\text{TIF}_B - \text{TIF}^{k}|$: 
@@
 
+\color{blue}
+\subsection{Léon}
+Léon has the same structure as Frank. However, at step (2.) the $IIF_i$ are computed also considering the $d_r$ related to the number of items included in the STF up to that point.  
+\normalcolor
+
 \section{Simulation study}
@@
 Moreover, the average TIF is computed considering the item with the tiredness effect in $B'$, denoted as $\text{TIF}_{B'}$.
+Although Frank grounds the item selection on $B$ (i.e., without considering the tiredness), the final TIF is computed by considering the vector $d_r$ associated to the rank of the items in $Q_{\text{Frank}}$.
 %La differenza è che Frank calcola tutte le iif degli tiem all'inizio, consdierando la careless error legata alla posizione dell'item così come viene generata inizialmente dalla funzione. 
@@
 
-On average, Léon and Frank included the same of items included more items in the STF than Frank did, $M_{\text{Léon}} = 6.75 \pm 3.06$, $M_{\text{Frank}} = 6.31 \pm 2.40$, $t = 1.13$, $df = 187.59$, $p = .26$, suggesting that accounting for the tiredness of the respondents does not influence the number of items included in the STF.
+On average, Léon and Frank included the same number of items in the STF, $M_{\text{Léon}} = 6.75 \pm 3.06$, $M_{\text{Frank}} = 6.31 \pm 2.40$, $t = 1.13$, $df = 187.59$, $p = .26$, suggesting that accounting for the tiredness of the respondents does not influence the number of items included in the STF.
 %\color{red}
@@
 Frank falls in between the two, also presenting the least consistent performance across the replications.
+\ottavia{dovrei aggiunger some sort of test}
 
@@
 
-\bibitem {smit:wat}
-Smith, T.F., Waterman, M.S.: Identification of common molecular subsequences.
-J. Mol. Biol. 147, 195?197 (1981). \url{doi:10.1016/0022-2836(81)90087-5}
+\bibitem {baker}
+ Baker, F. B., Kim, S.-H. (2017). The basics of Item Response Theory using R. Springer.
 
-\bibitem {may:ehr:stein}
-May, P., Ehrlich, H.-C., Steinke, T.: ZIB structure prediction pipeline:
-composing a complex biological workflow through web services.
-In: Nagel, W.E., Walter, W.V., Lehner, W. (eds.) Euro-Par 2006.
-LNCS, vol. 4128, pp. 1148?1158. Springer, Heidelberg (2006).
-\url{doi:10.1007/11823285_121}
+\bibitem {barton:4pl}
+Barton, M. A., Lord, F. M. (1981). An upper asymptote for the three-parameter logistic item-response
+model. Princeton, NJ: Educational Testing Service.
 
-\bibitem {fost:kes}
-Foster, I., Kesselman, C.: The Grid: Blueprint for a New Computing Infrastructure.
-Morgan Kaufmann, San Francisco (1999)
+\bibitem {birnbaum}
+Birnbaum, A. (1968). Some latent trait models and their use in inferring an examinee’s ability. In F. M.
+Lord, M. R. Novick (Eds.), Statistical theories of mental test scores (pp. 397-479). Reading, MA:
+Addison-Wesley
 
-\bibitem {czaj:fitz}
-Czajkowski, K., Fitzgerald, S., Foster, I., Kesselman, C.: Grid information services
-for distributed resource sharing. In: 10th IEEE International Symposium
-on High Performance Distributed Computing, pp. 181?184. IEEE Press, New York (2001).
-\url{doi: 10.1109/HPDC.2001.945188}
+\bibitem {lord:3pl}
+Lord, F. M. (1980). Applications of item response theory to practical testing problems. Hillsdale, NJ:
+Lawrence Erlbaum
 
-\bibitem {fo:kes:nic:tue}
-Foster, I., Kesselman, C., Nick, J., Tuecke, S.: The physiology of the grid: an open grid services architecture for distributed systems integration. Technical report, Global Grid
-Forum (2002)
+\bibitem {magis:iif}
+Magis, D. (2013). A note on the item information function of the four-parameter logistic model. Applied Psychological Measurement, 37(4), 304-315.
 
-\bibitem {onlyurl}
-National Center for Biotechnology Information. \url{http://www.ncbi.nlm.nih.gov}
+\bibitem {rsoft}
+R Development Core Team. (2012). R: A language and environment for statistical computing [Computer
+software]. Vienna, Austria: R Foundation for Statistical Computing.
 

### 2025-02-24 sis2025/LaTex+Package/styles/paper-sis-template.tex
i give up.

@@
 \subsection{Léon}
-Léon has the same structure as Frank. However, at step (2.) the $IIF_i$ are computed also considering the $d_r$ related to the number of items included in the STF up to that point.  
+Differently from Frank, at step (2.) Léon computes the $\text{IIF}_i$ by considering the $d_r$ related to the number of items included in the STF up to that point.  
 \normalcolor
@@
 
-Figure \ref{fig:points-alogirthms} illustrates the distributions of the distances from $\text{TIF}_B$ of  $\text{TIF}_{B'}$ (green dots), $\text{TIF}_{Frank}$ (yellow triangles), and $\text{TIF}_{\text{Léon}}$ (brown squares).
+Figure \ref{fig:points-alogirthms} illustrates the distributions of the distances from $\text{TIF}_B$ ($y$-axis) of $Q_x$ ($x$-axis).
+
 \begin{figure}[!h]

### 2025-02-24 sis-2025.R

@@ -242,13 +242,25 @@ ggsave("C:/Users/Ottavia/Documents/GitHub/frank-and-friends/sis2025/LaTex+Packag
        device = "pdf", width = 14, height = 8.5, units = "in")
 
 
-res_tot %>%  
+myres = res_tot %>%  
   group_by(type) %>%  
   summarise(mean = round(mean(difference),2), 
             sd = round(sd(difference),2), 
             min = round(min(difference), 8), 
-            max = round(max(difference), 2))
+            max = round(max(difference), 2)) %>% 
+  mutate(cv = sd/mean)
 
+library(lme4)
+
+model = lmer(difference ~ type + (1|iteration) + (1|theta), data = res_tot)
+summary(model)
+
+
+m = aov(difference ~ type, data = res_tot)
+summary(m)
+coefficients(m)
+library(effects)
+plot(allEffects(m))
 # mi prendo la cardnialità di q frank e q leon 
 numberItems = data.frame(iteration = 1:100, 
                          q_frank = numeric(100), 
@@ -259,3 +271,4 @@ for (i in 1:100) {
 }
 colMeans(numberItems)
 t.test(numberItems$q_leon, numberItems$q_frank)
+apply(numberItems, 2, sd)

### 2025-02-25 sis2025/LaTex+Package/styles/paper-sis-template.tex
last upodate

@@
 %
-\title{How much is too much? Item Response Theory procedures to shorten tests}
+\title{Nothing lasts forever -- only item administration: Item Response Theory procedures to shorten tests}
 %
@@
 IRT models differentiate according to the number of parameters used for describing the characteristics of the items.
-According to the 4-parameter logistic model (4-PL, \cite{barton:4pl}), the probability of a correct response can be formalized as:
+According to the 4-Parameter logistic model (4-PL, \cite{barton:4pl}), the probability of a correct response can be formalized as:
 
@@
 \end{equation}
-where $\theta_p$ is the latent trait level of person $p$, $b_i$ is the location of the item on the latent trait (i.e., difficulty parameter, the higher the value, the higher the difficulty of the item), $a_i$ describes the ability of $i$ to discriminate between respondents with different latent trait levels (i.e., discrimination parameter, the higher the value, the higher the discrimination ability of the item), and $c_i$ and $d_i$ describe the probability of observing a correct response when $\theta \to - \infty$ and $\theta \to +\infty$, respectively.
-When $\theta \to - \infty$, the probability of observing a correct response should tend to 0.
-Likewise, when $\theta \rightarrow +\infty$, the probability of observing a correct response should tend to 1.
-However, there might be instances where respondents with $\theta$ levels below the difficulty of the item, whom are hence expected not to respond correctly, might provide the correct response out of luck.
-The pseudoguessing parameter $c_i$ describes this probability, such that the probability of observing a correct response on $i$ for $\theta \to - \infty$ tends to $c_i$ instead of 0.
-The same but inverse consideration applies when $\theta \to + \infty$.
-The $d_i$ parameter describes the probability of endorsing the item given that the latent trait is above the location of the item, such that the probability of observing a correct response on $i$ for $\theta \to + \infty$ tends to $d_i$ instead of 1.
-\ottavia{In other words, $d_i$ represents the upper asymptote for each item.
-The careless error probability is $1 - d_i$.}
+where $\theta_p$ is the latent trait level of person $p$, $b_i$ is the location of the item on the latent trait (i.e., difficulty parameter, the higher the value, the higher the difficulty of the item), and $a_i$ describes the ability of $i$ to discriminate between respondents with different latent trait levels (i.e., discrimination parameter, the higher the value, the higher the discrimination ability of the item).
+Parameters $c_i$ and $d_i$ represent the lower and upper asymptotes of the probability, which should naturally tend to 0 and 1 when $\theta \to - \infty$ and $\theta \to +\infty$, respectively.
+%However, there might instances where respondents with $\theta_p \to -\infty$ provide the correct response and respondents with $\theta_p \to + \infty$ do not provide the correct response.
+%However, there might be instances where respondents with $\theta$ levels below the difficulty of the item, whom are hence expected not to respond correctly, might provide the correct response out of luck.
+The pseudoguessing parameter $c_i$ describes the probability of observing a correct response on $i$ for $\theta \to - \infty$, such that the probability tends to $c_i$ instead of 0. 
+%The same but inverse consideration applies when $\theta \to + \infty$. 
+The $d_i$ parameter describes the probability of observing a correct response on $i$ for $\theta \to + \infty$, such that this probability tends to $d_i$ instead of 1.
+The careless error probability is $1 - d_i$ (i.e., the probability of not endorsing the item given that the $\theta_p > b_i$).
 
-By constraining $\forall i \in B, \, d_i = 1$ (where $B$ is the set of items in a test) in equation \ref{eq:4pl}, the 3-Parameter logistic (3-PL, \cite{lord:3pl}) model is obtained.
+%By constraining $\forall i \in B, \, d_i = 1$ (where $B$ is the set of items in a test) in equation \ref{eq:4pl}, the 3-Parameter logistic (3-PL, \cite{lord:3pl}) model is obtained.
 From the 3-PL model, the 2-Parameter logistic model (2-PL, \cite{birnbaum}) is obtained by constraining $\forall i \in B, \, c_i = 0$, and the 1-parameter logistic model (1-PL, equivalent to the Rasch model) is obtained by constraining $\forall i \in B, \, a_i = 1$.
@@
 As $1 - d_i$ increases, the upper aymptote $d_i$ decreases.
-This probability is instrinsically related to the rank of the item in the test.
-As such, the careless error parameter in Equation (\ref{eq:4pl}), which usually a property of the item per se expressed as $d_i$, in this case becomes a property of the item rank $r = \{1, \ldots, R\}$ in the test, $d_r$, with the constraint $d_{r-1} < d_r$.
+This probability is instrinsically related to the rank of the item in the test, hence the careless error parameter in Equation (\ref{eq:4pl}), which is usually a property of the item ($d_i$), becomes a property of the item rank $r = \{1, \ldots, R\}$ in the test, $d_r$, with the constraint $d_{r-1} > d_r$.
 \normalcolor
@@
 
-The measurement precision of each item with respect to different levels of the latent trait can be expressed by the so-called \emph{item information functions} (IIFs), which for the 4-PL is typically formalized as \cite{magis:iif}:
+The measurement precision of each item with respect to different levels of the latent trait can be expressed by the \emph{item information functions} (IIFs). 
+\color{blue}
+Given that in this application the tiredness of the respondents has been conceptualized as the careless errors observed as the administration goes on, the typical formalization of the IIF for the 4-PL \cite{magis:iif} has been modified to account for the rank of presentation $r$ of item $i$, as follows:
+\normalcolor
 
 \begin{equation}\label{eq:iif}
-	\text{IIF}_i = \dfrac{a^2[P(\theta)-c_i]^2[d_i - P(\theta)]^2}{(d_i-c_i)^2 P(\theta)Q(\theta)}.
+	\text{IIF}_{i}(r) = \dfrac{a^2[P(\theta)-c_i]^2[d_r - P(\theta)]^2}{(d_{r}-c_i)^2 P(\theta)Q(\theta)}, 
 \end{equation}
+whereas in the typical formalization $d_r = d_i$.
+%the $d$ parameter in Equation (\ref{eq:iif}) is a property related to its order of presentation in the test $r$, and it is hence denoted as $d_r$ with $r = \{1, \ldots, R\}$.
 The informativeness of each item is strongly influenced by the location of the item on the latent trait with respect to a specific latent trait level $\theta$, its discriminativity, and the probability of lucky guess and careless error.
-In absence of lucky guess and careless error, the IIF reaches its maximum when the location of the item $b_i$ matches the latent trait level $\theta$, and it decreases as the distance between $b_i$ and $\theta$ increases.
+In absence of lucky guess and careless error, the IIF is maximum when  $\theta_p = b_i$, and it decreases as the distance between $b_i$ and $\theta_p$ increases.
 Moreover, the higher the discrimination of the item $a_i$, the more informative the item.
-When the lucky guess and careless error are taken into account, the informativeness of the item decreases, and, most importantly, the maximum of the IIF does not corresponds to the item location on the latent trait and it is generally lower.
+When the lucky guess and careless error are taken into account, the informativeness of the item decreases, the IIF is lower, and it maximum is shifted.
 
-The \emph{test information function} (TIF) is the sum of the IIFs, such that its shape (i.e., its informativeness with respect to different levels of the latent trait) and its height (i.e., the amount of information for different levels of the latent trait) depend on the distribution of the items along the latent trait.
-The more the items with high discrimination and low lucky guess and careless error parameters are spread throughout the latent trait, the more the test would be informative of different regions.
-The more the items have lucky guesses and careless errors, the lower the TIF.
-
-\color{blue}
-Again, given that in this application the tiredness of the respondents has been conceptualized as the probability of observing careless errors as the administration goes on, the $d$ parameter in Equation \ref{eq:iif} is a property related to its order of presentation in the test $r$, and it is hence denoted as $d_r$ with $r = \{1, \ldots, R\}$.
-\normalcolor
+The \emph{test information function} (TIF) is the sum of the IIFs, such that its shape (i.e., its informativeness with respect to different latent trait levels) and its height (i.e., the amount of information for different latent trait levels) depend on the items distribution along the latent trait.
+The more the items with high discrimination and low lucky guess and careless error parameters are spread throughout the latent trait, the more the test is informative of different regions.
 
@@
 
-The two algorithms are based on the same principle of reducing as much as possible the distance between a target TIF (TIF-target, describes the desired characteristics of the STFs in terms of measurement precision) and a provisional TIF (pTIF) obtained from the items selected up to that point.
-At each iteration, the item is included in the STF according to its ability of bridging the gap between the two TIFs. 
-The algorithms stop when the last item considered for inclusion does not contribute to bring the pTIF closer to the TIF-target, that is when the distance between the TIF-target and the pTIF with the last considered item is equal to or greater than the distance between the TIF-target and the pTIF without the last considered items (i.e., termination criterion).
+The two algorithms aim at reducing the distance between a target TIF (TIF-target, describes the desired measurement precision of the STFs) and a provisional TIF (pTIF) obtained from the items included in the STF.
+At each iteration, an item is included in the STF according to its ability of bridging the gap between the two TIFs. 
+The algorithms stop when the distance between the TIF-target and the pTIF with the last considered item is equal to or greater than the distance between the TIF-target and the pTIF without the last considered items (i.e., termination criterion).
 
-In what follows, the TIF-target is represented by the TIF obtained on all the items in a test without careless error parameters, that is the TIF that would be obtained if respondents would never get tired during the administration.
-Given that the original set of items is denoted as $B$, the TIF-target obtained from this set is denoted as $\text{TIF}_B$.
+In what follows, the TIF-target is represented by the TIF that would be obtained if respondents would never get tired during the administration of all the items in a test $B$.
+Therefore, the TIF-target is denoted as  $\text{TIF}_B$.
 
-The parameters of the items in $B$ are defined through an $I \times 4$ matrix, where $I$ is the total number of items in $B$ ($||B||$, where $||X||$ denotes the cardinality of set $X$) and the 4 columns contain the item parameters $b_i$, $a_i$, $c_i$, and $d_i$.
+%The parameters of the items in $B$ are defined through an $I \times 4$ matrix, where $I$ is the total number of items in $B$ ($||B||$, where $||X||$ denotes the cardinality of set $X$) and the 4 columns contain the item parameters $b_i$, $a_i$, $c_i$, and $d_i$.
 Given that $B$ is the set of item without the effect of the tiredness, $d_i = 1$, $\forall i \in \{1, \ldots, I\}$.
-To include the tiredness of the respondents, the vector of careless error parameters $d_i$ is modified with an exponential function, $d_i' = \exp(-\lambda r_i)$ (where $\lambda$ is the speed parameter that determines the steepness of the function and $r$ is the rank of the $i$-th item in the administration).
-The set of items with $d_i'$ is denoted $B'$.
+To include the tiredness of the respondents, the vector of careless error parameters $d_r$ should be modified considering the item rank of presentation.
+In this application, $d_r$ is modified with an exponential function, $d_r = \exp(-\lambda r)$ (where $\lambda$ is the non-negative speed parameter that determines the steepness of the function and $r$ is the rank of the $r$-th item in the administration).
+of the i-th item in the administration).
+The set of items with $d'$
+i is denoted $B'$.
 
-Since the TIF increases as the number of items in a test increases, the comparison between $\text{TIF}_B$ and the TIF of the STF obtained by the item selections provided by the two algorithms is based on the mean TIF (i.e., the TIF divided by the number of items in the STF).
-Nonetheless, in what follows the mean TIF will be simply referred to as $\text{TIF}_{Q_x}$, with $x \in \{B, B', \text{Frank}, \text{\text{Léon}}\}$.
+Since the TIF increases as the number of items in a test increases, the comparison between $\text{TIF}_B$ and the TIF of the STFs is based on the mean TIF (i.e., the TIF divided by the number of items).
+Nonetheless, in what follows the mean TIF will be simply referred to as $\text{TIF}_{Q_x}$, with $x \in \{B, B', \text{Frank}, \text{\text{Léon}}\}$ and $Q$ is the set of items in the tests $B$ or $B'$ or the subset of items included in the STFs generated by Frank and Léon.
 
@@
 	\item  $A^k = B \setminus Q^k$ 
-	\item $\forall i \in A^k$, $p\text{TIF}_{i}^k = \frac{\text{TIF}^k + \text{IIF}_{i}}{||Q^k||+1}$
-	\item $i^* = \arg \min_{i \in A^k} |\text{TIF}_B - \text{pTIF}_i|$, with $c_i = 0$ and $d_i$, $\forall i \in B$
-	\item Termination criterion: $|\text{TIF}_B - \text{pTIF}_{i^*}| \geq |\text{TIF}_B - \text{TIF}^{k}|$: 
+	\item $\forall i \in A^k$, $p\text{TIF}_{i}^k = \frac{\text{TIF}^k + \text{IIF}_{i}}{||Q^k||+1}$, with $c_i = 0$ and $d_i = 1$, $\forall i \in B$
+	\item $i^* = \arg \min_{i \in A^k} |\text{TIF}_B - \text{pTIF}_i^k|$
+	\item Termination criterion: $|\text{TIF}_B - \text{pTIF}_{i^*}^k| \geq |\text{TIF}_B - \text{TIF}^{k}|$: 
 	\begin{itemize}
-		\item FALSE:  $Q^{k+1} = Q^{k} \cup \{i^*\}$, $TIF^{k+1} = p\text{TIF}_{i^*}$, iterates 1-4 
+		\item FALSE:  $Q^{k+1} = Q^{k} \cup \{i^*\}$, $\text{TIF}^{k+1} = p\text{TIF}_{i^*}$, iterates 1-4 
 		\item TRUE: Stop, %The item in $i^*$ does not contribute to reduce the distance from the TIF-target, hence: 
-		$Q_{Frank} = Q^k$
+		$Q_{\text{Frank}} = Q^k$
 
@@
 \end{enumerate}
-
-%The first operation done by Frank at the beginning ($k=0$) is to compute the IIFs of all the items in $B$, considering the available item parameters.
 At $k = 0$, the subset of items $Q^0$ is empty and the $\text{TIF}^0$ is 0 for all the $\theta$ levels. 
@@
 The procedure is replicated 100 times.
-At each replica, a test of $B$ of 50 items with difficulty ($b_i \sim \mathcal{U}(-3, 3)$) discrimination ($a_i \sim \mathcal{U}(.90, 2)$) parameters drawn from uniform distributions is generated.
+At each replication, a test $B$ of 50 items with difficulty ($b_i \sim \mathcal{U}(-3, 3)$) discrimination ($a_i \sim \mathcal{U}(.90, 2)$) parameters drawn from uniform distributions is generated.
 Lucky
-guess and careless error parameters are constant, $c_i = 0, \forall i \in B$ and $d_i = \, \forall i \in B$.
+guess and careless error parameters are constant, $c_i = 0$ and $d_i = 1$, $\forall i \in B$.
 The $\text{TIF}_B$ (i.e., the TIF-target) is obtained as the average TIF  from the items in $B$, and describes the measurement precision that would be obtained if respondents were administered with all the items without getting tired.
@@
 \color{blue}
-A new test, $B'$, is generated at each replication, where $b_i' = b_i$, $a_i' = a_i$, $c_i = 0$, $\forall i \in B'$, and $d_i' = \exp(-\lambda r_i)$, with $\lambda = 0.01$ and $r = \{0, \ldots I -1\}$.
+At each replication, a new test, $B'$, is generated, where $b_i' = b_i$, $a_i' = a_i$, $c_i = 0$, $\forall i \in B'$, and $d_r = \exp(-\lambda r_i)$, with $\lambda = 0.01$ and $r = \{0, \ldots, ||B|| -1\}$.
 
-At each replication, Frank and Léon generate a STF for approximating the $\text{TIF}_B$.
-Moreover, the average TIF is computed considering the item with the tiredness effect in $B'$, denoted as $\text{TIF}_{B'}$.
-Although Frank grounds the item selection on $B$ (i.e., without considering the tiredness), the final TIF is computed by considering the vector $d_r$ associated to the rank of the items in $Q_{\text{Frank}}$.
+At each replication, Frank and Léon generate a STF for approximating the $\text{TIF}_B$. An average TIF is computed considering the item in $B'$, denoted as $\text{TIF}_{B'}$.
+Although Frank grounds the item selection on the set $B$, the final TIF is computed by considering the vector $d_r$ associated to the rank of the items in $Q_{\text{Frank}}$.
 %La differenza è che Frank calcola tutte le iif degli tiem all'inizio, consdierando la careless error legata alla posizione dell'item così come viene generata inizialmente dalla funzione. 
@@
 The average distance from $\text{TIF}_B$ of the STFs generated by Frank and Léon at each iteration, as well as of the test obtained from $B'$ has been considered as a criterion for evaluating the ability of Léon of generating informative STFs while accounting for the tiredness of the respondents, $\Delta_x = |\text{TIF}_B - \text{TIF}_{Q_x}|$, with $x \in \{B', \text{Frank}, \text{Léon}\}$.
-Trivially, when the $\text{TIF}_\{B'\}$ is considered, $Q = B'$.
+Trivially, when the $\text{TIF}_{B'}$ is considered, $Q = B'$.
 
@@
 	\includegraphics[width=\linewidth]{img/box-plot-alogirthms}
-	\caption{Distance from $\text{TIF}_{B}$ of $\text{TIF}_{B'}$ (green dots), $\text{TIF}_{Frank}$ (yellow triangles), and $\text{TIF}_{\text{Léon}}$ (brown squares) in each of the 100 replications.
-The horizontal green, yellow, and brown lines are the average distance from $\text{TIF}_B$ of $\text{TIF}_{B'}$, $\text{TIF}_{Frank}$, and $\text{TIF}_{\text{Léon}}$, respectively}
+	\caption{Distance from $\text{TIF}_{B}$ of $\text{TIF}_{B'}$, $\text{TIF}_{\text{Frank}}$, and $\text{TIF}_{\text{Léon}}$  across the 100 replications.} 
 	\label{fig:points-alogirthms}
@@
 
-This manuscript presented a first attempt at the development of an IRT-based algorithm, denoted as Léon, for the generation of informative and static STFs able to account for the tiredness of the respondents.
-In the item selection for inclusion in the STF, Léon considers the number of items included up to that iteration and adds a penalty in terms of higher probability of careless error, which increases as the number of items included in the STF increases.
-Its performance in approximating a TIF target, which is here conceptualized as the TIF that one would obtain considering the entire administration of the test if respondents would never get tired (i.e., without careless error) , is compared against that of another IRT-based algorithm, denoted as Frank.
-Differently from Léon, Frank does not add any penalization for the number of items included in the STF.
-Finally, the distance between the TIF obtained from the administration of the entire test with and without tiredness has been considered as well.
+This manuscript presented an IRT-based algorithm, denoted as Léon, for the generation of  STFs. 
+Léon grounds the item selection by concurrently considering the number of items included in the STF and the measurement precision with respect to an ideal target where all the items are administered in absence of careless error (i.e., TIF-target).
+The ability of Léon of approximating the TIF-target has been compared against that of another algorithm (Frank) not accounting for the tiredness of the respondents during item selection and with the measurement precision obtained from the administration of the entire test, including the careless mistakes due to the response fatigue.
 
-The results of a simulation study suggest that the administration of fewer items selected also considering the tiredness of the respondents might provide better measurement tools  than administering the entire test and tiring out the respondents.
+Generally, the results suggest that the administration of fewer items provide better measurement tools than administering the entire test, especially if the selection process accounts for the effect of the response fatigue.
 
-Although the results are promising, there are several limitations that should be acknowledged.
-Firstly, this study is focused on the approximation of the TIF target.
-However, the final aim with which tests are administered is to estimate the latent trait of the respondents.
-The lack of the precision of estimation of the latent trait of the respondents represents the main limitation and future studies should focus on this issue.
-Secondly, the operalization of the tiredness of the respondents as an increase of the probability of committing careless error as the administration goes on is an arbitrary choice.
+Although the results are promising, several limitations must be acknowledged.
+Firstly, while this study primarily focuses on approximating ideal measurement precision as expressed by the TIF-target, no investigations on the precision with which the latent trait is estimated with the STF are presented.
+Future studies should further investigate this issue to understand whether administering less items brings actual benefits in the estimation of the latent trait.
+Secondly, the operalization of the tiredness of the respondents as an increase of the probability of committing careless error as the administration goes on is an arbitrary choice, and other possibilities should be investigated.
 
@@
 
-\bibitem {birnbaum}
-Birnbaum, A. (1968). Some latent trait models and their use in inferring an examinee’s ability. In F. M.
-Lord, M. R. Novick (Eds.), Statistical theories of mental test scores (pp. 397-479). Reading, MA:
-Addison-Wesley
+%\bibitem {birnbaum}
+%Birnbaum, A. (1968). Some latent trait models and their use in inferring an examinee’s ability. In F. M.
+%Lord, M. R. Novick (Eds.), Statistical theories of mental test scores (pp. 397-479). Reading, MA:
+%Addison-Wesley
 
-\bibitem {lord:3pl}
-Lord, F. M. (1980). Applications of item response theory to practical testing problems. Hillsdale, NJ:
-Lawrence Erlbaum
+%\bibitem {lord:3pl}
+%Lord, F. M. (1980). Applications of item response theory to practical testing problems. Hillsdale, NJ:
+%Lawrence Erlbaum
 
@@
 
-\bibitem {rsoft}
-R Development Core Team. (2012). R: A language and environment for statistical computing [Computer
-software]. Vienna, Austria: R Foundation for Statistical Computing.
+%\bibitem {rsoft}
+%R Development Core Team. (2012). R: A language and environment for statistical computing [Computer
+%software]. Vienna, Austria: R Foundation for Statistical Computing.
 

### 2025-02-28 sis2025/LaTex+Package/styles/paper-sis-template.tex
yupdate sis

@@
 \def\UrlFont{\rmfamily}
-\newcommand{\ottavia}[1]{\textcolor{red}{#1}}
-\newcommand{\livio}[1]{\textcolor{blue}{#1}}
+\newcommand{\ottavia}[1]{\textcolor{purple}{#1}}
+\newcommand{\livio}[1]{\textcolor{orange}{#1}}
 
@@
 %
-\title{Nothing lasts forever -- only item administration: Item Response Theory procedures to shorten tests}
+\title{Nothing lasts forever -- only item administration: An Item Response Theory algorithm to shorten tests}
 %
@@
 \and
-{\color{red}Department of Statistics, University of Padova, IT} \\}
+{\color{red}Department of Statistics, University of Padova, IT} \livio{devi vedere se è giusto} \\}
 
@@
 However, there is a trade-off between the number of administered items and the response quality.
-As such, the trade-off between the number of administered items and the tiredness of the respondents should be kept in mind to obtain reliable and precise measurement tools.
-Item Response Theory (IRT, see, e.g., \cite{baker}) provides an ideal framework for shortening existing tests (or for developing tests from item banks) given the detailed information that they provide of the measurement precision of each item with respect to different levels of the latent trait.
+As such, the trade-off between the number of administered items and the tiredness of the respondents \ottavia{(i.e., response fatigue)} should be kept in mind to obtain reliable and precise measurement tools.
+Item Response Theory (IRT, see, e.g., \cite{baker}) provides an ideal framework for shortening existing tests given the detailed information that they provide of the measurement precision of each item with respect to different levels of the latent trait (see e.g., \cite{pauci}).
 In this contribution, we present a new IRT-based algorithm for developing short test forms (STFs) from existing tests, denoted as Léon.
-This algorithm accounts for the tiredness of the respondents during the item inclusion process, such that it attempts at minimizing the number of selected items while accounting for the tiredness  of the respondents in order to maximize the measurement precision (as expressed by the test information function, TIF) of the STF.
+This algorithm considers the response fatigue during the item selection process, such that it attempts at minimizing the number of selected items to maximize the measurement precision (as expressed by the test information function, TIF) of the STF.
 %The ability of Léon of developing STFs able to approximate the TIF that would be obtained by administering all the items under the assumption that respondents would never get tired is investigated in a simulation study.
 %Specifically, Léon's ability is compared against that of another algorithm for developing STFs, which does not account for the tiredness of the respondents. 
-\color{red} The tiredness of the respondents has been here conceptualized as the careless error related to the rank of the items during the administration. \normalcolor
+The response fatigue has been here conceptualized as the careless error related to the item rank during the administration.
 
@@
 IRT models differentiate according to the number of parameters used for describing the characteristics of the items.
-According to the 4-Parameter logistic model (4-PL, \cite{barton:4pl}), the probability of a correct response can be formalized as:
+According to the 4-Parameter logistic model (4-PL, \cite{barton:4pl}), the probability of a correct response is:
 
@@
 \end{equation}
-where $\theta_p$ is the latent trait level of person $p$, $b_i$ is the location of the item on the latent trait (i.e., difficulty parameter, the higher the value, the higher the difficulty of the item), and $a_i$ describes the ability of $i$ to discriminate between respondents with different latent trait levels (i.e., discrimination parameter, the higher the value, the higher the discrimination ability of the item).
-Parameters $c_i$ and $d_i$ represent the lower and upper asymptotes of the probability, which should naturally tend to 0 and 1 when $\theta \to - \infty$ and $\theta \to +\infty$, respectively.
+where $\theta_p$ is the latent trait level of person $p$, $b_i$ is the item location on the latent trait (i.e., difficulty parameter, the higher the value, the higher the difficulty of the item), and $a_i$ is the item ability to discriminate between respondents with different latent trait levels (i.e., discrimination parameter, the higher the value, the higher the discrimination ability of the item).
+Parameters $c_i$ and $d_i$ are the lower and upper asymptotes of the probability, which should naturally tend to 0 and 1 when $\theta \to - \infty$ and $\theta \to +\infty$, respectively.
 %However, there might instances where respondents with $\theta_p \to -\infty$ provide the correct response and respondents with $\theta_p \to + \infty$ do not provide the correct response.
 %However, there might be instances where respondents with $\theta$ levels below the difficulty of the item, whom are hence expected not to respond correctly, might provide the correct response out of luck.
-The pseudoguessing parameter $c_i$ describes the probability of observing a correct response on $i$ for $\theta \to - \infty$, such that the probability tends to $c_i$ instead of 0. 
+The pseudoguessing parameter $c_i$ is the probability of observing a correct response on $i$ for $\theta \to - \infty$, such that the probability tends to $c_i$ instead of 0. 
 %The same but inverse consideration applies when $\theta \to + \infty$. 
-The $d_i$ parameter describes the probability of observing a correct response on $i$ for $\theta \to + \infty$, such that this probability tends to $d_i$ instead of 1.
+The $d_i$ parameter is the probability of observing a correct response on $i$ for $\theta \to + \infty$, such that this probability tends to $d_i$ instead of 1.
 The careless error probability is $1 - d_i$ (i.e., the probability of not endorsing the item given that the $\theta_p > b_i$).
@@
 
-\color{blue}
-In this study, we operationalized the tiredness of the individuals as the careless error probability $1 - d_i$, which increases as the administration goes on.
-As $1 - d_i$ increases, the upper aymptote $d_i$ decreases.
-This probability is instrinsically related to the rank of the item in the test, hence the careless error parameter in Equation (\ref{eq:4pl}), which is usually a property of the item ($d_i$), becomes a property of the item rank $r = \{1, \ldots, R\}$ in the test, $d_r$, with the constraint $d_{r-1} > d_r$.
+\ottavia{In this study, the response fatigue has been conceptualized as the careless error probability $1 - d_i$, which increases as the administration goes on.
+As $1 - d_i$ increases, the upper aymptote $d_i$ decreases.}
+This probability is instrinsically related to the item rank in the test, hence the careless error parameter in Equation (\ref{eq:4pl}), which is usually a property of the item ($d_i$), becomes a property of the item rank $r = \{1, \ldots, R\}$ in the test, $d_r$, with the constraint $d_{r-1} > d_r$.
 \normalcolor
@@
 
-The measurement precision of each item with respect to different levels of the latent trait can be expressed by the \emph{item information functions} (IIFs). 
+The measurement precision of each item with respect to different levels of the latent trait is expressed by the \emph{item information functions} (IIFs). 
 \color{blue}
-Given that in this application the tiredness of the respondents has been conceptualized as the careless errors observed as the administration goes on, the typical formalization of the IIF for the 4-PL \cite{magis:iif} has been modified to account for the rank of presentation $r$ of item $i$, as follows:
+Given that in this application the response fatigue has been conceptualized as the careless errors as the administration goes on, the typical formalization of the IIF for the 4-PL \cite{magis:iif} has been modified to account for the rank of presentation $r$ of item $i$, as follows:
 \normalcolor
@@
 %the $d$ parameter in Equation (\ref{eq:iif}) is a property related to its order of presentation in the test $r$, and it is hence denoted as $d_r$ with $r = \{1, \ldots, R\}$.
-The informativeness of each item is strongly influenced by the location of the item on the latent trait with respect to a specific latent trait level $\theta$, its discriminativity, and the probability of lucky guess and careless error.
+The $\text{IIF}_i$ is strongly influenced by the item location on the latent trait with respect to a specific $\theta_p$, its discriminativity, and its lucky guess and careless error.
 In absence of lucky guess and careless error, the IIF is maximum when  $\theta_p = b_i$, and it decreases as the distance between $b_i$ and $\theta_p$ increases.
-Moreover, the higher the discrimination of the item $a_i$, the more informative the item.
 When the lucky guess and careless error are taken into account, the informativeness of the item decreases, the IIF is lower, and it maximum is shifted.
@@
 
-The two algorithms aim at reducing the distance between a target TIF (TIF-target, describes the desired measurement precision of the STFs) and a provisional TIF (pTIF) obtained from the items included in the STF.
+The two algorithms (denoted as Frank and Léon) aim at reducing the distance between a target TIF (TIF-target, describes the desired measurement precision of the STFs) and a provisional TIF (pTIF) obtained from the items included in the STF.
 At each iteration, an item is included in the STF according to its ability of bridging the gap between the two TIFs. 
@@
 %The parameters of the items in $B$ are defined through an $I \times 4$ matrix, where $I$ is the total number of items in $B$ ($||B||$, where $||X||$ denotes the cardinality of set $X$) and the 4 columns contain the item parameters $b_i$, $a_i$, $c_i$, and $d_i$.
-Given that $B$ is the set of item without the effect of the tiredness, $d_i = 1$, $\forall i \in \{1, \ldots, I\}$.
-To include the tiredness of the respondents, the vector of careless error parameters $d_r$ should be modified considering the item rank of presentation.
-In this application, $d_r$ is modified with an exponential function, $d_r = \exp(-\lambda r)$ (where $\lambda$ is the non-negative speed parameter that determines the steepness of the function and $r$ is the rank of the $r$-th item in the administration).
-of the i-th item in the administration).
-The set of items with $d'$
-i is denoted $B'$.
+Given that $B$ is the set of item without the effect of the tiredness, $d_i = 1$, $\forall i \in B$.
+To include the response fatigue, the vector of careless error parameters $d_r$ should be modified considering the item rank of presentation.
+In this application, $d_r$ is modified with an exponential function, $d_r = \exp(-\lambda r)$ (where $\lambda$ is the non-negative speed parameter determining the steepness of the function and $r$ is the rank of the $r$-th item in the administration).
+The items set with $d'$ is $B'$.
 
-Since the TIF increases as the number of items in a test increases, the comparison between $\text{TIF}_B$ and the TIF of the STFs is based on the mean TIF (i.e., the TIF divided by the number of items).
-Nonetheless, in what follows the mean TIF will be simply referred to as $\text{TIF}_{Q_x}$, with $x \in \{B, B', \text{Frank}, \text{\text{Léon}}\}$ and $Q$ is the set of items in the tests $B$ or $B'$ or the subset of items included in the STFs generated by Frank and Léon.
+Since the TIF increases as the number of test items increases, the comparison between $\text{TIF}_B$ and the TIF of the STFs is based on the mean TIF (i.e., the TIF divided by the number of items).
+In what follows, the mean TIF  is simply referred to as $\text{TIF}_{Q_x}$, with $x \in \{B, B', \text{Frank}, \text{\text{Léon}}\}$ and $Q$ is the items set in the tests $B$ or $B'$ or the items subset in the STFs generated by the algorithms.
 
@@
 
-Frank considers the entire latent trait for the item selection, in that it selects the item whose IIF is best able to reduce the distance from the $\text{TIF}_B$ along the entire latent trait, as follows:
+Frank selects the item whose IIF is best able to reduce the distance from the $\text{TIF}_B$ along the entire latent trait, as follows:
 
@@
 	\item $\forall i \in A^k$, $p\text{TIF}_{i}^k = \frac{\text{TIF}^k + \text{IIF}_{i}}{||Q^k||+1}$, with $c_i = 0$ and $d_i = 1$, $\forall i \in B$
-	\item $i^* = \arg \min_{i \in A^k} |\text{TIF}_B - \text{pTIF}_i^k|$
+	\item $i^* = \arg \min_{i \in A^k} (|\text{TIF}_B - \text{pTIF}_i^k|)$
 	\item Termination criterion: $|\text{TIF}_B - \text{pTIF}_{i^*}^k| \geq |\text{TIF}_B - \text{TIF}^{k}|$: 
@@
 
-\color{blue}
 At each replication, a new test, $B'$, is generated, where $b_i' = b_i$, $a_i' = a_i$, $c_i = 0$, $\forall i \in B'$, and $d_r = \exp(-\lambda r_i)$, with $\lambda = 0.01$ and $r = \{0, \ldots, ||B|| -1\}$.
@@
 Frank falls in between the two, also presenting the least consistent performance across the replications.
-\ottavia{dovrei aggiunger some sort of test}
 
@@
 Léon grounds the item selection by concurrently considering the number of items included in the STF and the measurement precision with respect to an ideal target where all the items are administered in absence of careless error (i.e., TIF-target).
-The ability of Léon of approximating the TIF-target has been compared against that of another algorithm (Frank) not accounting for the tiredness of the respondents during item selection and with the measurement precision obtained from the administration of the entire test, including the careless mistakes due to the response fatigue.
+The ability of Léon of approximating the TIF-target has been compared against that of another algorithm (Frank) not accounting for the response fatigue during item selection and with the measurement precision obtained from the administration of the entire test, including the careless mistakes due to the response fatigue.
 
@@
 Although the results are promising, several limitations must be acknowledged.
-Firstly, while this study primarily focuses on approximating ideal measurement precision as expressed by the TIF-target, no investigations on the precision with which the latent trait is estimated with the STF are presented.
+Firstly, while this study primarily focuses on approximating ideal measurement precision as expressed by the TIF-target, no investigations on the precision with which the latent trait is estimated with the STFs are presented.
 Future studies should further investigate this issue to understand whether administering less items brings actual benefits in the estimation of the latent trait.
-Secondly, the operalization of the tiredness of the respondents as an increase of the probability of committing careless error as the administration goes on is an arbitrary choice, and other possibilities should be investigated.
+Secondly, the operalization of the tiredness of the response fatigue as an increase of the probability of committing careless error as the administration goes on is an arbitrary choice, and other possibilities should be investigated.
 
@@
 model. Princeton, NJ: Educational Testing Service.
+
+\bibitem{pauci}
+
+Epifania, O.M., Anselmi, P., Robusto, E.
+(2022).
+Pauci sed boni: An Item Response Theory Approach for Shortening Tests.
+In: Wiberg, M.,et al.
+(eds) \textit{Quantitative Psychology.} IMPS 2022.
+Springer Proceedings in Mathematics \& Statistics, vol 422.
+Springer, Cham.
+\url{https://doi.org/10.1007/978-3-031-27781-87}
 

### 2025-02-28 sis2025/LaTex+Package/styles/paper-sis-template.tex
last update :)

@@
 \and
-{\color{red}Department of Statistics, University of Padova, IT} \livio{devi vedere se è giusto} \\}
+ Department of Statistical Sciences, University of Padova, IT \\}
 
@@
 \begin{abstract} 
-\ottavia{da rivedere}
-Although a larger number of test items improves measurement validity, the effect of respondents’ fatigue on the response quality should be acknowledged for developing reliable measurement tools.
-This contribution presents an item response theory-based algorithm (denoted as Léon) able to shorten existing tests by concurrently accounting for the measurement precision of the abbreviated test and the tiredness of the respondents, which is here conceptualized as the probability of observing careless errors as the number of administered items increases.
+	\ottavia{The responses to the items composing psychometrics tests are often used to estimate the respondents' latent trait levels.}
+Although a larger number of items improves measurement validity, the effect of respondents’ fatigue on the response quality should be acknowledged for developing reliable measurement tools.
+This contribution presents an item response theory-based algorithm (denoted as Léon) able to shorten existing tests by concurrently accounting for the measurement precision of the abbreviated test and the tiredness of the respondents.
 A simulation study compares the performance of Léon of approximating the measurement precision that would be obtained from the full-length test without the effect of the tiredness against that of another algorithm that does not account for the tiredness of the respondents.
-Although on average the two algorithms select the same number of items, Léon provides a better approximation to the measurement precision of the full-length test than the other algorithm.
+Although, on average, the two algorithms select the same number of items, Léon provides a better approximation to the measurement precision of the full-length test than the other algorithm.
 % We would like to encourage you to list your keywords within
@@
 %Specifically, Léon's ability is compared against that of another algorithm for developing STFs, which does not account for the tiredness of the respondents. 
-The response fatigue has been here conceptualized as the careless error related to the item rank during the administration.
+%The response fatigue has been here conceptualized as the careless error related to the item rank during the administration.
 
@@
 The careless error probability is $1 - d_i$ (i.e., the probability of not endorsing the item given that the $\theta_p > b_i$).
+\ottavia{Item parameters are summarized in vector $\varphi = (b_i, a_i, c_i, d_r)$.}
 
@@
 This probability is instrinsically related to the item rank in the test, hence the careless error parameter in Equation (\ref{eq:4pl}), which is usually a property of the item ($d_i$), becomes a property of the item rank $r = \{1, \ldots, R\}$ in the test, $d_r$, with the constraint $d_{r-1} > d_r$.
+\ottavia{per come l'ho scritto non uò essere maggiore uguale.
+credo che a livello teorico non abbia senso}
 \normalcolor
@@
 \begin{equation}\label{eq:iif}
-	\text{IIF}_{i}(r) = \dfrac{a^2[P(\theta)-c_i]^2[d_r - P(\theta)]^2}{(d_{r}-c_i)^2 P(\theta)Q(\theta)}, 
+	\text{IIF}_{i}(r) = \dfrac{a^2[P(x_{pi}=1|\theta, \varphi)-c_i]^2[d_r - P(x_{pi}=1|\theta, \varphi)]^2}{(d_{r}-c_i)^2 P(x_{pi}=1|\theta, \varphi)P(x_{pi}=0|\theta, \varphi)}, 
 \end{equation}
@@
 The $\text{IIF}_i$ is strongly influenced by the item location on the latent trait with respect to a specific $\theta_p$, its discriminativity, and its lucky guess and careless error.
-In absence of lucky guess and careless error, the IIF is maximum when  $\theta_p = b_i$, and it decreases as the distance between $b_i$ and $\theta_p$ increases.
+In absence of lucky guess and careless error (i.e., $c = 0$, $d = 1$), the IIF is maximum when  $\theta_p = b_i$, and it decreases as the distance between $b_i$ and $\theta_p$ increases.
 When the lucky guess and careless error are taken into account, the informativeness of the item decreases, the IIF is lower, and it maximum is shifted.
@@
 Since the TIF increases as the number of test items increases, the comparison between $\text{TIF}_B$ and the TIF of the STFs is based on the mean TIF (i.e., the TIF divided by the number of items). 
-In what follows, the mean TIF  is simply referred to as $\text{TIF}_{Q_x}$, with $x \in \{B, B', \text{Frank}, \text{\text{Léon}}\}$ and $Q$ is the items set in the tests $B$ or $B'$ or the items subset in the STFs generated by the algorithms.
-
-\subsection{Frank}
+\ottavia{In what follows, the mean TIF  is referred to as $\text{TIF}_{x}$, with $x \in \{B, B', \text{Frank}, \text{\text{Léon}}\}$, $Q_x \subset B$ is the item subsets selected by Frank and Léon, and $||X||$ denotes the cardinality of set $X$.}
 
@@
 
-Frank selects the item whose IIF is best able to reduce the distance from the $\text{TIF}_B$ along the entire latent trait, as follows:
+Frank selects the item whose IIF is best able to reduce the distance from the $\text{TIF}_B$ along the entire latent trait, without considering the respondents' fatigue, as follows:
 
-At $k = 0$: $\text{IIF}_i$, $\text{TIF}^0(\theta) = 0 \, \forall \theta$, $Q^0 = \emptyset$. For $k \geq 0$,
+At $k = 0$: $\text{TIF}^0(\theta) = 0 \, \forall \theta$, $Q^0 = \emptyset$. For $k \geq 0$,
 
@@
 At each iteration $k$: (1.) a set of available items is generated as the items in the item bank that have not been included in the STF yet, $A^k = B \setminus Q^k$; (2.)
-An average provisional TIF, $\text{pTIF}$, is computed by adding the IIF of each of the items in the set of the available items $A^k$, one at the time, to the TIF obtained from the items in $Q^k$ (The denominator is obtained by adding 1 to the cardinality of $Q^k$); (3.) Among all the items in $A^k$, the one that allows for minimizing the distance between $\text{pTIF}$ and $\text{TIF}_B$ is included in $i^*$; (4.)
+An average provisional TIF, $\text{pTIF}$, is computed by adding the IIF of each of the items in the set of the available items $A^k$, one at the time, to the TIF obtained from the items in $Q^k$ (the denominator is obtained by adding 1 to the cardinality of $Q^k$); (3.) Among all the items in $A^k$, the one that allows for minimizing the distance between $\text{pTIF}$ and $\text{TIF}_B$ is included in $i^*$; (4.)
 The termination criterion is tested. 
@@
 
-\color{blue}
-\subsection{Léon}
-Differently from Frank, at step (2.) Léon computes the $\text{IIF}_i$ by considering the $d_r$ related to the number of items included in the STF up to that point.  
+To account for the respondents' fatigue, at step (2.) Léon computes the $\text{IIF}_i$ by considering the $d_r$ related to the number of items included in the STF up to that point.  
 \normalcolor
@@
 
-The procedure is replicated 100 times.
+The following procedure is replicated 100 times.
 At each replication, a test $B$ of 50 items with difficulty ($b_i \sim \mathcal{U}(-3, 3)$) discrimination ($a_i \sim \mathcal{U}(.90, 2)$) parameters drawn from uniform distributions is generated.
@@
 
-At each replication, a new test, $B'$, is generated, where $b_i' = b_i$, $a_i' = a_i$, $c_i = 0$, $\forall i \in B'$, and $d_r = \exp(-\lambda r_i)$, with $\lambda = 0.01$ and $r = \{0, \ldots, ||B|| -1\}$.
-
-At each replication, Frank and Léon generate a STF for approximating the $\text{TIF}_B$. An average TIF is computed considering the item in $B'$, denoted as $\text{TIF}_{B'}$.
+At each replication, a new test, $B'$, is generated, where $b_i' = b_i$, $a_i' = a_i$, $c_i = 0$, $\forall i \in B'$, and $d_r = \exp(-\lambda r)$, with $\lambda = 0.01$ and $r = \{0, \ldots, ||B|| -1\}$, the $\text{TIF}_B$ is computed, and Frank and Léon generate a STF for approximating it.
+An average TIF is computed considering the item in $B'$ ($\text{TIF}_{B'}$), as well as the TIFs from the STFs generated by Frank and Léon, $\text{TIF}_{\text{Frank}}$ and $\text{TIF}_{\text{Léon}}$, respectively.
 Although Frank grounds the item selection on the set $B$, the final TIF is computed by considering the vector $d_r$ associated to the rank of the items in $Q_{\text{Frank}}$.
@@
 
-The average distance from $\text{TIF}_B$ of the STFs generated by Frank and Léon at each iteration, as well as of the test obtained from $B'$ has been considered as a criterion for evaluating the ability of Léon of generating informative STFs while accounting for the tiredness of the respondents, $\Delta_x = |\text{TIF}_B - \text{TIF}_{Q_x}|$, with $x \in \{B', \text{Frank}, \text{Léon}\}$.
-Trivially, when the $\text{TIF}_{B'}$ is considered, $Q = B'$.
-
+The average distance between $\text{TIF}_B$ and $\text{TIF}_{\text{Frank}}$ and $\text{TIF}_B$ and $\text{TIF}_{\text{Léon}}$ at each iteration, as well as the  distance between $\text{TIF}_B$ and $\text{TIF}_{B'}$, have been considered as a criterion for evaluating the ability of Léon of generating informative STFs while accounting for the tiredness of the respondents, $\Delta_x = |\text{TIF}_B - \text{TIF}_{x}|$, with $x \in \{B', \text{Frank}, \text{Léon}\}$.
 To better understand whether acknowledging the tiredness of the respondents influences the number of items included in $Q$, the cardinalities of the STFs generated by Frank and Léon, $||Q_{\text{Frank}}||$ and $||Q_{\text{Léon}}||$, respectively, have been compared.
@@
 
-On average, Léon and Frank included the same number of items in the STF, $M_{\text{Léon}} = 6.75 \pm 3.06$, $M_{\text{Frank}} = 6.31 \pm 2.40$, $t = 1.13$, $df = 187.59$, $p = .26$, suggesting that accounting for the tiredness of the respondents does not influence the number of items included in the STF.
+On average, Léon and Frank included the same number of items in the STF, $M_{\text{Léon}} = 6.75 \pm 3.06$, $M_{\text{Frank}} = 6.31 \pm 2.40$, suggesting that accounting for the tiredness of the respondents does not influence the number of items included in the STF.
 %\color{red}
@@
 
-Figure \ref{fig:points-alogirthms} illustrates the distributions of the distances from $\text{TIF}_B$ ($y$-axis) of $Q_x$ ($x$-axis).
+Figure \ref{fig:points-alogirthms} illustrates the distributions of the distances from $\text{TIF}_B$ ($y$-axis) of $B'$, Frank, and Léon ($x$-axis).
 

### 2025-03-01 sis2025/LaTex+Package/styles/paper-sis-template.tex
Submission paper

@@
 \begin{abstract} 
-	\ottavia{The responses to the items composing psychometrics tests are often used to estimate the respondents' latent trait levels.}
+The responses to the items composing psychometrics tests are often used to estimate the respondents' latent trait levels.
 Although a larger number of items improves measurement validity, the effect of respondents’ fatigue on the response quality should be acknowledged for developing reliable measurement tools.
@@
 % the abstract section using the \keywords{...} command.
-\keywords{Item response theory, careless error, information functions, short test forms}
+\keywords{Item response theory; Careless error; Measurement precision; Short test forms}
 \end{abstract}
@@
 However, there is a trade-off between the number of administered items and the response quality.
-As such, the trade-off between the number of administered items and the tiredness of the respondents \ottavia{(i.e., response fatigue)} should be kept in mind to obtain reliable and precise measurement tools.
+As such, the trade-off between the number of administered items and the tiredness of the respondents (i.e., response fatigue) should be kept in mind to obtain reliable and precise measurement tools.
 Item Response Theory (IRT, see, e.g., \cite{baker}) provides an ideal framework for shortening existing tests given the detailed information that they provide of the measurement precision of each item with respect to different levels of the latent trait (see e.g., \cite{pauci}).
@@
 The careless error probability is $1 - d_i$ (i.e., the probability of not endorsing the item given that the $\theta_p > b_i$).
-\ottavia{Item parameters are summarized in vector $\varphi = (b_i, a_i, c_i, d_r)$.}
 
@@
 
-\ottavia{In this study, the response fatigue has been conceptualized as the careless error probability $1 - d_i$, which increases as the administration goes on.
-As $1 - d_i$ increases, the upper aymptote $d_i$ decreases.}
+In this study, the response fatigue has been conceptualized as the careless error probability $1 - d_i$, which increases as the administration goes on.
+As $1 - d_i$ increases, the upper aymptote $d_i$ decreases.
 This probability is instrinsically related to the item rank in the test, hence the careless error parameter in Equation (\ref{eq:4pl}), which is usually a property of the item ($d_i$), becomes a property of the item rank $r = \{1, \ldots, R\}$ in the test, $d_r$, with the constraint $d_{r-1} > d_r$.
-\ottavia{per come l'ho scritto non uò essere maggiore uguale.
-credo che a livello teorico non abbia senso}
-\normalcolor
 
@@
 The measurement precision of each item with respect to different levels of the latent trait is expressed by the \emph{item information functions} (IIFs). 
-\color{blue}
-Given that in this application the response fatigue has been conceptualized as the careless errors as the administration goes on, the typical formalization of the IIF for the 4-PL \cite{magis:iif} has been modified to account for the rank of presentation $r$ of item $i$, as follows:
-\normalcolor
+Given that in this application the response fatigue has been conceptualized as the careless errors as the administration goes on, the typical formalization of the IIF for the 4-PL \cite{magis:iif} has been modified to account for the rank of presentation $r$ of item $i$:
 
 \begin{equation}\label{eq:iif}
-	\text{IIF}_{i}(r) = \dfrac{a^2[P(x_{pi}=1|\theta, \varphi)-c_i]^2[d_r - P(x_{pi}=1|\theta, \varphi)]^2}{(d_{r}-c_i)^2 P(x_{pi}=1|\theta, \varphi)P(x_{pi}=0|\theta, \varphi)}, 
+	\text{IIF}_{i}(r) = \dfrac{a^2[P(\theta)-c_i]^2[d_r - P(\theta)]^2}{(d_{r}-c_i)^2 P(\theta)Q(\theta)}, 
 \end{equation}
-whereas in the typical formalization $d_r = d_i$.
+whereas in the typical formalization $d_r = d_i$. In Equation (\ref{eq:iif}), $P(\theta) = P(x_{pi}=1|\theta, b_i, a_i, c_i, d_r)$  and $Q(\theta) = 1- P(\theta)$.
 %the $d$ parameter in Equation (\ref{eq:iif}) is a property related to its order of presentation in the test $r$, and it is hence denoted as $d_r$ with $r = \{1, \ldots, R\}$.
 The $\text{IIF}_i$ is strongly influenced by the item location on the latent trait with respect to a specific $\theta_p$, its discriminativity, and its lucky guess and careless error.
-In absence of lucky guess and careless error (i.e., $c = 0$, $d = 1$), the IIF is maximum when  $\theta_p = b_i$, and it decreases as the distance between $b_i$ and $\theta_p$ increases.
+In absence of lucky guess and careless error (i.e., $c_i = 0$, $d_i = 1$), the IIF is maximum when  $\theta_p = b_i$, and it decreases as the distance between $b_i$ and $\theta_p$ increases.
 When the lucky guess and careless error are taken into account, the informativeness of the item decreases, the IIF is lower, and it maximum is shifted.
@@
 Since the TIF increases as the number of test items increases, the comparison between $\text{TIF}_B$ and the TIF of the STFs is based on the mean TIF (i.e., the TIF divided by the number of items). 
-\ottavia{In what follows, the mean TIF  is referred to as $\text{TIF}_{x}$, with $x \in \{B, B', \text{Frank}, \text{\text{Léon}}\}$, $Q_x \subset B$ is the item subsets selected by Frank and Léon, and $||X||$ denotes the cardinality of set $X$.}
+In what follows, the mean TIF  is referred to as $\text{TIF}_{x}$, with $x \in \{B, B', \text{Frank}, \text{\text{Léon}}\}$, $Q_x \subset B$ is the item subsets selected by Frank and Léon, and $||X||$ denotes the cardinality of set $X$.
 
@@
 %\normalcolor
-
 Figure \ref{fig:points-alogirthms} illustrates the distributions of the distances from $\text{TIF}_B$ ($y$-axis) of $B'$, Frank, and Léon ($x$-axis).

### 2025-03-01 sis-2025.R

@@ -189,15 +189,18 @@ for (i in 1:length(resAllitems)) {
                        target = tif[[i]]$mean_tif, 
                        type = "all", 
                        value = resAllitems[[i]]$tif_all, 
+                       n = 50,
                        iteration = i)
   tempFrank = data.frame(theta = theta, 
                        target = tif[[i]]$mean_tif, 
                        type = "frank", 
+                       n = ncol(resFrank[[i]]$iif_stf), 
                        value =rowMeans(resFrank[[i]]$iif_stf), 
                        iteration = i)
   tempLeon = data.frame(theta = theta, 
                          target = tif[[i]]$mean_tif, 
                          type = "leon", 
+                        n =  ncol(resLeon[[i]]$iif_stf), 
                          value =rowMeans(resLeon[[i]]$iif_stf), 
                          iteration = i)
   res_tot = rbind(res_tot, tempAll, tempFrank, tempLeon)
@@ -241,6 +244,12 @@ ggplot(myRes,
 ggsave("C:/Users/Ottavia/Documents/GitHub/frank-and-friends/sis2025/LaTex+Package/styles/img/points-alogirthms.pdf", 
        device = "pdf", width = 14, height = 8.5, units = "in")
 
+temp_res = res_tot%>%  
+  group_by(type, n) %>%  
+  summarise(m = mean(difference))
+
+ggplot(res_tot, 
+       aes(y = difference, x = factor(n), color = type)) + geom_boxplot()
 
 myres = res_tot %>%  
   group_by(type) %>%  
